### 2015-08-06 Vortrag/folien.tex
Vortragsfolien angefangen

\documentclass[ucs]{beamer}

%\usepackage[ngerman]{babel}
%\usepackage[latin1]{inputenc}

\usepackage[utf8x]{inputenc}
\usepackage[all]{xy}
\usepackage{hyperref}
\usepackage{algorithm2e}
\usepackage{tikz}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx} % Required for the inclusion of images
\usepackage{amsmath} % Required for some math elements 
\usepackage{ae} % Uml. im PDF-Verzeichnis
%\makeatletter

% to change colors
\newcommand{\fillcol}{green!20}
\newcommand{\bordercol}{black}

\setbeamercovered{transparent} 
\mode<presentation>{
	  \useoutertheme[subsection=false]{miniframes}
	    \useinnertheme{rectangles}
		   \usecolortheme{crane}
}

\title{A Lattice Boltzmann Method for immiscible multiphase flow simulations using the Level Set Method} % Title

\author{Lorenz Hufnagel, Daniel Zint} % Author name
\institute{BGCE Student Project}

\date{x y, 2015} % Date for the report

\begin{document}

\maketitle % Insert the title, author and date

\section{Motivation \& Introduction}

\begin{frame}
\frametitle{Multiphase flow - Examples}
\begin{itemize}
\item<1-> Examples
\item<2-> e.g. Oil in water 
\item<3-> \ldots
\end{itemize}
\end{frame}

\section{Mathematic foundation}
\begin{frame}
\frametitle{Macroscopic fluid mechanics}

\begin{itemize}
\item<1-> $N$ immiscible fluids.
\item<2-> Each has own $\rho_i, \nu_i$
\item<3-> Hydrodynamics described by (incompressible) NSE
\end{itemize}
\visible<3->{
$$
\nabla \cdot  \vec v = 0
$$
$$
\frac{\partial \vec v}{\partial t} + \left(\vec  v \cdot \nabla \right) \vec v
=
-\frac{1}{\rho_i}\nabla p + \nu_i \nabla^2 \vec v $$
}
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface conditions}
\begin{figure}[h!]
    %\flushright
\includegraphics[width=6cm]{skizze.png}
  \caption{Two fluid domains $\Omega_i$ and interface $\Gamma$ inbetween}
\end{figure}
\begin{itemize}
\item<1-> Velocity across interface is $C_0$-continous 
  $$\lim_{\epsilon \to 0}(\vec v\left(x+\epsilon \vec n\right) -\vec v(x-\epsilon \vec n))=0$$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface conditions cont'd}
\begin{figure}[h!]
    %\flushright
\includegraphics[width=4cm]{skizze.png}
  %\caption{Two fluid domains $\Omega_i$ and interface $\Gamma$ inbetween}
\end{figure}
\begin{itemize}
\item<1->Normal stress is balanced by surface tension
  $$\lim_{\epsilon \to 0}(\textbf{T}_2(x+\epsilon \vec n) - \textbf{T}_1(x-\epsilon \vec n)) \cdot \vec n= 2\sigma \kappa \vec n$$
\end{itemize}
\vspace{-.5cm}
\visible<2->{
  where $\textbf{T}_i$ is the stress tensor $\textbf{T}_i=2\nu_i \rho_i \textbf{S}_i -p \textbf{Id}$ and $\kappa$ is the curvature of the interface $\nabla \cdot \vec n$. $\textbf{S} = \frac{1}{2}(\partial_{x_i} v_j+\partial_{x_j}  v_i)$
}
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
The interface between fluid phases is captured by a Level-Set Method.

I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
It holds
$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0$$
%todo benefits erklaeren
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian

Interface properties (curvature, normal) are obtained from discrete level-set function by weighted least-squares method.
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Hydrodynamics are solved by LBM.

<Coupling und BC's erklären!!\ldots>
\end{frame}

\section{Results}
\begin{frame}
\frametitle{Validation}
\framesubtitle{Validation setups}
\end{frame}

\section{Outlook}
\begin{frame}
\frametitle{Conclusion \& Outlook}
$\rightarrow$ \dots

\vspace{.8cm}
Outlook:
\begin{itemize}
\item<1-> Include thermal flow (simulate e.g. lava lamp)
\item<2-> \dots
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{References}
\begin{thebibliography}{etw}
   \bibitem{thoemmes}
     Thömmes, Guido, et al. "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method." Journal of Computational Physics 228.4 (2009): 1139-1156
\end{thebibliography}
\end{frame}

\end{document}

### 2015-08-06 code/main.m

@@ -4,12 +4,12 @@
 t_end = 5; % [s]
 x_len = 1; % [m]
 y_len = 1; % [m]
-lidVel = 0.3; % [m/s]
-visc  = 1e-3;% [m^2/s]
+lidVel = 50; % [m/s]
+visc  = 1e-6;% [m^2/s]
 
 g=Grid;
-g.dx=0.05; % [m]
-g.dt=0.05; % [s]
+g.dx=0.1; % [m]
+g.dt=0.00005; % [s]
 g.c_s=sqrt(1/3); % [m/s]
 g.lidVel = [lidVel*g.dt/g.dx; 0];
 g.omega = 1/(visc/(g.c_s^2*g.dt) + 1/2);

### 2015-08-12 code/Cell.m
Performance optimiert.. Objektorientierung ist quatsch..

@@ -1,99 +1,0 @@
-classdef Cell < handle
-  properties
-    % D2Q9; Indexing:
-    % 9   2   3
-    %     ^
-    % 8 < 1 > 4
-    %     v
-    % 7   6   5
-    %
-    %   ^
-    % y |__>
-    %     x
-
-    pdfs    = [ 0,      0,     0,     0,      0,      0,      0,      0,      0];
-    pdfs_new= [ 0,      0,     0,     0,      0,      0,      0,      0,      0];
-    type;
-  end
-  methods
-    function stream(obj, g, x, y)
-      if (obj.type ~= celltype.Regular)
-        return
-      end
-
-      for i=1:9
-        g.cells(x + g.c(1,i), y + g.c(2,i)).pdfs_new(i) = obj.pdfs(i);
-      end
-    end
-
-    function boundaryHandling(obj, g, x, y)
-      switch (obj.type)
-        case celltype.EastSolid
-          g.cells(x-1, y  ).pdfs_new(8) = obj.pdfs_new(4);
-          g.cells(x-1, y-1).pdfs_new(7) = obj.pdfs_new(3);
-          g.cells(x-1, y+1).pdfs_new(9) = obj.pdfs_new(5);
-        case celltype.EastPeriodic
-          g.cells(2, y).pdfs_new(4)     = obj.pdfs_new(4);
-          if (y>2)
-            g.cells(2, y).pdfs_new(3)     = obj.pdfs_new(3);
-          end
-          if (y<g.ny-1)
-            g.cells(2, y).pdfs_new(5)     = obj.pdfs_new(5);
-          end
-        case celltype.WestSolid
-          g.cells(x+1, y  ).pdfs_new(4) = obj.pdfs_new(8);
-          g.cells(x+1, y-1).pdfs_new(5) = obj.pdfs_new(9);
-          g.cells(x+1, y+1).pdfs_new(3) = obj.pdfs_new(7);
-        case celltype.WestPeriodic
-          g.cells(g.nx-1, y).pdfs_new(8) = obj.pdfs_new(8);
-          if (y>2)
-            g.cells(g.nx-1, y).pdfs_new(9) = obj.pdfs_new(9);
-          end
-          if (y<g.ny-1)
-            g.cells(g.nx-1, y).pdfs_new(7) = obj.pdfs_new(7);
-          end
-        case celltype.SouthSolid
[…]

### 2015-08-12 code/Grid.m

@@ -8,6 +8,8 @@ classdef Grid
     c_s
     lidVel
     cells
+    cells_new
+    type
 
     % D2Q9; Indexing:
     % 9   2   3
@@ -25,5 +27,52 @@ classdef Grid
 
     weights = [ 4/9,   1/9,   1/36,  1/9,   1/36,   1/9,    1/36,    1/9,    1/36];
     c       = [[0;0], [0;1], [1;1], [1;0], [1;-1], [0;-1], [-1;-1], [-1;0], [-1;1]];
+
+  end
+  methods
+    function boundaryHandling(obj, g, x, y) %not working, pass by value issue.........:-X
+      switch (g.type(x,y))
+        case celltype.EastSolid
+          g.cells_new(x-1, y ,8) = obj.cells_new(x,y, 4);
+          g.cells_new(x-1, y-1, 7) = obj.cells_new(x,y, 3);
+          g.cells_new(x-1, y+1, 9) = obj.cells_new(x,y, 5);
+        case celltype.EastPeriodic
+          g.cells_new(2, y, 4)     = obj.cells_new(x,y, 4);
+          if (y>2)
+            g.cells_new(2, y, 3)     = obj.cells_new(x,y, 3);
+          end
+          if (y<g.ny-1)
+            g.cells_new(2, y,5)     = obj.cells_new(x,y, 5);
+          end
+        case celltype.WestSolid
+          g.cells_new(x+1, y  ,4) = obj.cells_new(x,y, 8);
+          g.cells_new(x+1, y-1,5) = obj.cells_new(x,y, 9);
+          g.cells_new(x+1, y+1,3) = obj.cells_new(x,y, 7);
+        case celltype.WestPeriodic
+          g.cells_new(g.nx-1, y,8) = obj.cells_new(x,y,8);
+          if (y>2)
+            g.cells_new(g.nx-1, y,9) = obj.cells_new(x,y,9);
+          end
+          if (y<g.ny-1)
+            g.cells_new(g.nx-1, y,7) = obj.cells_new(x,y,7);
+          end
+        case celltype.SouthSolid
+          g.cells_new(x  , y+1,2) = obj.cells_new(x,y,6);
+          if (x<g.nx)
+            g.cells_new(x+1, y+1,3) = obj.cells_new(x,y,7);
+          end
+          if (x>1)
[…]

### 2015-08-12 code/main.m

@@ -4,87 +4,108 @@
 t_end = 5; % [s]
 x_len = 1; % [m]
 y_len = 1; % [m]
-lidVel = 50; % [m/s]
-visc  = 1e-6;% [m^2/s]
+lidVel = 2; % [m/s]
+visc  = 1e-4;% [m^2/s]
 
 g=Grid;
-g.dx=0.1; % [m]
-g.dt=0.00005; % [s]
+g.dx=0.02; % [m]
+g.dt=0.001; % [s]
 g.c_s=sqrt(1/3); % [m/s]
 g.lidVel = [lidVel*g.dt/g.dx; 0];
 g.omega = 1/(visc/(g.c_s^2*g.dt) + 1/2);
 g.nx = x_len/g.dx + 2; %Ghost layer
 g.ny = y_len/g.dx + 2; %Ghost layer
-g.cells = Cell;
+g.type=celltype.Regular;
 
 %init
-for x=1:g.nx
-  for y=1:g.ny
-    g.cells(x, y) = Cell;
-
-    g.cells(x,y).type = celltype.Regular;
-    g.cells(x,y).pdfs = g.weights;
-
-    %Below ordering is critical! Do better not touch...
-    if (x == 1)
-      g.cells(x,y).type = celltype.WestPeriodic;
-    end
-    if (x == g.nx)
-      g.cells(x,y).type = celltype.EastPeriodic;    
-    end
-    if (y == 1)
-      g.cells(x,y).type = celltype.SouthSolid;
-    end
-    if (y == g.ny)
-      g.cells(x,y).type = celltype.NorthMovSolid;
-    end
-    
-  end
+g.cells = ones(g.nx,g.ny,9);
+for i=1:9
+  g.cells(:,:,i)=g.weights(i);
 end
 
-densField = ones(g.nx-2,g.ny-2);
-velField_u = zeros(g.nx-2,g.ny-2);
-velField_v = zeros(g.nx-2,g.ny-2);
-
-fig = figure(1);
-set(fig,'Position', [0 0 800 300]);
+g.type([1:g.nx], [1:g.ny]) = celltype.Regular;
 
 %go for it
 for t=1:(t_end/g.dt)
+
+  %stream
+  for i=1:9 
+      g.cells_new(:,:,i) = circshift(g.cells(:,:,i), [g.c(1,i),g.c(2,i),0]); 
+  end
+
+  %ugly boundary handling
   for x=1:g.nx
-    for y=1:g.ny
[…]

### 2015-08-12 Vortrag/folien.tex
Performance optimiert.. Objektorientierung ist quatsch..
ian-mitchel-toolbox heruntergeladen + folien erweitert

@@
 \documentclass[ucs]{beamer}
+\usepackage{etex}
 
@@
 I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
-It holds
-$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0$$
+It holds:
+$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0.$$
 %todo benefits erklaeren
@@
 Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian
+TODO: Quellen als Footnotes + Uebersichtsfolie
 
 Interface properties (curvature, normal) are obtained from discrete level-set function by weighted least-squares method.
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Level Set}
+\begin{itemize}
+\item<1-> The level set equation of Osher and Sethian
+ $$\varphi_t+v \cdot \nabla \varphi = 0$$
+\item<2-> with the level set function $\varphi$
+\item<3-> we will use the signed distance function as level set function and therefore we get
+$$n = \nabla \varphi$$
+$$\kappa = \nabla \varphi$$
+\end{itemize}
 \end{frame}
@@
 <Coupling und BC's erklären!!\ldots>
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Coupling of LBM and level set method}
+\begin{itemize}
+\item<1-> New boundary condition at the interface
+$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
+\end{itemize}
 \end{frame}

### 2015-08-12 ian_mitchell-toolbox/Examples/Basic/convectionDemo.m

@@ -1,0 +1,312 @@
+function [ data, g, data0 ] = convectionDemo(flowType, accuracy, displayType)
+% convectionDemo: demonstrate a simple convective flow field.
+%
+%   [ data, g, data0 ] = convectionDemo(flowType, accuracy, displayType)
+%  
+% This function was originally designed as a script file, so most of the
+%   options can only be modified in the file.
+%
+% For example, edit the file to change the grid dimension, boundary conditions,
+%   flow field parameters, etc.
+%
+% Parameters:
+%
+%   flowType     String to specify type of flow field.
+%                  'constant'    Constant flow field xdot = k (default).
+%                  'linear'      Linear flow field xdot = A x.
+%                  'constantRev' Constant flow field, negate at t_half.
+%                  'linearRev'   Linear flow field, negate at t_half.
+%   accuracy     Controls the order of approximations.
+%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
+%                  'medium'      Use odeCFL2 and upwindFirstENO2.
+%                  'high'        Use odeCFL3 and upwindFirstENO3.
+%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
+%   displayType  String to specify how to display results.
+%                  The specific string depends on the grid dimension;
+%                  look at the helper visualizeLevelSet to see the options
+%                  (optional, default depends on grid dimension).
+%
+%   data         Implicit surface function at t_max.
+%   g            Grid structure on which data was computed.
+%   data0        Implicit surface function at t_0.
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% Ian Mitchell, 2/9/04
+
+%---------------------------------------------------------------------------
+% You will see many executable lines that are commented out.
+%   These are included to show some of the options available; modify
+%   the commenting to modify the behavior.
+  
+%---------------------------------------------------------------------------
[…]

### 2015-08-12 ian_mitchell-toolbox/Examples/Basic/laxFriedrichsDemo.m

@@ -1,0 +1,386 @@
+function [ data, g, data0 ] = ...
+       laxFriedrichsDemo(flowType, initShape, accuracy, dissType, displayType)
+% laxFriedrichsDemo: demonstrate Lax-Friedrichs on a convective flow field.
+%
+% [ data, g, data0 ] = ...
+%      laxFriedrichsDemo(flowType, initShape, accuracy, dissType, displayType)
+%  
+% This function demonstrates how the Lax-Friedrichs HJ term approximation
+%   termLaxFriedrichs could be used to approximate a convective flow field.
+%   In practice the LF approximation adds unnecessary dissipation, and so it
+%   should not be used for purely convective flow fields where the upwind
+%   direction can be easily determined (use termConvection instead).
+%
+% This function was originally designed as a script file, so most of the
+%   options can only be modified in the file.
+%
+% For example, edit the file to change the grid dimension, boundary conditions,
+%   flow field parameters, etc.
+%
+% Parameters (all inputs have defaults):
+%
+%   flowType     String to specify type of flow field.
+%                  'constant'    Constant flow field xdot = k (default).
+%                  'linear'      Linear flow field xdot = A x.
+%   initShape    String to specify what initial surface to use.
+%	   	   'sphere'      A sphere in the appropriate dimension.
+%	 	   'cube'  	 A cube in the appropriate dimension.
+%   accuracy     Controls the order of approximations.
+%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
+%                  'medium'      Use odeCFL2 and upwindFirstENO2.
+%                  'high'        Use odeCFL3 and upwindFirstENO3.
+%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
+%   dissType     Which type of dissipation to use with the LF approximation?
+%                  'global'      Use artificialDissipationGLF.
+%                  'local'       Use artificialDissipationLLF.
+%                  'locallocal'  Use artificialDissipationLLLF.
+%   displayType  String to specify how to display results.
+%                  The specific string depends on the grid dimension;
+%                  look at the helper visualizeLevelSet to see the options
[…]

### 2015-08-12 ian_mitchell-toolbox/Examples/Basic/maskDemo.m

@@ -1,0 +1,350 @@
+function [ data, g, data0 ] = maskDemo(accuracy, displayType)
+% maskDemo: demonstrate the masking process on a convective flow.
+%
+% [ data, g, data0 ] = maskDemo(accuracy, displayType)
+%  
+% This function was originally designed as a script file, so most of the
+%   options can only be modified in the file.
+%
+% For example, edit the file to change the grid dimension, boundary conditions,
+%   flow field parameters, etc.
+%
+% Parameters:
+%
+%   accuracy     Controls the order of approximations.
+%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
+%                  'medium'      Use odeCFL2 and upwindFirstENO2.
+%                  'high'        Use odeCFL3 and upwindFirstENO3.
+%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
+%   displayType  String to specify how to display results.
+%                  The specific string depends on the grid dimension;
+%                  look at the helper visualizeLevelSet to see the options
+%                  (optional, default depends on grid dimension).
+%
+%   data         Implicit surface function at t_max.
+%   g            Grid structure on which data was computed.
+%   data0        Implicit surface function at t_0.
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% Ian Mitchell, 4/11/04
+
+%---------------------------------------------------------------------------
+% You will see many executable lines that are commented out.
+%   These are included to show some of the options available; modify
+%   the commenting to modify the behavior.
+  
+%---------------------------------------------------------------------------
+% Make sure we can see the kernel m-files.
+run('../addPathToKernel');
+
+%---------------------------------------------------------------------------
+% Which of the tasks do you wish to perform?
+doMask = 1;
+doMin = 1;
+
+%---------------------------------------------------------------------------
+% Integration parameters.
+tMax = 1.0;                  % End time.
+plotSteps = 9;               % How many intermediate plots to produce?
[…]

### 2015-08-12 ian_mitchell-toolbox/Examples/Reachability/air3D.m

@@ -1,0 +1,388 @@
+function [ data, g, data0 ] = air3D(accuracy)
+% air3D: demonstrate the 3D aircraft collision avoidance example
+%
+%   [ data, g, data0 ] = air3D(accuracy)
+%  
+% In this example, the target set is a circle at the origin (cylinder in 3D)
+% that represents a collision in relative coordinates between the evader
+% (player a, fixed at the origin facing right) and the pursuer (player b).
+%
+% The relative coordinate dynamics are
+%
+%   \dot x    = -v_a + v_b \cos \psi + a y
+%	  \dot y    = v_b \sin \psi - a x
+%	  \dot \psi = b - a
+%
+% where v_a and v_b are constants, input a is trying to avoid the target
+%	input b is trying to hit the target.
+%
+% For more details, see my PhD thesis, section 3.1.
+%
+% This function was originally designed as a script file, so most of the
+% options can only be modified in the file.  For example, edit the file to
+% change the grid dimension, boundary conditions, aircraft parameters, etc.
+%
+% To get exactly the result from the thesis choose:
+%   targetRadius = 5, velocityA = velocityB = 5, inputA = inputB = +1.
+%
+% Input Parameters:
+%
+%   accuracy: Controls the order of approximations.
+%     'low': Use odeCFL1 and upwindFirstFirst.
+%     'medium': Use odeCFL2 and upwindFirstENO2 (default).
+%     'high': Use odeCFL3 and upwindFirstENO3.
+%     'veryHigh': Use odeCFL3 and upwindFirstWENO5.
+%
+% Output Parameters:
+%
+%   data: Implicit surface function at t_max.
+%
+%   g: Grid structure on which data was computed.
+%
+%   data0: Implicit surface function at t_0.
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% Ian Mitchell, 3/26/04
+% Subversion tags for version control purposes.
+% $Date: 2012-07-04 14:27:00 -0700 (Wed, 04 Jul 2012) $
+% $Id: air3D.m 74 2012-07-04 21:27:00Z mitchell $
+
+%---------------------------------------------------------------------------
+% You will see many executable lines that are commented out.
[…]

### 2015-08-12 ian_mitchell-toolbox/Examples/addPathToKernel.m

@@ -1,0 +1,16 @@
+% Script file that adds the Kernel subdirectories to the path.
+%
+% Call this script before working with the Matlab Level Set Toolbox
+%   (or place it in your startup.m file).
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% Ian Mitchell, 1/13/04
+
+% Proper operation of function handles seems to require an absolute path
+%   (at least for Matlab version 6.5).
+addpath(genpath('c:/cygwin/home/mitchell/Projects/ToolboxLS/Kernel'));
+

### 2015-08-12 ian_mitchell-toolbox/Kernel/BoundaryCondition/addGhostExtrapolate.m

@@ -1,0 +1,104 @@
+function dataOut = addGhostExtrapolate(dataIn, dim, width, ghostData)
+% addGhostExtrapolate: add ghost cells, values extrapolated from bdry nodes.
+%
+%   dataOut = addGhostExtrapolate(dataIn, dim, width, ghostData)
+%
+% Creates ghost cells to manage the boundary conditions for the array dataIn.
+%
+% This m-file fills the ghost cells with data linearly extrapolated
+%   from the grid edge, where the sign of the slope is chosen to make sure the
+%   extrapolation goes away from or towards the zero level set.
+%
+% For implicit surfaces, the extrapolation will typically be away from zero
+%   (the extrapolation should not imply the presence of an implicit surface
+%    beyond the array bounds).
+%
+% Notice that the indexing is shifted by the ghost cell width in output array.
+%   So in 2D with dim == 1, the first data in the original array will be at
+%          dataOut(width+1,1) == dataIn(1,1)
+%
+% parameters:
+%   dataIn	Input data array.
+%   dim		Dimension in which to add ghost cells.
+%   width	Number of ghost cells to add on each side (default = 1).
+%   ghostData	A structure (see below).
+%
+%   dataOut	Output data array.
+%
+% ghostData is a structure containing data specific to this type of
+%   ghost cell.  For this function it contains the field(s)
+%
+%   .towardZero Boolean indicating whether sign of extrapolation should
+%                 be towards or away from the zero level set (default = 0).
+%
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% Ian Mitchell, 5/12/03
+% modified to allow choice of dimension, Ian Mitchell, 5/27/03
+% modified to allow ghostData input structure & renamed, Ian Mitchell, 1/13/04
+
+if(nargin < 3)
+  width = 1;
+end
+
+if((width < 0) || (width > size(dataIn, dim)))
+  error('Illegal width parameter');
+end
+
[…]

### 2015-08-12 ian_mitchell-toolbox/Kernel/BoundaryCondition/addGhostPeriodic.m

@@ -1,0 +1,73 @@
+function dataOut = addGhostPeriodic(dataIn, dim, width, ghostData)
+% addGhostPeriodic: add ghost cells with periodic boundary conditions.
+%
+%   dataOut = addGhostPeriodic(dataIn, dim, width, ghostData)
+%
+% creates ghost cells to manage the boundary conditions for the array dataIn
+%
+% this m-file fills the ghost cells with periodic data
+%   data from the top of the array is put in the bottom ghost cells
+%   data from the bottom of the array is put in the top ghost cells
+%   in 2D for dim == 1
+%          dataOut(1,1)   == dataIn(end+1-width,1)
+%          dataOut(end,1) == dataIn(width, 1)
+%
+% notice that the indexing is shifted by the ghost cell width in output array
+%   so in 2D for dim == 1, the first data in the original array will be at
+%          dataOut(width+1,1) == dataIn(1,1)
+%
+% parameters:
+%   dataIn	input data array
+%   dim		dimension in which to add ghost cells
+%   width	number of ghost cells to add on each side (default = 1)
+%   ghostData	A structure (see below).
+%
+%   dataOut	Output data array.
+%
+% ghostData is a structure containing data specific to this type of
+%   ghost cell.  For this function it is entirely ignored.
+%
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing 
+%   agreement contained in the file LICENSE in the top directory of 
+%   the distribution.
+%
+% created Ian Mitchell, 5/12/03
+% modified to allow choice of dimension, Ian Mitchell, 5/27/03
+% modified to allow ghostData input structure, Ian Mitchell, 1/13/04
+
+if(nargin < 3)
+  width = 1;
+end
+
+if((width < 0) | (width > size(dataIn, dim)))
+  error('Illegal width parameter');
+end
+
+% create cell array with array indices
+dims = ndims(dataIn);
+sizeIn = size(dataIn);
+indicesOut = cell(dims, 1);
+for i = 1 : dims
+  indicesOut{i} = 1:sizeIn(i);
+end
+indicesIn = indicesOut;
+
+% create appropriately sized output array
+sizeOut = sizeIn;
+sizeOut(dim) = sizeOut(dim) + 2 * width;
[…]

### 2015-08-12 ian_mitchell-toolbox/Kernel/ExplicitIntegration/Term/termLaxFriedrichs.m

@@ -1,0 +1,182 @@
+function [ ydot, stepBound, schemeData ] = termLaxFriedrichs(t, y, schemeData)
+% termLaxFriedrichs: approximate H(x,p) term in an HJ PDE with Lax-Friedrichs.
+%
+%   [ ydot, stepBound, schemeData ] = termLaxFriedrichs(t, y, schemeData)
+%
+% Computes a Lax-Friedrichs (LF) approximation of a general Hamilton-Jacobi
+% equation.  Global LF, Local LF, Local Local LF and Stencil LF are
+% implemented by choosing different dissipation functions.  The PDE is:
+%
+%            D_t \phi = -H(x, t, \phi, D_x \phi).
+%
+% Based on methods outlined in O&F, chapter 5.3 and 5.3.1.
+%
+% Input parameters:
+%
+%   t: Time at beginning of timestep.
+%
+%   y: Data array in vector form.
+%
+%   schemeData: A structure (see below).
+%
+% Output parameters:
+%
+%   ydot: Change in the data array, in vector form.
+%
+%   stepBound: CFL bound on timestep for stability.
+%
+%   schemeData: The input structure, possibly modified.
+%
+%
+% schemeData is a structure containing data specific to this type of 
+% term approximation.  For this function it contains the field(s):
+%
+%   .grid: Grid structure (see processGrid.m for details).
+%
+%   .derivFunc: Function handle to upwinded finite difference 
+%   derivative approximation.
+%
+%   .dissFunc: Function handle to LF dissipation calculator.
+%
+%   .hamFunc: Function handle to analytic hamiltonian H(x,p).
+%
+%   .partialFunc: Function handle to extrema of \partial H(x,p) / \partial p.
+%
+% Note that options for derivFunc and dissFunc are provided as part of the
+% level set toolbox, while hamFunc and partialFunc depend on the exact term
+% H(x,p) and are user supplied.  Note also that schemeData may contain
+% addition fields at the user's discretion; for example, fields containing
+% parameters useful to hamFunc or partialFunc.
+%
+%
+% schemeData.hamFunc should have one of the prototypes:
+%
+%         [ hamValue ]             = hamFunc(t, data, deriv, schemeData)
+%
+%         [ hamValue, schemeData ] = hamFunc(t, data, deriv, schemeData)
+%
+% where t and schemeData are passed directly from this function, data = y
+% has been reshaped into its original size, and deriv is a cell vector (of
[…]

### 2015-08-13 Vortrag/folien.tex

--- 2015-08-06 Vortrag/folien.tex
@@
 I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
-It holds
-$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0$$
+It holds:
+$$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0.$$
 %todo benefits erklaeren
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Level Set}
+\begin{itemize}
+\item<1-> The level set equation of Osher and Sethian
+ $$\varphi_t+ \vec v \cdot \nabla \varphi = 0$$
+\item<2-> we will use the signed distance function as level set function and therefore we get
+$$n = \nabla \varphi$$
+$$\kappa = \nabla \varphi$$
+\end{itemize}
 \end{frame}
@@
 Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian
+TODO: Quellen als Footnotes + Uebersichtsfolie
 
@@
 Hydrodynamics are solved by LBM.
+\begin{itemize}
+\item<1-> Interface becomes a new boundary condition for LBM
+$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
+\end{itemize}
+<Coupling und BC's erklären!!\ldots>
+\end{frame}
 
-<Coupling und BC's erklären!!\ldots>
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Algorithm for LBM with level set}
+\begin{itemize}
+\item<1-> Create initial interface
+\item<2-> Run level set method to calculate surface description
+\item<3-> Run LBM for a prescribed number of steps
+\item<4-> Run level set method for the same number of steps
+\item<5-> Repeat till end of simulation
+\end{itemize}
 \end{frame}

### 2015-08-16 Vortrag/folien.tex
kleine Änderungen an den Folien

@@
 It holds:
-$$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0.$$
+$$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0$$
 %todo benefits erklaeren
-\end{frame}
-
-\begin{frame}
-\frametitle{Mathematic foundation}
-\framesubtitle{Level Set}
-\begin{itemize}
-\item<1-> The level set equation of Osher and Sethian
- $$\varphi_t+ \vec v \cdot \nabla \varphi = 0$$
-\item<2-> we will use the signed distance function as level set function and therefore we get
-$$n = \nabla \varphi$$
-$$\kappa = \nabla \varphi$$
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Mathematic foundation}
-\framesubtitle{Interface capturing}
-Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian
-TODO: Quellen als Footnotes + Uebersichtsfolie
-
-Interface properties (curvature, normal) are obtained from discrete level-set function by weighted least-squares method.
 \end{frame}
@@
 $$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
+\item<2-> $\tilde{u}$ is the velocity on the interface along the direction $c_i$
+\item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
 \end{itemize}
+TODO: Bild vom Interface
 <Coupling und BC's erklären!!\ldots>
@@
 \begin{itemize}
-\item<1-> Include thermal flow (simulate e.g. lava lamp)
-\item<2-> \dots
+\item<1-> Add correction term to prevent mass loss
+\item<1-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
+TODO: Quellen als Footnotes + Uebersichtsfolie
+\item<2-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
+\item<3-> \dots
 \end{itemize}

### 2015-08-17 Vortrag/folien.tex
Bisschen Arbeit an den Folien

@@
 =
--\frac{1}{\rho_i}\nabla p + \nu_i \nabla^2 \vec v $$
+-\frac{1}{\varrho_i}\nabla p + \nu_i \nabla^2 \vec v $$
 }
@@
   where $\textbf{T}_i$ is the stress tensor $\textbf{T}_i=2\nu_i \rho_i \textbf{S}_i -p \textbf{Id}$ and $\kappa$ is the curvature of the interface $\nabla \cdot \vec n$.
-$\textbf{S} = \frac{1}{2}(\partial_{x_i} v_j+\partial_{x_j}  v_i)$
+$\textbf{S}_{ij} = \frac{1}{2}(\partial_{i} v_j+\partial_{j}  v_i)$
 }
+\end{frame}
+
+\begin{frame}
+To solve the two-phase problem we need to:
+\begin{itemize}
+\item<1-> solve the flow equations $\rightarrow$ LBM
+\item<2-> compute the motion of the interface $\rightarrow$ level set
+\item<3-> couple the two algorithms
+\end{itemize}
 \end{frame}
@@
 
-I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
+I.e. a \textit{level set function} $\varphi:= \varphi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
 It holds:
@@
 <Coupling und BC's erklären!!\ldots>
+\end{frame}
+
+\begin{frame}
+$\tilde{u}$ is calculated by linear interpolation:
+$$\tilde{u} = q u (x_2,t) + (1-q) u(x_1,t)$$
+$R_i$ consists of several parts:
+$$R_i = 6 h^2 f_{i}^{*} {\Lambda}_i : A$$
+\begin{itemize}
+\item<1-> with:
+$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
+$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(h)$$
+\item<2-> $S^{(k)}$ velocity gradient at $x_k$
+\item<3-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
+\end{itemize}
 \end{frame}

### 2015-08-17 Vortrag/folien.tex
Nochmals Folien. Letztes Update für heute.

@@
 \begin{frame}
-\frametitle{Multiphase flow - Examples}
+\frametitle{Multiphase flow}
+Examples
 \begin{itemize}
-\item<1-> Examples
-\item<2-> e.g. Oil in water 
-\item<3-> \ldots
+\item<1-> Liquid-liquid mixtures (e.g. oil in water) 
+\item<2-> Gas-liquid mixtures (e.g. bubble dynamics)
 \end{itemize}
@@
 \end{itemize}
-TODO: Bild vom Interface
-<Coupling und BC's erklären!!\ldots>
+TODO: Bild vom Interface (sowas wie Fig.1-Right im Paper)
 \end{frame}
@@
 \begin{frame}
+\visible<1->{
 $\tilde{u}$ is calculated by linear interpolation:
 $$\tilde{u} = q u (x_2,t) + (1-q) u(x_1,t)$$
+}
+\visible<2->{
 $R_i$ consists of several parts:
 $$R_i = 6 h^2 f_{i}^{*} {\Lambda}_i : A$$
+}
+\visible<3->{
 \begin{itemize}
-\item<1-> with:
+\item<3-> with:
 $$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
 $$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(h)$$
-\item<2-> $S^{(k)}$ velocity gradient at $x_k$
-\item<3-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
+\item<4-> $S^{(k)}$ velocity gradient at $x_k$
+\item<5-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
 \end{itemize}
+}
 \end{frame}
@@
 \frametitle{Validation}
+TODO: Hier könnte man Bilder von unserer ersten Simulation zeigen. Leider können wir die Richtigkeit bisher nicht mit Zahlen belegen.
 \framesubtitle{Validation setups}
@@
 \begin{frame}
-\frametitle{Conclusion \& Outlook}
-$\rightarrow$ \dots
+\frametitle{Outlook}
+$\rightarrow$ \textit{Conclusion habe ich rausgenommen. Ich wüsste zumindest nicht was wir da reinschreiben könnten. Wenn du was weißt, darfst du das aber sehr gerne wieder einfügen.}
 
@@
 \item<1-> Add correction term to prevent mass loss
-\item<1-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
+\item<2-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
 TODO: Quellen als Footnotes + Uebersichtsfolie
-\item<2-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
-\item<3-> \dots
+\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
 \end{itemize}
@@
      Thömmes, Guido, et al. "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method." Journal of Computational Physics 228.4 (2009): 1139-1156
+   \bibitem{mitchell}
+     Mitchell, Ian, A Toolbox of Level Set Methods
 \end{thebibliography}

### 2015-08-18 Vortrag/folien.tex
Progress on slides

@@
 
-\date{x y, 2015} % Date for the report
+\date{August 20th, 2015} % Date for the report
 
@@
 \end{itemize}
+
+\begin{tabular}{l l}
+\begin{minipage}{0.4\textwidth}
+
+\visible<1->{
+\begin{figure}[h!]
+\includegraphics[width=4cm]{oilwater.jpg}
+\end{figure}
+}
+\end{minipage}
+&
+\begin{minipage}{0.6\textwidth}
+\visible<2->{
+\begin{figure}[h!]
+  \includegraphics[width=5.5cm]{bubbles.jpg}
+\end{figure}
+}
+\end{minipage}
+\end{tabular}
+
 \end{frame}
@@
 \item<1-> Velocity across interface is $C_0$-continous 
-  $$\lim_{\epsilon \to 0}(\vec v\left(x+\epsilon \vec n\right) -\vec v(x-\epsilon \vec n))=0$$
+  $$[v] = \lim_{\epsilon \to 0}(\vec v\left(x+\epsilon \vec n\right) -\vec v(x-\epsilon \vec n))=0$$
 \end{itemize}
@@
 \framesubtitle{Interface conditions cont'd}
+\vspace{-.5cm}
 \begin{figure}[h!]
@@
 \end{figure}
+\vspace{-.5cm}
 \begin{itemize}
-\item<1->Normal stress is balanced by surface tension
-  $$\lim_{\epsilon \to 0}(\textbf{T}_2(x+\epsilon \vec n) - \textbf{T}_1(x-\epsilon \vec n)) \cdot \vec n= 2\sigma \kappa \vec n$$
+\item<1->Normal stress is balanced by surface tension $\rightarrow$ pressure jump
+  $$[T] \cdot \vec n= \lim_{\epsilon \to 0}(\textbf{T}_2(x+\epsilon \vec n) - \textbf{T}_1(x-\epsilon \vec n)) \cdot \vec n= 2\sigma \kappa \vec n$$
 \end{itemize}
@@
 \visible<2->{
-  where $\textbf{T}_i$ is the stress tensor $\textbf{T}_i=2\nu_i \rho_i \textbf{S}_i -p \textbf{Id}$ and $\kappa$ is the curvature of the interface $\nabla \cdot \vec n$.
-$\textbf{S}_{ij} = \frac{1}{2}(\partial_{i} v_j+\partial_{j}  v_i)$
+  where $\textbf{T}_i$ is the stress tensor $\textbf{T}_i=2\nu_i \rho_i \textbf{S}_i -p \mathbb{I}$ and $\kappa$ is the curvature of the interface $\nabla \cdot \vec n$.
+$\textbf{S}_{ij} = \frac{1}{2}(\partial_{i} v_j+\partial_{j}  v_i)$.
 }
@@
 \item<1-> solve the flow equations $\rightarrow$ LBM
-\item<2-> compute the motion of the interface $\rightarrow$ level set
-\item<3-> couple the two algorithms
+\item<2-> compute the motion of the interface $\rightarrow$ Level Set Method
+\item<3-> couple the two algorithms $\rightarrow$ according BC's % Fuers coupling muessen ja eigentlich nur eine spezielle LBM-Randbehandlung am Interface gemacht werden, und fuer Coupling in die anderere Richtung halt die Geschwindigkeit interpoliert werden
 \end{itemize}
@@
 The interface between fluid phases is captured by a Level-Set Method. 
-
-I.e. a \textit{level set function} $\varphi:= \varphi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
+I.e. a \textit{level set function} $\varphi:= \varphi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given (implicitly) by the zero-isosurface of this function.
 It holds:
 $$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0$$
-%todo benefits erklaeren
+where $\vec v$ is the velocity at the interface, given by NSE.
+
+Benefit of Level-Set Method:
+\begin{itemize}
+\item<2-> Implicit surface description eases bubble coalescence/breakup in code
+\item<3-> High density and viscosity ratios ($>10^3$) possible for simulation
+\end{itemize}
 \end{frame}
@@
 \frametitle{Mathematic foundation}
-\framesubtitle{Interface capturing}
-Hydrodynamics are solved by LBM.
+\framesubtitle{Interface implementation (Methods Coupling)}
+Hydrodynamics are solved by LBM (D2Q9, SRT for our first test)
 \begin{itemize}
 \item<1-> Interface becomes a new boundary condition for LBM
-$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
-\item<2-> $\tilde{u}$ is the velocity on the interface along the direction $c_i$
+$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6 \Delta x f_{i}^{*}c_i \cdot \tilde{v} + R_i$$
+\item<2-> $\tilde{v}$ is the velocity on the interface along the direction $c_i$
+\end{itemize}
+\begin{tabular}{l l}
+\hspace{-.35cm} \begin{minipage}{0.6\textwidth}
+\visible<1->{
+\begin{itemize}
 \item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
 \end{itemize}
-TODO: Bild vom Interface (sowas wie Fig.1-Right im Paper)
+}
+\end{minipage}
+&
+\begin{minipage}{0.4\textwidth}
+\begin{figure}[h!]
+\includegraphics[width=3cm]{skizze2.png}
+\end{figure}
+\end{minipage}
+\end{tabular}
 \end{frame}
@@
 \visible<1->{
-$\tilde{u}$ is calculated by linear interpolation:
-$$\tilde{u} = q u (x_2,t) + (1-q) u(x_1,t)$$
+$\tilde{v}$ is calculated by linear interpolation:
+$$\tilde{v} = q v (x_2,t) + (1-q) v(x_1,t)$$
 }
@@
 $R_i$ consists of several parts:
-$$R_i = 6 h^2 f_{i}^{*} {\Lambda}_i : A$$
+$$R_i = 6 \Delta x^2 f_{i}^{*} {\Lambda}_i : A$$
 }
@@
 $$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
-$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(h)$$
+$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(\Delta x)$$
 \item<4-> $S^{(k)}$ velocity gradient at $x_k$
-\item<5-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
+\item<5-> $[S] = \lim_{\epsilon \to 0}(S(x+\epsilon \vec n) -S(x-\epsilon \vec n))$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
 \end{itemize}

### 2015-08-18 ian_mitchell-toolbox/lbm/addPathToKernel.m

@@ -12,5 +12,5 @@
 
 % Proper operation of function handles seems to require an absolute path
 %   (at least for Matlab version 6.5).
-addpath(genpath('C:\Users\Public\Documents\Studium\Master\BGCE\Projekt\multi-lbm\ian_mitchell-toolbox\Kernel'));
+addpath(genpath('/Users/lorenzhufnagel/Desktop/uni/BGCE_Proj/multi-lbm/ian_mitchell-toolbox/Kernel'));
 

### 2015-08-19 Vortrag/folien.tex
Slides..

@@
 \end{tabular}
-
 \end{frame}
@@
 $$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0$$
-where $\vec v$ is the velocity at the interface, given by NSE.
+where $\vec v$ is the velocity at the interface; given by NSE.
 
@@
 \framesubtitle{Interface implementation (Methods Coupling)}
-Hydrodynamics are solved by LBM (D2Q9, SRT for our first test)
+Hydrodynamics are solved by LBM (Stream-Collide, D2Q9, SRT for our first test)
 \begin{itemize}
@@
   $$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6 \Delta x f_{i}^{*}c_i \cdot \tilde{v} + R_i$$
-\item<2-> $\tilde{v}$ is the velocity on the interface along the direction $c_i$
 \end{itemize}
 \begin{tabular}{l l}
-\hspace{-.35cm} \begin{minipage}{0.6\textwidth}
+\hspace{-.35cm} \begin{minipage}{0.65\textwidth}
 \visible<1->{
 \begin{itemize}
+\item<2-> $\tilde{v}$ is the velocity on the interface along the direction $c_i$
 \item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
@@
 &
-\begin{minipage}{0.4\textwidth}
+\hspace{-.5cm} \begin{minipage}{0.4\textwidth}
 \begin{figure}[h!]
@@
 \item<3-> Run LBM for a prescribed number of steps
-\item<4-> Run level set method for the same number of steps
-\item<5-> Repeat till end of simulation
+\item<4-> Run level set method for the same time interval
+\item<5-> Repeat until end of simulation
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Validation}
-TODO: Hier könnte man Bilder von unserer ersten Simulation zeigen. Leider können wir die Richtigkeit bisher nicht mit Zahlen belegen.
-\framesubtitle{Validation setups}
+\frametitle{Results}
+\framesubtitle{Setup}
+Transient couette flow with immersed drop.
+\begin{tabular}{l l}
+\begin{minipage}{0.5\textwidth}
+
+\begin{figure}[h!]
+\includegraphics[width=7cm]{plots/vel0.png}
+\end{figure}
+\end{minipage}
+&
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[h!]
+  \includegraphics[width=4cm]{plots/interface_t0.png}
+\end{figure}
+\end{minipage}
+\end{tabular}
+\end{frame}
+
+\begin{frame}
+
+\begin{tabular}{l l}
+\begin{minipage}{0.5\textwidth}
+
+\begin{figure}[h!]
+\includegraphics[width=7cm]{plots/vel4.png}
+\end{figure}
+\end{minipage}
+&
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[h!]
+  \includegraphics[width=4cm]{plots/interface_t4.png}
+\end{figure}
+\end{minipage}
+\end{tabular}
+
+\end{frame}
+
+\begin{frame}
+\begin{tabular}{l l}
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[h!]
+\includegraphics[width=7cm]{plots/vel10.png}
+\end{figure}
+\end{minipage}
+&
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[h!]
+  \includegraphics[width=4cm]{plots/interface_t10.png}
+\end{figure}
+\end{minipage}
+\end{tabular}
+\dots more to come 
 \end{frame}
@@
 \frametitle{Outlook}
-$\rightarrow$ \textit{Conclusion habe ich rausgenommen. Ich wüsste zumindest nicht was wir da reinschreiben könnten. Wenn du was weißt, darfst du das aber sehr gerne wieder einfügen.}
+\textit{\dots so far intermediate results}
 
@@
 \item<2-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
-TODO: Quellen als Footnotes + Uebersichtsfolie
-\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
+\item<3-> $\rightarrow$ \dots ?
+%TODO: Quellen als Footnotes + Uebersichtsfolie
+%\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
 \end{itemize}
@@
      Thömmes, Guido, et al. "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method." Journal of Computational Physics 228.4 (2009): 1139-1156
+     \bibitem{adalseth}
+     D. Adalsteinsson, and J. A. Sethian. A fast level set method for propagating interfaces. J. Comput. Phys., 118(2):269-277, 1995
    \bibitem{mitchell}

### 2015-08-19 Vortrag/folien.tex
Folien

@@
 $$
-\nabla \cdot  \vec v = 0
+\nabla \cdot  \vec v_i = 0 \text{  in } \Omega_i
 $$
 $$
-\frac{\partial \vec v}{\partial t} + \left(\vec  v \cdot \nabla \right) \vec v
+\frac{\partial \vec v_i}{\partial t} + \left(\vec  v _i\cdot \nabla \right) \vec v_i
 =
--\frac{1}{\varrho_i}\nabla p + \nu_i \nabla^2 \vec v $$
+-\frac{1}{\varrho_i}\nabla p_i + \nu_i \nabla^2 \vec v_i \text{  in } \Omega_i
+$$
 }
@@
 $$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
-$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(\Delta x)$$
+$$ A = -q(1-q)[S] - (q - 1/2) S^{2}$$
 \item<4-> $S^{(k)}$ velocity gradient at $x_k$
@@
 \begin{itemize}
-\item<1-> Add correction term to prevent mass loss
-\item<2-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
-\item<3-> $\rightarrow$ \dots ?
+\item<1-> Create more examples
+\item<2-> Add correction term to prevent mass loss
+\item<3-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
 %TODO: Quellen als Footnotes + Uebersichtsfolie

### 2015-08-19 Vortrag/folien.tex
noch einmal Folien...

@@
 \begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Solvers for the two-phase problem}
+\begin{itemize}
+\item<1-> Colour gradient method of Gunstensen and Rothman
+\begin{itemize}
+\item only for small density and viscosity differences
+\end{itemize}
+\item<2-> Method of Shan and Chen
+\begin{itemize}
+\item models miscible fluids
+\item immiscible flows only approximatly
+\end{itemize}
+\item<3-> Free surface methods
+\begin{itemize}
+\item only for big density and viscosity differences
+\end{itemize}
+\item<4-> Method of Thoemmes and Becker
+\begin{itemize}
+\item using Level Set Method for interface motion
+\item small and big density/viscosity differences possible
+\item mass loss in Level Set Method
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Ingredients for solver with Level Set Method}
 To solve the two-phase problem we need to:
@@
 \frametitle{Mathematic foundation}
+\framesubtitle{LBM}
+\begin{itemize}
+\item<1-> Stream
+$$f_i(x+c_i,t+1) = f_i(x,t) - \frac{1}{\tau}(f_i - f_i^{eq}) + G_i$$
+\item<2-> Collide (Bhatnagar-Gross-Krook approximation)
+$$f_i^{eq}(\rho,v) = f_i^{*}(\rho + 3c_i \cdot v + \frac{9}{2}(c_i \cdot v)^2 - \frac{3}{2}v^2)$$
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{LBM}
+the corresponding D2Q9 weight factors
+\begin{figure}[h!]
+    %\flushright
+\includegraphics[width=3cm]{tutorial_basics03_d2q9.png}
+\end{figure}
+$$f_i^* = \begin{cases} \frac49 & i = C \\ \frac19 & i = N,E,S,W \\ \frac{1}{36} &  i = NE,SE,SW,NW \end{cases}$$
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{LBM}
+we can compute for
+\begin{itemize}
+\item Density
+$$\rho(x,t) = \sum f_i(x,t)$$
+\item Velocity
+$$u = \sum f_i(x,t)c_i$$
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Mathematic foundation}
 \framesubtitle{Interface capturing}
-The interface between fluid phases is captured by a Level-Set Method. 
-I.e. a \textit{level set function} $\varphi:= \varphi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given (implicitly) by the zero-isosurface of this function.
-It holds:
+\visible<1->{Interface between fluid phases is captured by level set method}
+\visible<2->{
+\begin{itemize}
+\item<2-> Level set function: $\varphi:= \varphi(x,t) \rightarrow \mathbb{R}$
+
+Interface is the zero-isosurface of this function
+\item<3-> Level set equation:
 $$ \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0$$
-where $\vec v$ is the velocity at the interface; given by NSE.
+where $\vec v$ is the velocity at the interface, given by NSE.
+\end{itemize}
+}
+\end{frame}
 
-Benefit of Level-Set Method:
+\begin{frame}
+\frametitle{Mathematic foundation}
+\framesubtitle{Interface capturing}
+Benefits of Level-Set Method:
 \begin{itemize}
@@
 \item<2-> $\tilde{v}$ is the velocity on the interface along the direction $c_i$
-\item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
+\item<3-> calculated by linear interpolation:
+$$\tilde{v} = q v (x_2,t) + (1-q) v(x_1,t)$$
 \end{itemize}
@@
 \begin{frame}
-\visible<1->{
-$\tilde{v}$ is calculated by linear interpolation:
-$$\tilde{v} = q v (x_2,t) + (1-q) v(x_1,t)$$
-}
-\visible<2->{
-$R_i$ consists of several parts:
-$$R_i = 6 \Delta x^2 f_{i}^{*} {\Lambda}_i : A$$
-}
-\visible<3->{
+\frametitle{Mathematic foundation}
+\framesubtitle{Interface implementation (Methods Coupling)}
+$R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment.
 \begin{itemize}
-\item<3-> with:
-$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
-$$ A = -q(1-q)[S] - (q - 1/2) S^{2}$$
-\item<4-> $S^{(k)}$ velocity gradient at $x_k$
-\item<5-> $[S] = \lim_{\epsilon \to 0}(S(x+\epsilon \vec n) -S(x-\epsilon \vec n))$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
+\item<1-> $R_i = 6 \Delta x^2 f_{i}^{*} {\Lambda}_i : A$,
+
+with $A : B = \sum_{i,j} A_{ij}B_{ij}$.
+\item<2->
+$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$ ,
+
+with $c_i \otimes c_i = c_i c_i^T$.
+
+\item<3->{$ A = -q(1-q)[S] - (q - 1/2) S^{(k)}$
+\begin{itemize}
+\item<3-> $S^{(k)}$ velocity gradient at $x_k$
+\item<4-> $[S]$ jump of velocity gradient at the interface. Depends on $\vec n$, $\vec t$ and $\kappa$.
 \end{itemize}
 }
+\end{itemize}
 \end{frame}
@@
 \frametitle{Results}
+\framesubtitle{Implementation}
+\begin{itemize}
+\item<1-> Implementation in Matlab
+\item<2-> Own LBM-solver
+\item<3-> Level set method solved by Toolbox of Ian Mitchell
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Results}
 \framesubtitle{Setup}
-Transient couette flow with immersed drop.
+\begin{itemize}
+\item<1-> Transient couette flow with immersed drop
+\item<2-> Fluids have the same $\rho_i, \nu_i \rightarrow [S]$ vanishes
+\item<3-> Goal: See interactions at the interface
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Results}
+\framesubtitle{Simulation}
 \begin{tabular}{l l}
@@
 \begin{frame}
-
+\frametitle{Results}
+\framesubtitle{Simulation}
 \begin{tabular}{l l}
@@
 \begin{frame}
+\frametitle{Results}
+\framesubtitle{Simulation}
 \begin{tabular}{l l}
@@
 \end{tabular}
-\dots more to come 
 \end{frame}

### 2015-10-29 Paper/scifile.tex
Stylesheet für das Paper. Inhaltlich bitte noch nicht ernst nehmen.

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{Implementation of a lattice Boltzman method for immiscible multiphase flow simulations using the level set method}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{Lorenz Hufnagel,$^{1}$ Daniel Zint,$^{1}$\\
\\
\normalsize{$^{1}$Chair for System-Simulation, Friedrich Alexander Univerität Erlangen-Nürnberg}\\
\normalsize{91058 Erlangen, Germany}\\ % ist das so richtig?
\\
%\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
  We implemented the lattice Boltzman method for immiscible multiphase flow simulations. We combined this with the level set method according to the paper of G. Thömmes FUSSNOTE. After reimplementing the testcases mentioned in the paper, we studied the coupling of the two methods and the impact of the variables.
\end{sciabstract}

\section{Introduction}

\section{Numerical Methods}

\subsection{The Lattice Boltzmann Method}

\subsection{The Level Set Method}

\section{something new what we did / Results}

\section{Conclusion}

\newpage
Hier folgen Informationen über das Stylesheet. Sollten wir dann irgendwann loeschen, fand ich aber fuers erste ganz hilfreich.

% In setting up this template for *Science* papers, we've used both
% the \section* command and the \paragraph* command for topical
% divisions.  Which you use will of course depend on the type of paper
% you're writing.  Review Articles tend to have displayed headings, for
% which \section* is more appropriate; Research Articles, when they have
% formal topical divisions at all, tend to signal them with bold text
% that runs into the paragraph, for which \paragraph* is the right
% choice.  Either way, use the asterisk (*) modifier, as shown, to
% suppress numbering.

\section*{Introduction}

In this file, we present some tips and sample mark-up to assure your
\LaTeX\ file of the smoothest possible journey from review manuscript
to published {\it Science\/} paper.  We focus here particularly on
issues related to style files, citation, and math, tables, and
figures, as those tend to be the biggest sticking points.  Please use
the source file for this document, \texttt{scifile.tex}, as a template
for your manuscript, cutting and pasting your content into the file at
the appropriate places.

{\it Science\/}'s publication workflow relies on Microsoft Word.  To
translate \LaTeX\ files into Word, we use an intermediate MS-DOS
routine \cite{tth} that converts the \TeX\ source into HTML\@.  The
routine is generally robust, but it works best if the source document
is clean \LaTeX\ without a significant freight of local macros or
\texttt{.sty} files.  Use of the source file \texttt{scifile.tex} as a
template, and calling {\it only\/} the \texttt{.sty} and \texttt{.bst}
files specifically mentioned here, will generate a manuscript that
should be eminently reviewable, and yet will allow your paper to
proceed quickly into our production flow upon acceptance \cite{use2e}.

\section*{Formatting Citations}

Citations can be handled in one of three ways.  The most
straightforward (albeit labor-intensive) would be to hardwire your
citations into your \LaTeX\ source, as you would if you were using an
ordinary word processor.  Thus, your code might look something like
this:

\begin{quote}
\begin{verbatim}
However, this record of the solar nebula may have been
partly erased by the complex history of the meteorite
parent bodies, which includes collision-induced shock,
thermal metamorphism, and aqueous alteration
({\it 1, 2, 5--7\/}).
\end{verbatim}
\end{quote}

\noindent Compiled, the last two lines of the code above, of course, would give notecalls in {\it Science\/} style:

\begin{quote}
\ldots thermal metamorphism, and aqueous alteration ({\it 1, 2, 5--7\/}).
\end{quote}

Under the same logic, the author could set up his or her reference list as a simple enumeration,

\begin{quote}
\begin{verbatim}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei
and Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ 
Physik\/} {\bf 56}, 1 (1929).
\end{enumerate}
\end{verbatim}
\end{quote}

\noindent yielding

\begin{quote}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei and
Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ Physik} {\bf 56},
1 (1929).
\end{enumerate}
\end{quote}

That's not a solution that's likely to appeal to everyone, however ---
especially not to users of B{\small{IB}}\TeX\ \cite{inclme}.  If you
are a B{\small{IB}}\TeX\ user, we suggest that you use the
\texttt{Science.bst} bibliography style file and the
\texttt{scicite.sty} package, both of which we are downloadable from our author help site
(http://www.sciencemag.org/about/authors/prep/TeX\_help/).  You can also
generate your reference lists by using the list environment
\texttt{\{thebibliography\}} at the end of your source document; here
again, you may find the \texttt{scicite.sty} file useful.

Whether you use B{\small{IB}}\TeX\ or \texttt{\{thebibliography\}}, be
very careful about how you set up your in-text reference calls and
notecalls.  In particular, observe the following requirements:

\begin{enumerate}
\item Please follow the style for references outlined at our author
  help site and embodied in recent issues of {\it Science}.  Each
  citation number should refer to a single reference; please do not
  concatenate several references under a single number.
\item Please cite your references and notes in text {\it only\/} using
  the standard \LaTeX\ \verb+\cite+ command, not another command
  driven by outside macros.
\item Please separate multiple citations within a single \verb+\cite+
  command using commas only; there should be {\it no space\/}
  between reference keynames.  That is, if you are citing two
  papers whose bibliography keys are \texttt{keyname1} and
  \texttt{keyname2}, the in-text cite should read
  \verb+\cite{keyname1,keyname2}+, {\it not\/}
  \verb+\cite{keyname1, keyname2}+.
\end{enumerate}

\noindent Failure to follow these guidelines could lead
to the omission of the references in an accepted paper when the source
file is translated to Word via HTML.

\section*{Handling Math, Tables, and Figures}

Following are a few things to keep in mind in coding equations,
tables, and figures for submission to {\it Science}.

\paragraph*{In-line math.}  The utility that we use for converting
from \LaTeX\ to HTML handles in-line math relatively well.  It is best
to avoid using built-up fractions in in-line equations, and going for
the more boring ``slash'' presentation whenever possible --- that is,
for \verb+$a/b$+ (which comes out as $a/b$) rather than
\verb+$\frac{a}{b}$+ (which compiles as $\frac{a}{b}$).  Likewise,
HTML isn't tooled to handle certain overaccented special characters
in-line; for $\hat{\alpha}$ (coded \verb+$\hat{\alpha}$+), for
example, the HTML translation code will return [\^{}$(\alpha)$].
Don't drive yourself crazy --- but if it's possible to avoid such
constructs, please do so.  Please do not code arrays or matrices as
in-line math; display them instead.  And please keep your coding as
\TeX-y as possible --- avoid using specialized math macro packages
like \texttt{amstex.sty}.

\paragraph*{Displayed math.} Our HTML converter sets up \TeX\
displayed equations using nested HTML tables.  That works well for an
HTML presentation, but Word chokes when it comes across a nested
table in an HTML file.  We surmount that problem by simply cutting the
displayed equations out of the HTML before it's imported into Word,
and then replacing them in the Word document using either images or
equations generated by a Word equation editor.  Strictly speaking,
this procedure doesn't bear on how you should prepare your manuscript
--- although, for reasons best consigned to a note \cite{nattex}, we'd
prefer that you use native \TeX\ commands within displayed-math
environments, rather than \LaTeX\ sub-environments.

\paragraph*{Tables.}  The HTML converter that we use seems to handle
reasonably well simple tables generated using the \LaTeX\
\texttt{\{tabular\}} environment.  For very complicated tables, you
may want to consider generating them in a word processing program and
including them as a separate file.

\paragraph*{Figures.}  Figure callouts within the text should not be
in the form of \LaTeX\ references, but should simply be typed in ---
that is, \verb+(Fig. 1)+ rather than \verb+\ref{fig1}+.  For the
figures themselves, treatment can differ depending on whether the
manuscript is an initial submission or a final revision for acceptance
and publication.  For an initial submission and review copy, you can
use the \LaTeX\ \verb+{figure}+ environment and the
\verb+\includegraphics+ command to include your PostScript figures at
the end of the compiled PostScript file.  For the final revision,
however, the \verb+{figure}+ environment should {\it not\/} be used;
instead, the figure captions themselves should be typed in as regular
text at the end of the source file (an example is included here), and
the figures should be uploaded separately according to the Art
Department's instructions.

\section*{What to Send In}

What you should send to {\it Science\/} will depend on the stage your manuscript is in:

\begin{itemize}
\item {\bf Important:} If you're sending in the initial submission of
  your manuscript (that is, the copy for evaluation and peer review),
  please send in {\it only\/} a PostScript or PDF version of the
  compiled file (including figures).  Please do not send in the \TeX\ 
  source, \texttt{.sty}, \texttt{.bbl}, or other associated files with
  your initial submission.  (For more information, please see the
  instructions at our Web submission site,
  http://www.submit2science.org/ .)
\item When the time comes for you to send in your revised final
  manuscript (i.e., after peer review), we require that you include
  all source files and generated files in your upload.  Thus, if the
  name of your main source document is \texttt{ltxfile.tex}, you
  need to include:
\begin{itemize}
\item \texttt{ltxfile.tex}.
\item \texttt{ltxfile.aux}, the auxilliary file generated by the
  compilation.
\item A PostScript file (compiled using \texttt{dvips} or some other
  driver) of the \texttt{.dvi} file generated from
  \texttt{ltxfile.tex}, or a PDF file distilled from that
  PostScript.  You do not need to include the actual \texttt{.dvi}
  file in your upload.
\item From B{\small{IB}}\TeX\ users, your bibliography (\texttt{.bib})
  file, {\it and\/} the generated file \texttt{ltxfile.bbl} created
  when you run B{\small{IB}}\TeX.
\item Any additional \texttt{.sty} and \texttt{.bst} files called by
  the source code (though, for reasons noted earlier, we {\it
    strongly\/} discourage the use of such files beyond those
  mentioned in this document).
\end{itemize}
\end{itemize}

% Your references go at the end of the main text, and before the
% figures.  For this document we've used BibTeX, the .bib file
% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
% was included to format the reference numbers according to *Science*
% style.

\bibliography{scibib}

\bibliographystyle{Science}

% Following is a new environment, {scilastnote}, that's defined in the
% preamble and that allows authors to add a reference at the end of the
% list that's not signaled in the text; such references are used in
% *Science* for acknowledgments of funding, help, etc.

\begin{scilastnote}
\item We've included in the template file \texttt{scifile.tex} a new
environment, \texttt{\{scilastnote\}}, that generates a numbered final
citation without a corresponding signal in the text.  This environment
can be used to generate a final numbered reference containing
acknowledgments, sources of funding, and the like, per {\it Science\/}
style.
\end{scilastnote}

% For your review copy (i.e., the file you initially send in for
% evaluation), you can use the {figure} environment and the
% \includegraphics command to stream your figures into the text, placing
% all figures at the end.  For the final, revised manuscript for
% acceptance and production, however, PostScript or other graphics
% should not be streamed into your compliled file.  Instead, set
% captions as simple paragraphs (with a \noindent tag), setting them
% off from the rest of the text with a \clearpage as shown  below, and
% submit figures as separate files according to the Art Department's
% instructions.

\clearpage

\noindent {\bf Fig. 1.} Please do not use figure environments to set
up your figures in the final (post-peer-review) draft, do not include graphics in your
source code, and do not cite figures in the text using \LaTeX\
\verb+\ref+ commands.  Instead, simply refer to the figure numbers in
the text per {\it Science\/} style, and include the list of captions at
the end of the document, coded as ordinary paragraphs as shown in the
\texttt{scifile.tex} template file.  Your actual figure files should
be submitted separately.

\end{document}

### 2015-11-02 Paper/cover_letter.tex
Cover Letter - Erster Entwurf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{SIAM \\
3600 Market Street, 6th Floor \\
Philadelphia, PA 19104-2688 USA}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Lorenz Hufnagel, Daniel Zint \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Chair for System-Simulation \\ 
Friedrich Alexander Universit\"at Erlangen-N\"urnberg \\ 
91058 Erlangen, Germany \\
lorenz.hufnagel@studium.uni-erlangen.de, daniel.zint@fau.de
\end{center} 
\vfill

\signature{Lorenz Hufnagel, Daniel Zint} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Sir or Madam,}

% Der Stil und der Inhalt richten sich nach dem was ich auf Google zu dem Thema gefunden habe. Ob dies tatsächlich so richtig ist, sollten wir aber nochmal absegnen lassen.

% The first paragraph introduces the writer, and follows the basic format of the intro para of the job cover letter described in this post (ie, field, Ph.D. institution and year, current institutional affiliation and status, and general focus of work). It then states that the writer is submitting a manuscript for review.

We are students of the Bavarian Graduate School of Computational Engineering. We are both students at the Friedrich Alexander Universit\"at Erlangen-N\"urnberg and participate in the program Computational Engineering. Whereas L. Hufnagel also did his Bachelors in Computational Engineering, D. Zint did Mechatronics in his Bachelors.

% The second paragraph covers the topic of the manuscript. This will be a crisp 4-5 sentences that will give a title and describe the topic, the specific material/data covered, the theoretical orientation or approach, any special issues of methodology if important, and, most importantly, the core argument.

One part of our program of study is a project. Our task was to reimplement the algorithm described in the paper "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method" of G. Th\"ommes. Furthermore, we did some parameter studies on the algorithm. The method described in the paper uses the lattice Boltzmann method to simulate the flow field of the fluids and the level set method to compute the movement of the interface between the different fluids. It couples the two methods by creating a new boundary condition for the interface in the lattice Boltzmann method. We took a closer look at this coupling and examined possibilities to optimize the code by changing parameters that influence the interacting behavior of the two methods.

% The third paragraph will be shorter, and will take about 2-3 sentences to describe the manuscript’s contribution to the field and the suitability of the manuscript to this particular journal based on topic, theme, or methodological or theoretical approach, with reference to other work recently published in the journal.

With this paper we will give some advices on what is to mind if someone wants to reimplement the method of G. Th\"ommes. Researcher can use our parameter studies to find their own sweet spot between performance and accuracy.

% The final paragraph will list 2-3 possible reviewers for the manuscript, and will thank the editor for considering the manuscript for publication. Contact info can be added here.

Possible reviewers for this paper would be G. Th\"ommes, J. Becker, and M. Junk. Thank you for considering this paper for puplication!

\closing{Sincerely yours,}

%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2015-11-02 Paper/scifile.tex
Cover Letter - Erster Entwurf

@@
 \\
-\normalsize{$^{1}$Chair for System-Simulation, Friedrich Alexander Univerität Erlangen-Nürnberg}\\
+\normalsize{$^{1}$Chair for System-Simulation, Friedrich Alexander Univerit\"at Erlangen-N\"urnberg}\\
 \normalsize{91058 Erlangen, Germany}\\ % ist das so richtig?
@@
 \begin{sciabstract}
-  We implemented the lattice Boltzman method for immiscible multiphase flow simulations.
-We combined this with the level set method according to the paper of G.
+  We implemented the lattice Boltzmann method for immiscible multiphase flow simulations and combined it with the level set method according to the paper of G.
 Thömmes FUSSNOTE.
-After reimplementing the testcases mentioned in the paper, we studied the coupling of the two methods and the impact of the variables.
+The level set method is used to calculate the movement of the interface between the two phases.
+The input for the level set method is computed by the lattice Boltzmann method.
+We reimplemented the test cases, mentioned in the paper, to study the method-coupling and its impact on accuracy.
 \end{sciabstract}
@@
 \newpage
-Hier folgen Informationen über das Stylesheet. Sollten wir dann irgendwann loeschen, fand ich aber fuers erste ganz hilfreich.
+Hier folgen Informationen \"uber das Stylesheet. Sollten wir dann irgendwann l\"oschen, fand ich aber f\"urs erste ganz hilfreich.
 

### 2015-11-03 Paper/docultexmm.tex
Anderes Stylesheet. Das davor hat ohne Bibtex gearbeitet

%%
%% This is file `docultexmm.tex', 
%% Documentation for siam multimedia macros for use with LaTeX 2e
%% 
%% December 19, 2013
%%
%% Version 1.0.1
%% 
%% You are not allowed to change this file. 
%% 
%% You are allowed to distribute this file under the condition that 
%% it is distributed together with all of the files in the siam macro 
%% distribution. These are:
%%
%%  siamltexmm.cls (this file)
%%  siam11.clo   (required size option for 11pt papers)
%%  subeqn.clo   (allows equation numbers with lettered subelements)
%%  siam.bst     (bibliographic style file for BibTeX)
%%  docultexmm.tex (documentation file)
%%
%% If you receive only some of these files from someone, please contact: 
%% multimedia@siam.org  
%% 
%% You are not allowed to distribute this file alone. You are not 
%% allowed to take money for the distribution or use of either this 
%% file or a changed version, except for a nominal charge for copying 
%% etc.
%%
%% \CharacterTable
%%  {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%%   Digits        \0\1\2\3\4\5\6\7\8\9
%%   Exclamation   \!     Double quote  \"     Hash (number) \#
%%   Dollar        \$     Percent       \%     Ampersand     \&
%%   Acute accent  \'     Left paren    \(     Right paren   \)
%%   Asterisk      \*     Plus          \+     Comma         \,
%%   Minus         \-     Point         \.     Solidus       \/
%%   Colon         \:     Semicolon     \;     Less than     \<
%%   Equals        \=     Greater than  \>     Question mark \?
%%   Commercial at \@     Left bracket  \[     Backslash     \\
%%   Right bracket \]     Circumflex    \^     Underscore    \_
%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%%   Right brace   \}     Tilde         \~}

\documentclass[final,leqno,onefignum,onetabnum]{siamltexmm}

\title{USING SIAM'S MULTIMEDIA \LaTeX\ MACROS\thanks{This work was
supported by the Society for Industrial and Applied
Mathematics.}}

\author{TeX Production\thanks{Society for Industrial and
Applied Mathematics, Philadelphia, Pennsylvania. 
(\email{multimedia@siam.org}). Questions, comments, or corrections
to this document may be directed to that email address.}}

\begin{document}
\maketitle
\newcommand{\slugmaster}{%
\slugger{siads}{xxxx}{xx}{x}{x--x}}%slugger should be set to juq, siads, sifin, or siims

\begin{abstract}
Documentation is given for use of the SIAM multimedia \LaTeX\ macros. These
macros are compatible with \LaTeX$2_{\varepsilon}$.
Instructions and suggestions for compliance with SIAM style
standards are also included. Familiarity with standard \LaTeX\ commands
is assumed.
\end{abstract}

\begin{keywords}\end{keywords}

\begin{AMS}\end{AMS}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{TEX PRODUCTION}{USING SIAM'S MM \LaTeX\ MACROS}

\section{Introduction}

This file is documentation for the SIAM Multimedia \LaTeX\ macros, and
provides instruction for submission of your files.

To accommodate authors who electronically typeset their manuscripts,
SIAM supports the use of \LaTeX. To ensure quality typesetting according
to SIAM style standards, SIAM provides a multimedia \LaTeX\ macro style file.
Using \LaTeX\ to format a manuscript should simplify the editorial process
and lessen the author's proofreading burden. However,
it is still necessary to proofread the galley proofs with care.

Electronic files should not be submitted until the paper has been
accepted, and then not until requested to do so by someone in the SIAM
office. Once an article is slated for an issue,
someone from the SIAM office will contact the author about any or all
of the following: editorial and stylistic queries, 
supplying the source files (and any supplementary macros)
for the properly formatted article, and handling figures.

When submitting electronic files  (electronic submissions) 
(to {\tt tex@siam.org}) include  the journal, issue, and author's
name in the subject line of the message. 
Authors are responsible for ensuring  that the paper generated 
from the source files exactly matches the paper that
was accepted for publication by the review editor. If it does not,
information on how it differs should be indicated in the transmission 
of the file. When submitting a file, please be sure to include any 
additional macros (other than those provided by SIAM) that will be 
needed to run the paper.

SIAM uses MS-DOS-based computers for \LaTeX\ processing. Therefore
all filenames should be restricted to eight characters or less,
plus a three character extension.

Once the files are corrected here at SIAM, we will mail the revised 
proofs to be read against the original edited hardcopy 
manuscript. We are not
set up to shuttle back and forth varying electronic versions of each
paper, so we must rely on hard copy of the galleys. The author's proofreading
is an important but easily overlooked step. Even if SIAM were not
to introduce a single editorial change into your manuscript, there
would still be a need to check, because electronic transmission
can introduce errors.

The distribution contains the following items: {\tt
siamltexmm.cls}, the main multimedia macro package; 
{\tt siam11.clo}, for the eleven-point size option; 
{\tt subeqn.clo}, a style option for equation numbering (see \S3 for
an explanation); and  {\tt siam.bst},
 the style file for use with {\sc Bib}\TeX. Also included is this
file {\tt docultexmm.tex}.
The rest of this paper will highlight
some keys to effective macro use, as well as point out options and
special cases, and describe SIAM style standards to which
authors should conform.

\section{Headings}
The top matter of a journal paper falls into a standard
format. It begins of course with the \verb|\documentclass| command

\begin{verbatim}

\documentclass{siamltexmm}

\end{verbatim}

Other class options  can be included
in the bracketed argument of the command, separated by commas.

Optional arguments include:
\begin{description}
\item[final] Without this option, lines which extend past the
margin will have black boxes next to them to help authors identify
lines that they need to fix, by re-writing or inserting breaks. \verb|final|
turns these boxes off, so that very small margin breaks which are not
noticible will not cause boxes to be generated.

\item[oneeqnum] Normally \verb|siamltexmm.cls| numbers equations,
tables, figures, and theorem environments with a decimal number, 
composed of the section of the paper, a period, and the number of
the enumerated object (example: 1.2). The sequence of numbering
is also restarted with each new section, so that, for example, the last
equation of section 3 may be 3.10, but the first equation of section
4 would be 4.1. Using \verb|oneeqnum| numbers all equations consecutively
throughout a paper with a single digit.

\item[onethmnum] Using \verb|onethmnum| numbers all theorem-like
environments consecutively throughout a paper with a single digit.

\item[onefignum] Using \verb|onethmnum| numbers all figures
 consecutively throughout a paper with a single digit.

\item[onetabnum] Using \verb|onethmnum| numbers all tables
 consecutively throughout a paper with a single digit.
\end{description}

The title and author parts are formatted using the
\verb|\title| and \verb|\author| commands as described in Lamport
\cite{Lamport}. The \verb|\date|
command is not used. \verb|\maketitle| produces the actual
output of the commands.

The addresses and support acknowledgments are put into the
\verb|\author| commands via \verb|\thanks|. If support is
overall for the authors, the support acknowledgment should
be put in a \verb|\thanks| command in the \verb|\title|.
Specific support should go following the addresses of the
individual authors in the same \verb|\thanks| command.

Sometimes authors have support or addresses in common which
necessitates having multiple \verb|\thanks| commands for
each author. Unfortunately \LaTeX\ does not normally allow this, 
so a special procedure must be used. An example of this procedure
follows. Grant information can also be run into both authors' 
footnotes.

\begin{verbatim}

\title{TITLE OF PAPER}

\author{A.~U. Thorone\footnotemark[2]\ \footnotemark[5]
\and A.~U. Thortwo\footnotemark[3]\ \footnotemark[5]
\and A.~U. Thorthree\footnotemark[4]}

\begin{document}
\maketitle
\newcommand{\slugmaster}{%
\slugger{siads}{xxxx}{xx}{x}{x--x}}%slugger should be set to juq, siads, sifin, or siims

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\footnotetext[2]{Address of A.~U. Thorone}
\footnotetext[3]{Address of A.~U. Thortwo}
\footnotetext[4]{Address of A.~U. Thorthree}
\footnotetext[5]{Support in common for the first and second authors.}

\renewcommand{\thefootnote}{\arabic{footnote}}

\end{verbatim}

Notice that the footnote marks begin with {\tt [2]}
because the first mark (the asterisk) will be used in the
title for date-received information by SIAM, even if not
already used for support data. This is just one example;
other situations follow a similar pattern.

Following the author and title is the abstract, key words
listing, and AMS subject classification number(s),
designated using the \verb|{abstract}|, \verb|{keywords}|,
and \verb|{AMS}| environments. If
there is only one AMS number, the commands
\verb|\begin{AM}| and \verb|\end{AM}| are used
instead of \verb|{AMS}|. This causes the heading to be
in the singular. Authors are responsible for providing AMS numbers.
They can be found in the Annual Index of Math Reviews, or
through {\tt e-Math} ({\tt telnet e-math.ams.com}; login
and password are both {\tt e-math}).

Left and right running heads should be provided in the
following way.

\begin{verbatim}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{A.~U. THORONE AND A.~U. THORTWO}{SHORTER PAPER TITLE}

\end{verbatim}

\section{Equations and mathematics}

One advantage of \LaTeX\ is that it can automatically number
equations and refer to these equation numbers in text. While plain \TeX's
method of equation numbering (explicit numbering using
\verb|\leqno|) works in the SIAM macro, it is not preferred
except in certain cases. SIAM style guidelines call for
aligned equations in many circumstances, and \LaTeX's 
\verb|{eqnarray}| environment is not compatible with
\verb|\leqno| and \LaTeX\ is not compatible with the plain
\TeX\ command \verb|\eqalign| and \verb|\leqalignno|. Since
SIAM may have to alter or realign certain groups of
equations, it is necessary to use the \LaTeX\ system of
automatic numbering.

Sometimes it is desirable to designate subequations of a larger
equation number. The subequations are designated with
(roman font) letters appended after the number. SIAM has
supplemented its macros with the {\tt subeqn.clo} option which
defines the environment \verb|{subequations}|.

\begin{verbatim}

\begin{subequations}\label{EKx}
\begin{equation}
 y_k =  B  y_{k-1} +  f, \qquad k=1,2,3,\ldots  
\end{equation}
for  any initial vector $ y_0$.   Then 
\begin{equation}
 y_k\rightarrow  u \mbox{\quad iff\quad} \rho( B)<1.
\end{equation}
\end{subequations}

\end{verbatim}

All equations within the \verb|{subequations}| environment
will keep the same overall number, but the letter
designation will increase.

Clear equation formatting using \TeX\ can be challenging. Aside from
the regular \TeX\ documentation, authors will find Nicholas 
J. Higham's book {\em Handbook of Writing for the Mathematical
Sciences\/} \cite{Higham} useful for guidelines and tips on 
formatting with \TeX. The book covers many other topics related 
to article writing as well.

Authors commonly make mistakes by using
 \verb|<|, \verb|>|, \verb|\mid|, and 
\verb|\parallel| as delimiters, instead of 
\verb|\langle|, \verb|\rangle|, \verb:|:,
and \verb:\|:. The incorrect symbols have particular 
meanings distinct from the correct ones and should not be confused.

\begin{table}[htbp]
\caption{Illustration of incorrect delimiter use.}
\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{|ll|ll|}\hline
\multicolumn{2}{|c|}{{\bf Wrong}} & \multicolumn{2}{c|}{{\bf Right}}\\ \hline
\verb|<x, y>| & $<x, y>$   &  \verb|\langle x, y\rangle| & $\langle x, y\rangle$\\
\verb|5 < \mid A \mid| &  $5 < \mid A \mid$ & \verb:5 < |A|: &  $5 < |A|$\\
\verb|6x = \parallel x|&&&\\ 
\verb|    - 1\parallel_{i}| & $6x = \parallel x - 1\parallel_{i}$ &
   \verb:6x = \|x - 1\|_{i}: & $6x = \| x - 1\|_{i}$\\ \hline
\end{tabular}
\end{center}
\end{table}

Another common author error is to put large (and even medium sized)
matrices in-line with the text, rather than displaying them. This
creates unattractive line spacing problems, and should be assiduously
avoided. Text-sized matrices (like $({a \atop b} {b \atop c})$) might
be used but anything much more complex than the example cited will
not be easy to read and should be displayed.

More information on the formatting of equations and aligned
equations is found in Lamport \cite{Lamport}. Authors bear 
primary responsibility for formatting their equations within 
margins and in an aesthetically pleasing and informative manner.

The SIAM macros include additional roman math words, or ``log-like"
functions, to those provided in standard \TeX.  The following
commands are added: \verb:\const:, \verb:\diag:, \verb:\grad:,
\verb:\Range:, \verb:\rank:, and \verb:\supp:.
These commands produce the same word as the command name
in math mode, in upright type.

\section{Special fonts}

SIAM supports the use of the AMS-\TeX\ fonts (version 2.0
and later). The package \verb|amsfonts| can be included with
the command\linebreak \verb|\usepackage{amsfonts}|. This package
is part of the AMS-\LaTeX distribution, available
from the AMS or from the Comprehensive TeX Archive
Network (anonymous ftp to ftp.shsu.edu). The blackboard bold font in this
font package can be used for designating number sets. 
This is preferable to other methods of combining letters
(such as I and R for the real numbers) to produce pseudo-bold
letters but this is tolerable as well. Typographically speaking,
number sets may simply be designated using regular bold letters; 
the blackboard bold typeface was designed to fulfil a desire
to simulate the limitations of a chalk board in printed type.

\subsection{Punctuation}
All standard punctuation and all numerals should be set in roman type
(upright) even within italic text. The only exceptions are periods and 
commas. They may be set to match the surrounding text.

References to sections should use the symbol \S, generated by
\verb|\S|. (If the reference begins a sentence, the term ``Section''
should be spelled out in full.) Authors should not redefine
\verb|\S|, say, to be a calligraphic S, because \verb|\S|
must be reserved for use as the section symbol.

Authors sometimes confuse the use of various types of dashes.
Hyphens (\verb|-|, -) are used for some compound words (many
such words should have no hyphen but must be run together, 
like ``nonzero,'' or split apart, like ``well defined''). 
Minus signs (\verb|$-$|, $-$)
should be used in math to represent subtraction or negative numbers.
En dashes (\verb|--|, --) are used for ranges (like 3--5, 
June--August), or for joined names (like Runge--Kutta). Em dashes
(\verb|---|, ---) are used to set off a clause---such as this 
one---from the rest of the sentence.

\subsection{Text formatting}

SIAM style preferences do not make regular use of the \verb|{enumerate}|
and \verb|{itemize}| environments. Instead,
{\tt siamltexmm.cls} includes definitions of two alternate list
environments, \verb|{remunerate}| and \verb|{romannum}|.
Unlike the standard itemized lists, these environments do
not indent the secondary lines of text. The labels, whether
defaults or the optional user-defined, are always aligned
flush right.

The \verb|{remunerate}| environment consecutively numbers
each item with an arabic numeral followed by a period. This
number is always upright, even in slanted
environments. (For those wondering at the unusual
naming of this environment, it comes from Seroul and Levy's
\cite{SerLev} definition of a similar macro for plain \TeX: 
%{\tt \char"5C meti} 
\verb|\meti| which is
% {\tt \char"5C item}
\protect\verb|\item|  spelled backwards. Thus
%{\tt \{remunerate\}}, 
\verb|{remunerate}|
a portion of 
%{\tt \{enumerate\}}
\verb|{enumerate}|
spelled backwards.)

The \verb|{romannum}| environment consecutively numbers
each item with a lower-case roman numeral enclosed in
parentheses. This number will always be upright within
slanted environments (as in theorems).

\section{Theorems and Lemmas}
Theorems, lemmas, corollaries, definitions, and propositions are covered
in the SIAM macros by the theorem-environments
\verb|{theorem}|, \verb|{lemma}|, \verb|{corollary}|,
\verb|{definition}| and \verb|{proposition}|. These are all
numbered in the same sequence and produce labels in small 
caps with an italic body. Other environments may be specified by the
\verb|\newtheorem| command. SIAM's style is for Remarks and Examples
to appear with italic labels and an upright roman body.

\begin{verbatim}

\begin{theorem}
Sample theorem included for illustration.  
Numbers and parentheses, like equation $(3.2)$, should be set 
in roman type.  Note that words (as opposed to ``log-like''
functions) in displayed equations, such as
$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
will appear in italic type in a theorem, though normally
they should appear in roman.\end{theorem}

\end{verbatim}

This sample produces Theorem 4.1 below.

\begin{theorem}
Sample theorem included for illustration.  
Numbers and parentheses, like equation $(3.2)$, should be set 
in roman type.  Note that words (as opposed to ``log-like''
functions) in displayed equations, such as
$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
will appear in italic type in a theorem, though normally
they should appear in roman.
\end{theorem}

Proofs are handled with the \verb|\begin{proof}|
\verb|\end{proof}| environment. A ``QED'' box \endproof\ is created
automatically by \verb|\end{proof}|, but this should be
preceded with a \verb|\qquad|.

Named proofs, if used, must be done independently by the
authors. SIAM style specifies that proofs which end with
displayed equations should have the QED box two ems (\verb|\qquad|)
from the end of the equation on line with it horizontally.
Below is an example of how this can be done:

\begin{verbatim}

{\em Proof}. Proof of the previous theorem 
                .
                .
                .
thus,
$$
a^2 + b^2 = c^2 \qquad\endproof
$$

\end{verbatim}

\section{Figures and tables}
Figures and tables sometimes require special consideration.
Tables in SIAM style are need to be set in eight point size
by using the \verb|\footnotesize| command inside the 
\verb|\begin{table}| environment. Also, they should be designed 
so that they do not extend beyond the text margins.

SIAM style requires that no figures or tables  appear in the
references section of the paper. \LaTeX\ is notorious for
making figure placement difficult, so it is important to
pay particular attention to figure placement near the
references in the text. All figures and tables should
be referred to in the text.

SIAM supports the use of {\tt epsfig} for including {\sc PostScript}
figures. All {\sc Post\-Script} figures should be sent in separate
files. See the {\tt epsfig} documentation (available via
anonymous ftp from CTAN: ftp.shsu.edu) for more details on the use
of this style option. It is a good idea to submit high-quality
hardcopy of all {\sc Post\-Script} figures just in case there 
is difficulty in the reproduction of the figure. Figures produced 
by other non-\TeX\ methods should be included as high-quality 
hardcopy when  the manuscript is submitted.

{\sc PostScript} figures that are sent should be generated with
sufficient line thickness. Some past figures authors have sent
had their line widths become very faint when SIAM set the papers
using a high-quality 1200dpi printer.

Hardcopy for non-{\sc PostScript} figures should be included in
the submission of the hardcopy of the manuscript. Space
should be left in the \verb|{figure}| command for the
hardcopy to be inserted in production.

\section{Bibliography and Bib\TeX}

If using {\sc Bib}\TeX, authors need not submit the {\tt .bib} file for
their papers. Merely submit the completed {\tt .bbl} file, having used
{\tt siam.bst} as their bibliographic style file. {\tt siam.bst}
only works with Bib\TeX\ version 99i and later. The use of
Bib\TeX\ and the preparation of a {\tt .bib} file is
described in greater detail in \cite{Lamport}.

If not using Bib\TeX, SIAM bibliographic references follow
the format of the following examples:

\begin{verbatim}

\bibitem{Ri} {\sc W. Riter},
{\em Title of a paper appearing in a book}, in The Book 
Title, E.~D. One, E.~D. Two, and A.~N. Othereditor, eds., 
Publisher, Location, 1992, pp.~000--000.

\bibitem{AuTh1} {\sc A.~U. Thorone}, {\em Title of paper
with lower case letters}, SIAM J. Abbrev. Correctly, 2
(1992), pp.~000--000.

\bibitem{A1A2} {\sc A.~U. Thorone and A.~U. Thortwo}, {\em
Title of paper appearing in book}, in Book Title: With All
Initial Caps, Publisher, Location, 1992.

\bibitem{A1A22} \sameauthor, % generates the 3 em rule
{\em Title of Book{\rm :} Note Initial Caps and {\rm ROMAN
TYPE} for Punctuation and Acronyms}, Publisher,
Location, pp.~000--000, 1992.

\bibitem{AuTh3} {\sc A.~U. Thorthree}, {\em Title of paper
that's not published yet}, SIAM. J. Abbrev. Correctly, to appear.

\end{verbatim}

Other types of references fall into the same general
pattern. See the sample file or any SIAM journal for other
examples. Authors must correctly format their bibliography to
be considered as having used the macros correctly. An incorrectly 
formatted bibliography is not only time-consuming for SIAM to
process but it is possible that errors may be introduced into 
it by keyboarders/copy editors.

As an alternative to the above style of reference, an alphanumeric
code may be used in place of the number (e.g., [AUTh90]). The same
commands are used, but \verb|\bibitem| takes an optional argument
containing the desired alphanumeric code.

Another alternative is no number, simply the authors' names and
the year of publication following in parentheses. The rest of the
format is identical. The macros do not support this alternative
directly, but modifications to the macro definition are possible
if this reference style is preferred.

\section{Conclusion} Many other style suggestions and tips
could be given to help authors but are beyond the scope of this
document. Simple mistakes can be avoided by increasing your familiarity
with how \LaTeX\ functions. The books referred to throughout this document
are also useful to the author who wants clear, beautiful typography
with minimal mistakes.

\Appendix
\section{The use of appendices}
The \verb|\appendix| command may be used before the final sections
of a paper to designate them as appendices. Once \verb|\appendix|
is called, all subsequent sections will appear as

\appendix
\section{Title of appendix} Each one will be sequentially lettered
instead of numbered. Theorem-like environments, subsections,
and equations will also have the section number changed to a letter.

If there is only {\em one} appendix, however, the \verb|\Appendix|
(with a capital letter) should be used instead. This produces only 
the word {\bf Appendix} in the section title, and does not add a letter.
Equation numbers, theorem numbers and subsections of the appendix
will have the letter ``A''  designating the section number.

If you don't want to title your appendix, and just call it
{\bf Appendix A.} for example, use \verb|\appendix\section*{}| 
and don't include anything in the title field. This works
opposite to the way \verb|\section*| usually works, by including the
section number, but not using a title.

Appendices should appear before the bibliography section, not after,
and any acknowledgments should be placed after the appendices and before
the bibliography.

\begin{thebibliography}{1}
\bibitem{GoMiSa} {\sc M. Goossens, F. Mittelbach, and A. Samarin},
{\em The} \LaTeX\ {\em Companion}, Addison-Wesley, Reading, MA, 1994.

\bibitem{Higham} {\sc N.~J. Higham}, {\em Handbook of Writing for
the Mathematical Sciences}, Society for Industrial and Applied
Mathematics, Philadelphia, PA, 1993.

\bibitem{Lamport} {\sc L. Lamport}, \LaTeX: {\em A Document
Preparation System}, Addison-Wesley, Reading, MA, 1986.

\bibitem{SerLev} {\sc R. Seroul and S. Levy}, {\em A
Beginner's Book of} \TeX, Springer-Verlag, Berlin, New
York, 1991.
\end{thebibliography}

\end{document}
%% end of file `docultexmm.tex'

### 2015-11-03 Paper/paper.tex
Anderes Stylesheet. Das davor hat ohne Bibtex gearbeitet

--- 2015-11-03 Paper/docultexmm.tex
@@
 
-\title{USING SIAM'S MULTIMEDIA \LaTeX\ MACROS\thanks{This work was
-supported by the Society for Industrial and Applied
-Mathematics.}}
+\title{Implementation of a lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}
 
-\author{TeX Production\thanks{Society for Industrial and
-Applied Mathematics, Philadelphia, Pennsylvania. 
-(\email{multimedia@siam.org}). Questions, comments, or corrections
-to this document may be directed to that email address.}}
+\author
+{Lorenz Hufnagel, Daniel Zint\\
+Chair for System-Simulation, Friedrich Alexander Univerit\"at Erlangen-N\"urnberg\\
+91058 Erlangen, Germany % ist das so richtig?
+}
 
@@
 \begin{abstract}
-Documentation is given for use of the SIAM multimedia \LaTeX\ macros. These
-macros are compatible with \LaTeX$2_{\varepsilon}$.
-Instructions and suggestions for compliance with SIAM style
-standards are also included. Familiarity with standard \LaTeX\ commands
-is assumed.
+	We implemented the lattice Boltzmann method for immiscible multiphase flow simulations and combined it with the level set method according to the paper of G.
+Th\"ommes \cite{Thoemmes}.
+The level set method is used to calculate the movement of the interface between the two phases.
+The input for the level set method is computed by the lattice Boltzmann method.
+We reimplemented the test cases, mentioned in the paper, to study the method-coupling and its impact on accuracy.
 \end{abstract}
 
-\begin{keywords}\end{keywords}
+\begin{keywords}
+	Lattice Boltzmann method,
+	Level set method,
+	Free surface,
+	Multiphase
+\end{keywords}
 
@@
 \thispagestyle{plain}
-\markboth{TEX PRODUCTION}{USING SIAM'S MM \LaTeX\ MACROS}
+%\markboth{TEX PRODUCTION}{USING SIAM'S MM \LaTeX\ MACROS}
 
@@
 
-This file is documentation for the SIAM Multimedia \LaTeX\ macros, and
-provides instruction for submission of your files.
+\section{Numerical Methods}
 
-To accommodate authors who electronically typeset their manuscripts,
-SIAM supports the use of \LaTeX. To ensure quality typesetting according
-to SIAM style standards, SIAM provides a multimedia \LaTeX\ macro style file.
-Using \LaTeX\ to format a manuscript should simplify the editorial process
-and lessen the author's proofreading burden. However,
-it is still necessary to proofread the galley proofs with care.
+\subsection{The Lattice Boltzmann Method}
 
-Electronic files should not be submitted until the paper has been
-accepted, and then not until requested to do so by someone in the SIAM
-office. Once an article is slated for an issue,
-someone from the SIAM office will contact the author about any or all
-of the following: editorial and stylistic queries, 
-supplying the source files (and any supplementary macros)
-for the properly formatted article, and handling figures.
+\subsection{The Level Set Method}
 
-When submitting electronic files  (electronic submissions) 
-(to {\tt tex@siam.org}) include  the journal, issue, and author's
-name in the subject line of the message. 
-Authors are responsible for ensuring  that the paper generated 
-from the source files exactly matches the paper that
-was accepted for publication by the review editor. If it does not,
-information on how it differs should be indicated in the transmission 
-of the file. When submitting a file, please be sure to include any 
-additional macros (other than those provided by SIAM) that will be 
-needed to run the paper.
+\section{something new what we did / Results}
 
-SIAM uses MS-DOS-based computers for \LaTeX\ processing. Therefore
-all filenames should be restricted to eight characters or less,
-plus a three character extension.
-
-Once the files are corrected here at SIAM, we will mail the revised 
-proofs to be read against the original edited hardcopy 
-manuscript. We are not
-set up to shuttle back and forth varying electronic versions of each
-paper, so we must rely on hard copy of the galleys. The author's proofreading
-is an important but easily overlooked step. Even if SIAM were not
-to introduce a single editorial change into your manuscript, there
-would still be a need to check, because electronic transmission
-can introduce errors.
-
-The distribution contains the following items: {\tt
-siamltexmm.cls}, the main multimedia macro package; 
-{\tt siam11.clo}, for the eleven-point size option; 
-{\tt subeqn.clo}, a style option for equation numbering (see \S3 for
-an explanation); and  {\tt siam.bst},
- the style file for use with {\sc Bib}\TeX. Also included is this
-file {\tt docultexmm.tex}.
-The rest of this paper will highlight
-some keys to effective macro use, as well as point out options and
-special cases, and describe SIAM style standards to which
-authors should conform.
-
-\section{Headings}
-The top matter of a journal paper falls into a standard
-format. It begins of course with the \verb|\documentclass| command
-
-\begin{verbatim}
-
-\documentclass{siamltexmm}
-
-\end{verbatim}
-
-Other class options  can be included
-in the bracketed argument of the command, separated by commas.
-
-Optional arguments include:
-\begin{description}
-\item[final] Without this option, lines which extend past the
-margin will have black boxes next to them to help authors identify
-lines that they need to fix, by re-writing or inserting breaks. \verb|final|
-turns these boxes off, so that very small margin breaks which are not
-noticible will not cause boxes to be generated.
-
-\item[oneeqnum] Normally \verb|siamltexmm.cls| numbers equations,
-tables, figures, and theorem environments with a decimal number, 
-composed of the section of the paper, a period, and the number of
-the enumerated object (example: 1.2). The sequence of numbering
-is also restarted with each new section, so that, for example, the last
-equation of section 3 may be 3.10, but the first equation of section
-4 would be 4.1. Using \verb|oneeqnum| numbers all equations consecutively
-throughout a paper with a single digit.
-
-\item[onethmnum] Using \verb|onethmnum| numbers all theorem-like
-environments consecutively throughout a paper with a single digit.
-
-\item[onefignum] Using \verb|onethmnum| numbers all figures
- consecutively throughout a paper with a single digit.
-
-\item[onetabnum] Using \verb|onethmnum| numbers all tables
- consecutively throughout a paper with a single digit.
-\end{description}
-
-The title and author parts are formatted using the
-\verb|\title| and \verb|\author| commands as described in Lamport
-\cite{Lamport}. The \verb|\date|
-command is not used. \verb|\maketitle| produces the actual
-output of the commands.
-
-The addresses and support acknowledgments are put into the
-\verb|\author| commands via \verb|\thanks|. If support is
-overall for the authors, the support acknowledgment should
-be put in a \verb|\thanks| command in the \verb|\title|.
-Specific support should go following the addresses of the
-individual authors in the same \verb|\thanks| command.
-
-Sometimes authors have support or addresses in common which
-necessitates having multiple \verb|\thanks| commands for
-each author. Unfortunately \LaTeX\ does not normally allow this, 
-so a special procedure must be used. An example of this procedure
-follows. Grant information can also be run into both authors' 
-footnotes.
-
-\begin{verbatim}
-
-\title{TITLE OF PAPER}
-
-\author{A.~U. Thorone\footnotemark[2]\ \footnotemark[5]
-\and A.~U. Thortwo\footnotemark[3]\ \footnotemark[5]
-\and A.~U. Thorthree\footnotemark[4]}
-
-\begin{document}
-\maketitle
-\newcommand{\slugmaster}{%
-\slugger{siads}{xxxx}{xx}{x}{x--x}}%slugger should be set to juq, siads, sifin, or siims
-
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-
-\footnotetext[2]{Address of A.~U. Thorone}
-\footnotetext[3]{Address of A.~U. Thortwo}
-\footnotetext[4]{Address of A.~U. Thorthree}
-\footnotetext[5]{Support in common for the first and second authors.}
-
-\renewcommand{\thefootnote}{\arabic{footnote}}
-
-\end{verbatim}
-
-Notice that the footnote marks begin with {\tt [2]}
-because the first mark (the asterisk) will be used in the
-title for date-received information by SIAM, even if not
-already used for support data. This is just one example;
-other situations follow a similar pattern.
-
-Following the author and title is the abstract, key words
-listing, and AMS subject classification number(s),
-designated using the \verb|{abstract}|, \verb|{keywords}|,
-and \verb|{AMS}| environments. If
-there is only one AMS number, the commands
-\verb|\begin{AM}| and \verb|\end{AM}| are used
-instead of \verb|{AMS}|. This causes the heading to be
-in the singular. Authors are responsible for providing AMS numbers.
-They can be found in the Annual Index of Math Reviews, or
-through {\tt e-Math} ({\tt telnet e-math.ams.com}; login
-and password are both {\tt e-math}).
-
-Left and right running heads should be provided in the
-following way.
-
-\begin{verbatim}
-
-\pagestyle{myheadings}
-\thispagestyle{plain}
-\markboth{A.~U. THORONE AND A.~U. THORTWO}{SHORTER PAPER TITLE}
-
-\end{verbatim}
-
-\section{Equations and mathematics}
-
-One advantage of \LaTeX\ is that it can automatically number
-equations and refer to these equation numbers in text. While plain \TeX's
-method of equation numbering (explicit numbering using
-\verb|\leqno|) works in the SIAM macro, it is not preferred
-except in certain cases. SIAM style guidelines call for
-aligned equations in many circumstances, and \LaTeX's 
-\verb|{eqnarray}| environment is not compatible with
-\verb|\leqno| and \LaTeX\ is not compatible with the plain
-\TeX\ command \verb|\eqalign| and \verb|\leqalignno|. Since
-SIAM may have to alter or realign certain groups of
-equations, it is necessary to use the \LaTeX\ system of
-automatic numbering.
-
-Sometimes it is desirable to designate subequations of a larger
-equation number. The subequations are designated with
-(roman font) letters appended after the number. SIAM has
-supplemented its macros with the {\tt subeqn.clo} option which
-defines the environment \verb|{subequations}|.
-
-\begin{verbatim}
-
-\begin{subequations}\label{EKx}
-\begin{equation}
- y_k =  B  y_{k-1} +  f, \qquad k=1,2,3,\ldots  
-\end{equation}
-for  any initial vector $ y_0$.   Then 
-\begin{equation}
- y_k\rightarrow  u \mbox{\quad iff\quad} \rho( B)<1.
-\end{equation}
-\end{subequations}
-
-\end{verbatim}
-
-All equations within the \verb|{subequations}| environment
-will keep the same overall number, but the letter
-designation will increase.
-
-Clear equation formatting using \TeX\ can be challenging. Aside from
-the regular \TeX\ documentation, authors will find Nicholas 
-J. Higham's book {\em Handbook of Writing for the Mathematical
-Sciences\/} \cite{Higham} useful for guidelines and tips on 
-formatting with \TeX. The book covers many other topics related 
-to article writing as well.
-
-Authors commonly make mistakes by using
- \verb|<|, \verb|>|, \verb|\mid|, and 
-\verb|\parallel| as delimiters, instead of 
-\verb|\langle|, \verb|\rangle|, \verb:|:,
-and \verb:\|:. The incorrect symbols have particular 
-meanings distinct from the correct ones and should not be confused.
-
-\begin{table}[htbp]
-\caption{Illustration of incorrect delimiter use.}
-\begin{center}\footnotesize
-\renewcommand{\arraystretch}{1.3}
-\begin{tabular}{|ll|ll|}\hline
-\multicolumn{2}{|c|}{{\bf Wrong}} & \multicolumn{2}{c|}{{\bf Right}}\\ \hline
-\verb|<x, y>| & $<x, y>$   &  \verb|\langle x, y\rangle| & $\langle x, y\rangle$\\
-\verb|5 < \mid A \mid| &  $5 < \mid A \mid$ & \verb:5 < |A|: &  $5 < |A|$\\
-\verb|6x = \parallel x|&&&\\ 
-\verb|    - 1\parallel_{i}| & $6x = \parallel x - 1\parallel_{i}$ &
-   \verb:6x = \|x - 1\|_{i}: & $6x = \| x - 1\|_{i}$\\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Another common author error is to put large (and even medium sized)
-matrices in-line with the text, rather than displaying them. This
-creates unattractive line spacing problems, and should be assiduously
-avoided. Text-sized matrices (like $({a \atop b} {b \atop c})$) might
-be used but anything much more complex than the example cited will
-not be easy to read and should be displayed.
-
-More information on the formatting of equations and aligned
-equations is found in Lamport \cite{Lamport}. Authors bear 
-primary responsibility for formatting their equations within 
-margins and in an aesthetically pleasing and informative manner.
-
-The SIAM macros include additional roman math words, or ``log-like"
-functions, to those provided in standard \TeX.  The following
-commands are added: \verb:\const:, \verb:\diag:, \verb:\grad:,
-\verb:\Range:, \verb:\rank:, and \verb:\supp:.
-These commands produce the same word as the command name
-in math mode, in upright type.
-
-\section{Special fonts}
-
-SIAM supports the use of the AMS-\TeX\ fonts (version 2.0
-and later). The package \verb|amsfonts| can be included with
-the command\linebreak \verb|\usepackage{amsfonts}|. This package
-is part of the AMS-\LaTeX distribution, available
-from the AMS or from the Comprehensive TeX Archive
-Network (anonymous ftp to ftp.shsu.edu). The blackboard bold font in this
-font package can be used for designating number sets. 
-This is preferable to other methods of combining letters
-(such as I and R for the real numbers) to produce pseudo-bold
-letters but this is tolerable as well. Typographically speaking,
-number sets may simply be designated using regular bold letters; 
-the blackboard bold typeface was designed to fulfil a desire
-to simulate the limitations of a chalk board in printed type.
-
-\subsection{Punctuation}
-All standard punctuation and all numerals should be set in roman type
-(upright) even within italic text. The only exceptions are periods and 
-commas. They may be set to match the surrounding text.
-
-References to sections should use the symbol \S, generated by
-\verb|\S|. (If the reference begins a sentence, the term ``Section''
-should be spelled out in full.) Authors should not redefine
-\verb|\S|, say, to be a calligraphic S, because \verb|\S|
-must be reserved for use as the section symbol.
-
-Authors sometimes confuse the use of various types of dashes.
-Hyphens (\verb|-|, -) are used for some compound words (many
-such words should have no hyphen but must be run together, 
-like ``nonzero,'' or split apart, like ``well defined''). 
-Minus signs (\verb|$-$|, $-$)
-should be used in math to represent subtraction or negative numbers.
-En dashes (\verb|--|, --) are used for ranges (like 3--5, 
-June--August), or for joined names (like Runge--Kutta). Em dashes
-(\verb|---|, ---) are used to set off a clause---such as this 
-one---from the rest of the sentence.
-
-\subsection{Text formatting}
-
-SIAM style preferences do not make regular use of the \verb|{enumerate}|
-and \verb|{itemize}| environments. Instead,
-{\tt siamltexmm.cls} includes definitions of two alternate list
-environments, \verb|{remunerate}| and \verb|{romannum}|.
-Unlike the standard itemized lists, these environments do
-not indent the secondary lines of text. The labels, whether
-defaults or the optional user-defined, are always aligned
-flush right.
-
-The \verb|{remunerate}| environment consecutively numbers
-each item with an arabic numeral followed by a period. This
-number is always upright, even in slanted
-environments. (For those wondering at the unusual
-naming of this environment, it comes from Seroul and Levy's
-\cite{SerLev} definition of a similar macro for plain \TeX: 
-%{\tt \char"5C meti} 
-\verb|\meti| which is
-% {\tt \char"5C item}
-\protect\verb|\item|  spelled backwards. Thus
-%{\tt \{remunerate\}}, 
-\verb|{remunerate}|
-a portion of 
-%{\tt \{enumerate\}}
-\verb|{enumerate}|
-spelled backwards.)
-
-The \verb|{romannum}| environment consecutively numbers
-each item with a lower-case roman numeral enclosed in
-parentheses. This number will always be upright within
-slanted environments (as in theorems).
-
-\section{Theorems and Lemmas}
-Theorems, lemmas, corollaries, definitions, and propositions are covered
-in the SIAM macros by the theorem-environments
-\verb|{theorem}|, \verb|{lemma}|, \verb|{corollary}|,
-\verb|{definition}| and \verb|{proposition}|. These are all
-numbered in the same sequence and produce labels in small 
-caps with an italic body. Other environments may be specified by the
-\verb|\newtheorem| command. SIAM's style is for Remarks and Examples
-to appear with italic labels and an upright roman body.
-
-\begin{verbatim}
-
-\begin{theorem}
-Sample theorem included for illustration.  
-Numbers and parentheses, like equation $(3.2)$, should be set 
-in roman type.  Note that words (as opposed to ``log-like''
-functions) in displayed equations, such as
-$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
-will appear in italic type in a theorem, though normally
-they should appear in roman.\end{theorem}
-
-\end{verbatim}
-
-This sample produces Theorem 4.1 below.
-
-\begin{theorem}
-Sample theorem included for illustration.  
-Numbers and parentheses, like equation $(3.2)$, should be set 
-in roman type.  Note that words (as opposed to ``log-like''
-functions) in displayed equations, such as
-$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
-will appear in italic type in a theorem, though normally
-they should appear in roman.
-\end{theorem}
-
-Proofs are handled with the \verb|\begin{proof}|
-\verb|\end{proof}| environment. A ``QED'' box \endproof\ is created
-automatically by \verb|\end{proof}|, but this should be
-preceded with a \verb|\qquad|.
-
-Named proofs, if used, must be done independently by the
-authors. SIAM style specifies that proofs which end with
-displayed equations should have the QED box two ems (\verb|\qquad|)
-from the end of the equation on line with it horizontally.
-Below is an example of how this can be done:
-
-\begin{verbatim}
-
-{\em Proof}. Proof of the previous theorem 
-                .
-                .
-                .
-thus,
-$$
-a^2 + b^2 = c^2 \qquad\endproof
-$$
-
-\end{verbatim}
-
-\section{Figures and tables}
-Figures and tables sometimes require special consideration.
-Tables in SIAM style are need to be set in eight point size
-by using the \verb|\footnotesize| command inside the 
-\verb|\begin{table}| environment. Also, they should be designed 
-so that they do not extend beyond the text margins.
-
-SIAM style requires that no figures or tables  appear in the
-references section of the paper. \LaTeX\ is notorious for
-making figure placement difficult, so it is important to
-pay particular attention to figure placement near the
-references in the text. All figures and tables should
-be referred to in the text.
-
-SIAM supports the use of {\tt epsfig} for including {\sc PostScript}
-figures. All {\sc Post\-Script} figures should be sent in separate
-files. See the {\tt epsfig} documentation (available via
-anonymous ftp from CTAN: ftp.shsu.edu) for more details on the use
-of this style option. It is a good idea to submit high-quality
-hardcopy of all {\sc Post\-Script} figures just in case there 
-is difficulty in the reproduction of the figure. Figures produced 
-by other non-\TeX\ methods should be included as high-quality 
-hardcopy when  the manuscript is submitted.
-
-{\sc PostScript} figures that are sent should be generated with
-sufficient line thickness. Some past figures authors have sent
-had their line widths become very faint when SIAM set the papers
-using a high-quality 1200dpi printer.
-
-Hardcopy for non-{\sc PostScript} figures should be included in
-the submission of the hardcopy of the manuscript. Space
-should be left in the \verb|{figure}| command for the
-hardcopy to be inserted in production.
-
-\section{Bibliography and Bib\TeX}
-
-If using {\sc Bib}\TeX, authors need not submit the {\tt .bib} file for
-their papers. Merely submit the completed {\tt .bbl} file, having used
-{\tt siam.bst} as their bibliographic style file. {\tt siam.bst}
-only works with Bib\TeX\ version 99i and later. The use of
-Bib\TeX\ and the preparation of a {\tt .bib} file is
-described in greater detail in \cite{Lamport}.
-
-If not using Bib\TeX, SIAM bibliographic references follow
-the format of the following examples:
-
-\begin{verbatim}
-
-\bibitem{Ri} {\sc W. Riter},
-{\em Title of a paper appearing in a book}, in The Book 
-Title, E.~D. One, E.~D. Two, and A.~N. Othereditor, eds., 
-Publisher, Location, 1992, pp.~000--000.
-
-\bibitem{AuTh1} {\sc A.~U. Thorone}, {\em Title of paper
-with lower case letters}, SIAM J. Abbrev. Correctly, 2
-(1992), pp.~000--000.
-
-\bibitem{A1A2} {\sc A.~U. Thorone and A.~U. Thortwo}, {\em
-Title of paper appearing in book}, in Book Title: With All
-Initial Caps, Publisher, Location, 1992.
-
-\bibitem{A1A22} \sameauthor, % generates the 3 em rule
-{\em Title of Book{\rm :} Note Initial Caps and {\rm ROMAN
-TYPE} for Punctuation and Acronyms}, Publisher,
-Location, pp.~000--000, 1992.
-
-\bibitem{AuTh3} {\sc A.~U. Thorthree}, {\em Title of paper
-that's not published yet}, SIAM. J. Abbrev. Correctly, to appear.
-
-\end{verbatim}
-
-Other types of references fall into the same general
-pattern. See the sample file or any SIAM journal for other
-examples. Authors must correctly format their bibliography to
-be considered as having used the macros correctly. An incorrectly 
-formatted bibliography is not only time-consuming for SIAM to
-process but it is possible that errors may be introduced into 
-it by keyboarders/copy editors.
-
-As an alternative to the above style of reference, an alphanumeric
-code may be used in place of the number (e.g., [AUTh90]). The same
-commands are used, but \verb|\bibitem| takes an optional argument
-containing the desired alphanumeric code.
-
-Another alternative is no number, simply the authors' names and
-the year of publication following in parentheses. The rest of the
-format is identical. The macros do not support this alternative
-directly, but modifications to the macro definition are possible
-if this reference style is preferred.
-
-\section{Conclusion} Many other style suggestions and tips
-could be given to help authors but are beyond the scope of this
-document. Simple mistakes can be avoided by increasing your familiarity
-with how \LaTeX\ functions. The books referred to throughout this document
-are also useful to the author who wants clear, beautiful typography
-with minimal mistakes.
-
-\Appendix
-\section{The use of appendices}
-The \verb|\appendix| command may be used before the final sections
-of a paper to designate them as appendices. Once \verb|\appendix|
-is called, all subsequent sections will appear as
-
-\appendix
-\section{Title of appendix} Each one will be sequentially lettered
-instead of numbered. Theorem-like environments, subsections,
-and equations will also have the section number changed to a letter.
-
-If there is only {\em one} appendix, however, the \verb|\Appendix|
-(with a capital letter) should be used instead. This produces only 
-the word {\bf Appendix} in the section title, and does not add a letter.
-Equation numbers, theorem numbers and subsections of the appendix
-will have the letter ``A''  designating the section number.
-
-If you don't want to title your appendix, and just call it
-{\bf Appendix A.} for example, use \verb|\appendix\section*{}| 
-and don't include anything in the title field. This works
-opposite to the way \verb|\section*| usually works, by including the
-section number, but not using a title.
-
-Appendices should appear before the bibliography section, not after,
-and any acknowledgments should be placed after the appendices and before
-the bibliography.
+\section{Conclusion}
 
 \begin{thebibliography}{1}
-\bibitem{GoMiSa} {\sc M. Goossens, F. Mittelbach, and A. Samarin},
-{\em The} \LaTeX\ {\em Companion}, Addison-Wesley, Reading, MA, 1994.
 
-\bibitem{Higham} {\sc N.~J. Higham}, {\em Handbook of Writing for
-the Mathematical Sciences}, Society for Industrial and Applied
-Mathematics, Philadelphia, PA, 1993.
+\bibitem{Thoemmes} {\sc G. Th\"ommes},{\em A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}, Journal of Computational Physics, 07.11.2008
 
-\bibitem{Lamport} {\sc L. Lamport}, \LaTeX: {\em A Document
-Preparation System}, Addison-Wesley, Reading, MA, 1986.
+%\bibitem{GoMiSa} {\sc M. Goossens, F. Mittelbach, and A. Samarin},
+%{\em The} \LaTeX\ {\em Companion}, Addison-Wesley, Reading, MA, 1994.
 
-\bibitem{SerLev} {\sc R. Seroul and S. Levy}, {\em A
-Beginner's Book of} \TeX, Springer-Verlag, Berlin, New
-York, 1991.
+%\bibitem{Higham} {\sc N.~J. Higham}, {\em Handbook of Writing for
+%the Mathematical Sciences}, Society for Industrial and Applied
+%Mathematics, Philadelphia, PA, 1993.
+
+%\bibitem{Lamport} {\sc L. Lamport}, \LaTeX: {\em A Document
+%Preparation System}, Addison-Wesley, Reading, MA, 1986.
+
+%\bibitem{SerLev} {\sc R. Seroul and S. Levy}, {\em A
+%Beginner's Book of} \TeX, Springer-Verlag, Berlin, New
+%York, 1991.
 \end{thebibliography}

### 2015-11-04 Paper/paper.tex
started with writing the introduction

@@
 The input for the level set method is computed by the lattice Boltzmann method.
-We reimplemented the test cases, mentioned in the paper, to study the method-coupling and its impact on accuracy.
+We reimplemented the test cases that are mentioned in the paper, to study the method-coupling and its impact on accuracy.
 \end{abstract}
@@
 \section{Introduction}
+%Something about the two-phase problem and some other algorithms that solve it. We could do this according to the presentation-slides.
+In engineering the immiscible two-phase flow problem often needs to be considered.
+For example, bubble dynamics are decisive for the design of chemical reactors.
+Also fingering in oil recovery is a common problem that can be seen as a immiscible two-phase problem.
+
+The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids.
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (PICTURE).
+{\it continue here...}
+
+% Not done with this chapter ...
+
+There are different approaches to solve the immiscible two-phase problem.
+The most spread among these approaches is the colour gradient method of Gunstensen and Rothman \cite{GRcg1,GRcg2,GRcg3}.
+The downside of this method is that it is only applicable for small density and viscosity differences.
+Another approach is the concept of {\it interaction potentials} by Shan and Chen \cite{ShanChen1,ShanChen2}.
+This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
+Furthermore there are free surface methods which only take one fluid in account for computation (REFERENCE!).
+They work best for big density and viscosity differences.
 
 \section{Numerical Methods}
+Describe the basic concepts of how the methods work. Just as a short introduction to the subsections.
 
 \subsection{The Lattice Boltzmann Method}
+Explain LBM and introduce the most important formulas we use. Give references for further reading?
 
 \subsection{The Level Set Method}
+Explain level set method and the level set equation. Introduce the Ian Mitchell Toolbox.
+
+\subsection{Coupling of LBM and level set method}
+Present the new boundary condition but without all the formula deriving we have in the Th\"ommes-paper.
+Maybe explain the refill method?
+Show Fig.2 of the Th\"ommes-paper and explain the coupling of the two methods.
 
 \section{something new what we did / Results}
+Present our test case (I think one would be enough) and describe the parameters we have studied. Give graphs that show their impact on accuracy.
 
@@
 
-\bibitem{Thoemmes} {\sc G. Th\"ommes},{\em A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}, Journal of Computational Physics, 07.11.2008
+\bibitem{Thoemmes} {\sc G. Th\"ommes, J. Becker}, {\em A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}, J. Comput. Phys. 228 (2009), 1139-1156
+
+\bibitem{Adalsteinsson} {\sc D. Adalsteinsson, J.A. Sethian}, {\em A fast level set method for propagating interfaces}, J. Comput. Phys. 118 (2) (1995) 269-277
+
+\bibitem{GRcg1} {\sc A.K. Gunstensen, D.H. Rothman, S. Zaleski, G. Zanetti}, {\em Lattice Boltzmann model of immiscible fluids}, Phys. Rev. A 43 (8) (1991) 4320-4327
+
+\bibitem{GRcg2} {\sc A.K. Gunstensen, D.H. Rothman}, {\em Macroscopic modeling of immiscible flows in three dimensions by a lattice Boltzman method}, Europhys. Lett. 18 (2) (1998) 157-161
+
+\bibitem{GRcg3} {\sc K.
+Sankaranarayanan, I.G.
+Kevrekidies, S.
+Sundaresan, J.
+Lu, G.
+Tryggvason}, {\em A comparative study of lattice Boltzmann and front-tracking finite-difference methods for bubble simulations}, Int.
+J.
+Multiphase Flow 29 (1) (2003) 109-116
+
+\bibitem{ShanChen1} {\sc X. Shan, H. Chen}, {\em Lattice Boltzmann model for simulation flows with multiple phases and components}, Phys. Rev. E 47 (3) (1999) 567-603
+
+\bibitem{ShanChen2} {\sc X. Shan, H. Chen}, {\em Simulation of nonideal gases and liquid-gas phase transition by the Lattice Boltzmann equation}, Phys. Rev. E 49 (4) (1994) 2941
 

### 2015-11-07 Paper/paper.tex
am Paper weitergeschrieben

@@
 
+\usepackage{amsmath}
+
 \title{Implementation of a lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}
@@
 The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids.
-To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (PICTURE).
-{\it continue here...}
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (Fig.
+\ref{intro_phases}).
+The material properties in each fluid are constant and the interface is assumed to be sharp.
+Thus the material properties are discontinuous and the fluids won't mix.
 
-% Not done with this chapter ...
+\begin{figure}[h!]
+	\flushright
+	\includegraphics[width=12cm,natwidth=1690,natheight=1174]{skizze.png}
+	\caption{Two fluid domains $\Omega_i$ and the interface $\Gamma$ in between}
+	\label{intro_phases}
+\end{figure}
+
+The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations:
+\begin{equation}
+	\nabla \cdot  \vec u_i = 0 \text{  in } \Omega_i \text{,}
+\end{equation}
+\begin{equation}
+\frac{\partial \vec u_i}{\partial t} + \left(\vec  u_i\cdot \nabla \right) \vec u_i
+=
+-\frac{1}{\varrho_i}\nabla p_i + \nu_i \nabla^2 \vec u_i \text{  in } \Omega_i \text{.}
+\end{equation}
+Here, $v_i$ is the velocity, $p_i$ the pressure, $v_i$ the kinematic viscosity and $\varrho_i$ the mass density.
+
+Furthermore, we need boundary conditions and initial conditions. For our domain-boundaries and the interior we can take for example
+\begin{equation}
+	u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,}
+\end{equation}
+\begin{equation}
+	u_i(x,0) = u_{ini,i}(x) \text{, in } \Omega_i \text{.}
+\end{equation}
+For the interface $\Gamma$ we have the influence of the surface tension and we assume continuity of the velocities within the fluids. Therefore, we get the following jump conditions:
+\begin{equation}
+	[u] = 0 \text{,  } [T]n = 2 \sigma \kappa n \text{.}
+	\label{jumpconditions}
+\end{equation}
+Here, T is the stress tensor, $\sigma$ the surface tension, $\kappa = \frac{1}{2}(\kappa_1 + \kappa_2)$ the mean curvature with respect to the surface normal $n$.
+Brackets denote the jump of a quantity: $[q](x) = \lim_{\epsilon \rightarrow 0} (q(x + \epsilon n) - (q(x - \epsilon n))$.
 
@@
 This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
-Furthermore there are free surface methods which only take one fluid in account for computation (REFERENCE!).
+Furthermore there are free surface methods which only take one fluid in account for computation (\cite{Koerner}).
 They work best for big density and viscosity differences.
 
+The method we are presenting uses a hybrid lattice Boltzmann level set method.
+Thereby the surface motion is calculated by the level set method.
+The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
+This method has the advantage that it has a high accuracy but requires only little memory.
+
+This paper is organized as follows: Section 2 gives a short introduction to the numerical methods and the coupling of these.
+In section 3 we present our results and finally in section 4 we draw a conclusion.
+
 \section{Numerical Methods}
-Describe the basic concepts of how the methods work. Just as a short introduction to the subsections.
+The method contains two different numerical methods. Before we show how these can be coupled, we will shortly introduce the numerical methods independently.
 
 \subsection{The Lattice Boltzmann Method}
-Explain LBM and introduce the most important formulas we use. Give references for further reading?
+To solve the incompressible Naver-Stokes equations, we use the lattice Boltzmann method. This method consists of two steps. The streaming step and the collision step.
+\begin{equation}
+	\rho(x,t) = \sum_{i=0}^{8} f_i(x,t) \text{, } 
+	u = \sum_{i=0}^{8} f_i(x,t)c_i
+\end{equation}
+\begin{equation}
+	f_i(x+c_i,t+1) = f_i(x,t) - \omega(f_i-f_i^{eq}) + G_i
+\end{equation}
+\begin{equation}
+	f_i^{eq}(f) = f_i^*(\rho + 3c_i \cdot u + \frac92(c_i \cdot u)^2 - \frac32u^2)
+\end{equation}
+$$
+f_i^* = \begin{cases} \frac49 & i = C \\ \frac19 & i = N,E,S,W \\ \frac{1}{36} &  i = NE,SE,SW,NW \end{cases}
+$$
+NOT DONE WITH THIS CHAPTER!
 
 \subsection{The Level Set Method}
-Explain level set method and the level set equation. Introduce the Ian Mitchell Toolbox.
+We deal with the movement of the interface between the two fluids by using the level set method.
+The method captures the surface that represents the interface with a continuous signed distance function which has the interface as the zero level set.
+
+Let $\Gamma_t$ be our interface at time t.
+Within the level set method, $\Gamma_t$ is the zero iso-surface of the level set function $\varphi$.
+Thus for $x \in \Gamma_t$ we have $\varphi(x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
+For this level set function we get the level set equation of Osher and Sethian \cite{OsherSethian} for the evolution of free surfaces
+\begin{equation}
+	\varphi_t + v \cdot \nabla \varphi = 0 \text{,}
+\end{equation}
+with the velocity $v = v(x(t)) = \dot x(t)$ for $x(t) \in \Gamma_t$.
+
+To solve this equation we use the Toolbox of Ian Mitchell \cite{mitchell}.
+This toolbox takes as input the velocity field we get from the lattice Boltzmann method and computes the movement of the interface.
+The toolbox also provides functions to calculate the normal and the curvature of the surface.
+We will need this informations for the coupling of the methods.
 
 \subsection{Coupling of LBM and level set method}
-Present the new boundary condition but without all the formula deriving we have in the Th\"ommes-paper.
-Maybe explain the refill method?
-Show Fig.2 of the Th\"ommes-paper and explain the coupling of the two methods.
+The lattice Boltzmann method requires a boundary treatment at the interface which implements the jump conditions (\ref{jumpconditions}).
+We use a new boundary condition that is based on a simple bounce back type Dirichlet condition.
+For example, in Fig.
+\ref{intro_phases} for a point $x_2 \in \Omega_2$ that is next to the boundary we set
+% TODO: zweites Bild einfügen mit x_1, x_2 und c_i
+\begin{equation}
+	f_i(x_2,t+1) = f_{i*}^+(x_2,t) + 6hf_i^*c_i \cdot \tilde{u} + R_i \text{.}
+\end{equation}
+Here, $\tilde{u}$ describes the linear interpolation of the velocity along the direction $c_i$, evaluated at the location $\tilde{x} = x_1 + qc_i = x_2 + (q-1)c_i$ on the interface,
+$$
+\tilde{u} = qu(x_2,t) + (1-q)u(x_1,t) \text{.}
+$$
+The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that are caused by the bounce back treatment. $R_i$ is given as:
+\begin{equation}
+	R_i = 6 h^2 f_i^* \Lambda_i : A \text{ with } A = -q(1-q)[S] - (q - \frac12)S^{(2)} \text{.}
+\end{equation}
+We can rewrite the formula in the form
+\begin{equation}
+	R_i = 6h^2f_i^* \cdot (-q(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S^{(2)} \text{,}
+\end{equation}
+with
+\begin{equation}
+	S^{(k)} = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k)
+\end{equation}
+\begin{equation}
+	\Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - {|c_i|}^2/3) + 2([S]:n \otimes t_k)(n \cdot c_i)(t_k \cdot c_i) \text{.}
+\end{equation}
+For the calculation we use
+\begin{equation}
+	[S]:n \otimes n =  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,}
+\end{equation}
+\begin{equation}
+	[S]:n \otimes t_k = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t_k \text{.}
+\end{equation}
+The pressure jump is formulated by
+\begin{equation}
+	[p] \approx \frac{1}{3 h^2} (\rho(x_1,t)\varrho^{(1)} - \rho(x_2,t)\varrho^{(2)}) \text{.}
+\end{equation}
+We use now the information of the level set method for the new boundary condition.
+What is missing now, is a refill method.
+Due to the fact that the interface moves, some cells change their fluid type.
+To do so we use a equilibrium/non-equilibrium refill (CITE).
+This refill procedure consists out of four steps:
+\begin{itemize}
+	\item[1] Interpolate density and velocity from interior neighbors
+	\item[2] Compute the corresponding equilibrium
+	\item[3] Copy the non-equilibrium part from a direct interior neighbor
+	\item[4] Reinitialise by adding equilibrium and non-equilibrium parts
+\end{itemize}
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g.
+the direction of smallest angle with the surface normal.
+Then the density is interpolated in the following way:
+\begin{equation}
+	\tilde{p} = 3\rho(x-c_i,t+1) - 3\rho(x-2c_i,t+1) + \rho(x-3c_i,t+1) \text{.}
+\end{equation}
+To interpolate u we choose ....
+The same procedure has to be used in the second fluid $\Omega_2$.
+
+TODO: Explain the refill method. Show Fig.2 of the Th\"ommes-paper and explain the coupling of the two methods.
 
@@
 
-%\bibitem{GoMiSa} {\sc M. Goossens, F. Mittelbach, and A. Samarin},
-%{\em The} \LaTeX\ {\em Companion}, Addison-Wesley, Reading, MA, 1994.
+% Richtige Abkürzung fehlt hier!!!
+\bibitem{Koerner} {\sc C.
+K\"orner, M.
+Thies, T.
+Hofmann, N.
+Th\"urey, U.
+R\"ude}, {\em Lattice Boltzmann Model for Free Surface Flow for Modeling Foaming}, J.
+Statistical Physics Vol.
+121 (2005) 179-196
 
-%\bibitem{Higham} {\sc N.~J. Higham}, {\em Handbook of Writing for
-%the Mathematical Sciences}, Society for Industrial and Applied
-%Mathematics, Philadelphia, PA, 1993.
+\bibitem{OsherSethian} {\sc S. Osher, J. Sethian}, {\em Fronts propagating with curvature-dependent speed: algorithms based on Hamlton-Jacobi formulations}, J. Comput. Phys. 79 (1988) 12-49
 
-%\bibitem{Lamport} {\sc L. Lamport}, \LaTeX: {\em A Document
-%Preparation System}, Addison-Wesley, Reading, MA, 1986.
+\bibitem{mitchell}
+Mitchell, Ian, A Toolbox of Level Set Methods
 
-%\bibitem{SerLev} {\sc R. Seroul and S. Levy}, {\em A
-%Beginner's Book of} \TeX, Springer-Verlag, Berlin, New
-%York, 1991.
 \end{thebibliography}

### 2015-11-07 Paper/paper.tex
Paper: das meiste ist jetzt da. Results und Conclusion fehlen noch.

@@
 \begin{equation}
-	S^{(k)} = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k)
+	S^{(k)} = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{,}
 \end{equation}
@@
 \end{equation}
+Here $n$ is the normal of the interface, $t$ the tangential, $\kappa$ the curvature, and $\mu$ the dynamic viscosity.
 The pressure jump is formulated by
@@
 Due to the fact that the interface moves, some cells change their fluid type.
-To do so we use a equilibrium/non-equilibrium refill (CITE).
-This refill procedure consists out of four steps:
+We use a equilibrium/non-equilibrium refill (CITE) that consists out of four steps:
 \begin{itemize}
@@
 \end{itemize}
-Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g.
-the direction of smallest angle with the surface normal.
-Then the density is interpolated in the following way:
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g. the direction of smallest angle with the surface normal. Then the density is interpolated by
 \begin{equation}
-	\tilde{p} = 3\rho(x-c_i,t+1) - 3\rho(x-2c_i,t+1) + \rho(x-3c_i,t+1) \text{.}
+	\tilde{\rho} = 3\rho(x-c_i,t+1) - 3\rho(x-2c_i,t+1) + \rho(x-3c_i,t+1) \text{.}
 \end{equation}
-To interpolate u we choose ....
-The same procedure has to be used in the second fluid $\Omega_2$.
+In \cite{Thoemmes} the velocity is interpolated by using the velocity of the interface.
+The Ian-Mitchell toolbox does not provide a function to access this value.
+Therefore, we interpolate the velocity in the same way as we did for the density:
+\begin{equation}
+\tilde{u} = 3u(x-c_i,t+1) - 3u(x-2c_i,t+1) + u(x-3c_i,t+1) \text{.}
+\end{equation}
+We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor, $f_i^{neq}(x-c_i,t+1)$.
+The same procedure has also to be applied in the second fluid $\Omega_2$.
 
-TODO: Explain the refill method. Show Fig.2 of the Th\"ommes-paper and explain the coupling of the two methods.
+Finally we couple the two methods in the following way:
+\begin{itemize}
+	\item[1.] Create the initial interface $\Gamma_0$
+	\item[2.] Run the level set code once to create the surface description for LBM
+	\item[3.] Run the LBM using the data from the level set for a prescribed number of steps
+	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. MISSING)
+	\item[5.] Repeat step 3 and 4 until the end of the simulation.
+\end{itemize}
 

### 2015-11-09 Paper/paper.tex
Bilder und ein paar Verbesserungen

@@
 For example, bubble dynamics are decisive for the design of chemical reactors.
-Also fingering in oil recovery is a common problem that can be seen as a immiscible two-phase problem.
+Also fingering in oil recovery is a common two-phase problem.
 
@@
 \end{equation}
-Here, $v_i$ is the velocity, $p_i$ the pressure, $v_i$ the kinematic viscosity and $\varrho_i$ the mass density.
+Here, $u_i$ is the velocity, $p_i$ the pressure, $v_i$ the kinematic viscosity and $\varrho_i$ the mass density.
 
@@
 \end{equation}
-Here, T is the stress tensor, $\sigma$ the surface tension, $\kappa = \frac{1}{2}(\kappa_1 + \kappa_2)$ the mean curvature with respect to the surface normal $n$.
-Brackets denote the jump of a quantity: $[q](x) = \lim_{\epsilon \rightarrow 0} (q(x + \epsilon n) - (q(x - \epsilon n))$.
+Here, T is the stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its normal $n$.
+Brackets denote the jump of a quantity at the interface: $[q](x) = \lim_{\epsilon \rightarrow 0} (q(x + \epsilon n) - (q(x - \epsilon n)) \text{ with } x \in \Gamma$.
 
@@
 
-This paper is organized as follows: Section 2 gives a short introduction to the numerical methods and the coupling of these.
+This paper is organized as follows: Section 2 gives an introduction to the numerical methods and the coupling of these.
 In section 3 we present our results and finally in section 4 we draw a conclusion.
@@
 \section{Numerical Methods}
-The method contains two different numerical methods. Before we show how these can be coupled, we will shortly introduce the numerical methods independently.
+The algorithm uses two numerical methods. Before we show how these can be coupled, we will shortly introduce the numerical methods independently.
 
 \subsection{The Lattice Boltzmann Method}
-To solve the incompressible Naver-Stokes equations, we use the lattice Boltzmann method. This method consists of two steps. The streaming step and the collision step.
+To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
+This method describes the evolution of the particle density $f(x,v,t)$ in phase space, with a $(x,v)$ as the phase space variables and $t$ as time.
+The LBM algorithm discretizes with a regular grid in space and with restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
+We use the D2Q9 model in 2D, which has 9 velocity vectors on a plane grid with unit spacing including one zero velocity (Fig.
+\ref{lbmc_i}).
+\begin{figure}
+	\hfill\includegraphics[width=6cm,natwidth=352,natheight=352]{LBMc_i.png}\hspace*{\fill}
+	\caption{The vectors of one cell in LBM}
+	\label{lbmc_i}
+\end{figure}
+The vectors are given by the columns of the matrix
+\begin{equation}
+	c = 
+	\begin{bmatrix}
+	0 & 0 & 1 & 1 &  1 &  0 & -1 & -1 & -1 \\
+	0 & 1 & 1 & 0 & -1 & -1 & -1 &  0 &  1
+	\end{bmatrix}
+	\text{.}
+\end{equation}
+The corresponding particle distributions are denoted by $f_i(x,t) = f(x,c_i,t)$. We can get the density and velocity from the particle distribution functions by calculating:
 \begin{equation}
 	\rho(x,t) = \sum_{i=0}^{8} f_i(x,t) \text{, } 
-	u = \sum_{i=0}^{8} f_i(x,t)c_i
+	u = \sum_{i=0}^{8} f_i(x,t)c_i \text{.}
 \end{equation}
+For the collision step we use the Bhatnagar-Gross-Krook (BGK) approximation \cite{BGK}
 \begin{equation}
-	f_i(x+c_i,t+1) = f_i(x,t) - \omega(f_i-f_i^{eq}) + G_i
+	f_i(x+c_i,t+1) = f_i(x,t) - \frac1\tau(f_i-f_i^{eq}) + G_i \text{.}
 \end{equation}
+The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity $\nu = \frac16(2\tau - 1)$. Furthermore, we use the equilibrium distribution
 \begin{equation}
@@
 \end{equation}
+with the corresponding D2Q9 weight factors
 $$
-f_i^* = \begin{cases} \frac49 & i = C \\ \frac19 & i = N,E,S,W \\ \frac{1}{36} &  i = NE,SE,SW,NW \end{cases}
+f_i^* = \begin{cases} \frac49 \text{,} & i = 0 \\ \frac19 \text{,} & i = 1,3,5,7 \\ \frac{1}{36} \text{,} &  i = 2,4,6,8 \end{cases} \text{.}
 $$
-NOT DONE WITH THIS CHAPTER!
+
+The LBM algorithm consists out of the following steps:
+\begin{itemize}
+	\item[1. ] Collision step: $f_i^+ = f_i - \frac1\tau(f_i - f_i ^{eq}) + G_i$
+	\item[2. ] Propagation step: $f_i(x+c_i,t+1) = f_i^+(x,t)$, for interior nodes
+	\item[3. ] Boundary conditions: $f_i(x+c_i,t+1) = f_i(x+c_i,t)$, if $x \notin \Omega$
+\end{itemize}
 
@@
 \begin{equation}
-	R_i = 6h^2f_i^* \cdot (-q(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S^{(2)} \text{,}
+	R_i = 6h^2f_i^* \cdot (-q(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S_2 \text{,}
 \end{equation}
@@
 \begin{equation}
-	S^{(k)} = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{,}
+	S_k = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{,}
 \end{equation}
@@
 \begin{equation}
-	[p] \approx \frac{1}{3 h^2} (\rho(x_1,t)\varrho^{(1)} - \rho(x_2,t)\varrho^{(2)}) \text{.}
+	[p] \approx \frac{1}{3 h^2} (\rho(x_1,t)\varrho_1 - \rho(x_2,t)\varrho_2) \text{.}
 \end{equation}
 We use now the information of the level set method for the new boundary condition.
-What is missing now, is a refill method.
+What is still missing, is a refill method.
 Due to the fact that the interface moves, some cells change their fluid type.
-We use a equilibrium/non-equilibrium refill (CITE) that consists out of four steps:
+We use an equilibrium/non-equilibrium refill as it is described in \cite{Caiazzo} that consists out of four steps:
 \begin{itemize}
@@
 \end{itemize}
-Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g. the direction of smallest angle with the surface normal. Then the density is interpolated by
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g. the direction of biggest angle with the surface normal. Then the density is interpolated by
 \begin{equation}
-	\tilde{\rho} = 3\rho(x-c_i,t+1) - 3\rho(x-2c_i,t+1) + \rho(x-3c_i,t+1) \text{.}
+	\tilde{\rho} = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1) \text{.}
 \end{equation}
+\begin{figure}[h]
+	\hfill\includegraphics[width=8cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
+	\caption{Cells that are used for the refill method}
+	\label{refill}
+\end{figure}
+Figure \ref{refill} shows the cells we use for the interpolation.
 In \cite{Thoemmes} the velocity is interpolated by using the velocity of the interface.
@@
 \begin{equation}
-\tilde{u} = 3u(x-c_i,t+1) - 3u(x-2c_i,t+1) + u(x-3c_i,t+1) \text{.}
+\tilde{u} = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1) \text{.}
 \end{equation}
-We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor, $f_i^{neq}(x-c_i,t+1)$.
+We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor, $f_i^{neq}(x+c_i,t+1)$.
 The same procedure has also to be applied in the second fluid $\Omega_2$.
-
+\begin{figure}[h]
+	\hfill\includegraphics[width=8cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
+	\caption{Data exchange between LBM and level set method}
+	\label{dataexchange}
+\end{figure}
 Finally we couple the two methods in the following way:
@@
 	\item[3.] Run the LBM using the data from the level set for a prescribed number of steps
-	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. MISSING)
+	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. \ref{dataexchange})
 	\item[5.] Repeat step 3 and 4 until the end of the simulation.
@@
 
+\bibitem{LBM1} {\sc S. Chen, G.D. Doolenm}, {\em Lattice Boltzmann method for fluid flows}, Ann. Rev. Fluid Mech. 30 (1998) 329-364
+
+\bibitem{LBM2} {\sc X. He, L.S. Luo}, {\em Lattice Boltzmann model for the incompressible Navier-Stokes equation}, J. Stat. Phys. 88 (1997) 927-944
+
+\bibitem{LBM3} {\sc Sauro Succi}, {\em The Lattice Boltzmann Equation for Fluid Dynamics and Beyond}, Clarendon Press, Oxford, 2001
+
+\bibitem{LBM4} {\sc D.A. Wolf-Gladow}, {\em Lattice-Gas Cellular Automata and Lattice Boltzmann Models}, An Introduction, Springer, 2000
+
+\bibitem{BGK} {\sc P.
+Bhatnagar, E.
+Gross, M.
+Krook}, {\em A model for collision processes in gases: 1.
+Small amplitude processes in charged and neutral one-component systems}, Phys.
+Rev.
+94 (1954) 511
+
 \bibitem{OsherSethian} {\sc S. Osher, J. Sethian}, {\em Fronts propagating with curvature-dependent speed: algorithms based on Hamlton-Jacobi formulations}, J. Comput. Phys. 79 (1988) 12-49
@@
 
+\bibitem{Caiazzo} {\sc A. Caiazzo}, {\em Asymptotic analysis of lattice Boltzmann method for fluid-structure interaction problems}, Ph.D. Thesis, Kaiserslautern (Germany) and Pisa (Italy), 2007
+
 \end{thebibliography}

### 2015-11-10 Paper/paper.tex
Kapitel 2 sollte nun inhaltlich passen.

@@
 Chair for System-Simulation, Friedrich Alexander Univerit\"at Erlangen-N\"urnberg\\
-91058 Erlangen, Germany % ist das so richtig?
+Cauerstr. 11, 91058 Erlangen, Germany\\
+lorenz.hufnagel@studium.uni-erlangen.de\\
+daniel.zint@fau.de % ist das so richtig?
 }
@@
 \end{equation}
-Here, T is the stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its normal $n$.
-Brackets denote the jump of a quantity at the interface: $[q](x) = \lim_{\epsilon \rightarrow 0} (q(x + \epsilon n) - (q(x - \epsilon n)) \text{ with } x \in \Gamma$.
+Here, T is the stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its normal $n$. Brackets denote the jump of a quantity at the interface: 
+$[q](x) = \lim_{\epsilon \rightarrow 0} (q(x - \epsilon n) - (q(x + \epsilon n)) \text{ with } x \in \Gamma$ % I also turned this around, according to [p].
+. In Fig. \ref{intro_phases} this would be the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
 
@@
 To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
-This method describes the evolution of the particle density $f(x,v,t)$ in phase space, with a $(x,v)$ as the phase space variables and $t$ as time.
+This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with a $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
 The LBM algorithm discretizes with a regular grid in space and with restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
@@
 \begin{figure}
-	\hfill\includegraphics[width=6cm,natwidth=352,natheight=352]{LBMc_i.png}\hspace*{\fill}
+	\hfill\includegraphics[width=6cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
 	\caption{The vectors of one cell in LBM}
@@
 \end{equation}
-The corresponding particle distributions are denoted by $f_i(x,t) = f(x,c_i,t)$. We can get the density and velocity from the particle distribution functions by calculating:
+The corresponding particle distributions are denoted by $f_i(\vec{x},t) = f(\vec{x},\vec{c_i},t)$. We get the density and velocity from the particle distribution functions with:
 \begin{equation}
-	\rho(x,t) = \sum_{i=0}^{8} f_i(x,t) \text{, } 
-	u = \sum_{i=0}^{8} f_i(x,t)c_i \text{.}
+	\rho(\vec{x},t) = \sum_{i=0}^{8} f_i(\vec{x},t) \text{, } 
+	\vec{u} = \sum_{i=0}^{8} f_i(\vec{x},t)\vec{c_i} \text{.}
 \end{equation}
@@
 \begin{equation}
-	f_i(x+c_i,t+1) = f_i(x,t) - \frac1\tau(f_i-f_i^{eq}) + G_i \text{.}
+	f_i(\vec{x}+\vec{c_i},t+1) = f_i(\vec{x},t) - \frac1\tau(f_i-f_i^{eq}) + G_i \text{.}
 \end{equation}
-The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity $\nu = \frac16(2\tau - 1)$. Furthermore, we use the equilibrium distribution
+The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity $\nu = \frac16(2\tau - 1)$.
+$G_i$ is an additional force like gravity or a magnetic field.
+In our case we set $G_i = 0$.
+Furthermore, we use the equilibrium distribution
 \begin{equation}
-	f_i^{eq}(f) = f_i^*(\rho + 3c_i \cdot u + \frac92(c_i \cdot u)^2 - \frac32u^2)
+	f_i^{eq}(\rho,\vec{u}) = f_i^*(\rho + 3\vec{c_i} \cdot \vec{u} + \frac92(\vec{c_i} \cdot \vec{u})^2 - \frac32{|\vec{u}|}^2)
 \end{equation}
@@
 	\item[1. ] Collision step: $f_i^+ = f_i - \frac1\tau(f_i - f_i ^{eq}) + G_i$
-	\item[2. ] Propagation step: $f_i(x+c_i,t+1) = f_i^+(x,t)$, for interior nodes
-	\item[3. ] Boundary conditions: $f_i(x+c_i,t+1) = f_i(x+c_i,t)$, if $x \notin \Omega$
+	\item[2. ] Propagation step: $f_i(\vec{x}+\vec{c_i},t+1) = f_i^+(x,t)$, for interior nodes
+	\item[3. ] Boundary conditions: $f_i(\vec{x}+\vec{c_i},t+1) = f_i(\vec{x}+\vec{c_i},t)$, if $\vec{x} \notin \Omega$
 \end{itemize}
@@
 
-To solve this equation we use the Toolbox of Ian Mitchell \cite{mitchell}.
+To solve this equation we use the Toolbox of Ian Mitchell \cite{mitchell} for Matlab.
 This toolbox takes as input the velocity field we get from the lattice Boltzmann method and computes the movement of the interface.
@@
 The lattice Boltzmann method requires a boundary treatment at the interface which implements the jump conditions (\ref{jumpconditions}).
-We use a new boundary condition that is based on a simple bounce back type Dirichlet condition.
+For sake of simplicity, we don't write arrows for every vector, i.e.
+$\vec{u} \rightarrow u$.
+One should consider that every position, direction, and velocity is two-dimensional.
+
+For the coupling, we create a new boundary condition that is based on a simple bounce back type Dirichlet condition.
 For example, in Fig.
-\ref{intro_phases} for a point $x_2 \in \Omega_2$ that is next to the boundary we set
-% TODO: zweites Bild einfügen mit x_1, x_2 und c_i
+\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the boundary we set
+\begin{figure}
+	\hfill\includegraphics[width=10cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
+	\caption{link between two points in different fluids}
+	\label{coupling}
+\end{figure}
 \begin{equation}
@@
 \begin{equation}
-	S_k = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{,}
+\Lambda_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbf{I} \text{,}
 \end{equation}
 \begin{equation}
-	\Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - {|c_i|}^2/3) + 2([S]:n \otimes t_k)(n \cdot c_i)(t_k \cdot c_i) \text{.}
+	S_k = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
 \end{equation}
-For the calculation we use
+The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. Furthermore, we have
+\begin{equation}
+	\Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - {|c_i|}^2/3) + 2([S]:n \otimes t_k)(n \cdot c_i)(t_k \cdot c_i) \text{,}
+\end{equation}
+with the terms
 \begin{equation}
@@
 \end{equation}
-Here $n$ is the normal of the interface, $t$ the tangential, $\kappa$ the curvature, and $\mu$ the dynamic viscosity.
+Here $n$ is the normal of the interface, $t$ the tangential, $\bar{S} = (S_1 + S_2)/2$ the averaged symmetric velocity gradient, $\kappa$ the curvature, and $\mu$ the dynamic viscosity, with $[\mu] = \mu_2 - \mu_1$ as its jump.
 The pressure jump is formulated by
 \begin{equation}
-	[p] \approx \frac{1}{3 h^2} (\rho(x_1,t)\varrho_1 - \rho(x_2,t)\varrho_2) \text{.}
+	[p] \approx \frac{1}{3 h^2} (\rho(x_2,t)\varrho_2 - \rho(x_1,t)\varrho_1) \text{.}
 \end{equation}
-We use now the information of the level set method for the new boundary condition.
 What is still missing, is a refill method.
@@
 \end{itemize}
-Suppose we choose an inward pointing direction $c_i$ in a boundary point $x = x_b \in \Omega_1$, e.g. the direction of biggest angle with the surface normal. Then the density is interpolated by
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x \in \Omega_1$, e.g. the direction of biggest angle with the surface normal. Then the density is interpolated by
 \begin{equation}
@@
 \end{equation}
-\begin{figure}[h]
+\begin{figure}
 	\hfill\includegraphics[width=8cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
@@
 \end{equation}
-We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor, $f_i^{neq}(x+c_i,t+1)$.
-The same procedure has also to be applied in the second fluid $\Omega_2$.
-\begin{figure}[h]
+We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor:
+$$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
+We have to repeat the procedure for other fluid.
+\begin{figure}
 	\hfill\includegraphics[width=8cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
@@
 \end{figure}
-Finally we couple the two methods in the following way:
+
+Finally, we can couple the two methods in the following way:
 \begin{itemize}

### 2015-11-11 Paper/paper.tex
Results angefangen. Parameterangaben und Plots fehlen noch.

@@
 	\flushright
-	\includegraphics[width=12cm,natwidth=1690,natheight=1174]{skizze.png}
+	\includegraphics[width=11cm,natwidth=1690,natheight=1174]{skizze.png}
 	\caption{Two fluid domains $\Omega_i$ and the interface $\Gamma$ in between}
@@
 To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
-This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with a $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
+This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
 The LBM algorithm discretizes with a regular grid in space and with restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
@@
 
-The LBM algorithm consists out of the following steps:
+One time step in the LBM algorithm is achieved by the following sub-steps:
 \begin{itemize}
@@
 \end{equation}
-We can rewrite the formula in the form
+We can rewrite $R_i$ in the form
 \begin{equation}
@@
 The Ian-Mitchell toolbox does not provide a function to access this value.
-Therefore, we interpolate the velocity in the same way as we did for the density:
+Therefore, we follow the formula given in \cite{Lallemand} that is basically the same we use for density:
 \begin{equation}
@@
 
-\section{something new what we did / Results}
-Present our test case (I think one would be enough) and describe the parameters we have studied. Give graphs that show their impact on accuracy.
+\section{Results and Examples}
+To verify the correctness of our implementation we firstly created a Couette flow and compared our results with the one we get from the analytic solution.
+Secondly, we used the same LBM setup but with a different fluid distribution to check the behavior of our implementation for more complex problems.
+
+\subsection{Couette channel flow}
+The Couette channel flow consists of a fixed lower wall at $y=0$ and an upper wall at $y=1$ that is moving with a constant velocity.
+At these walls we use no-slip boundary conditions.
+To create a channel flow, we use periodic boundary conditions for the boundaries at the inflow $x=0$ and the outflow $x=1$.
+The two fluids are distributed in a way that the interface is parallel to our walls.
+%TODO: give information about the parameter
+%TODO: show graph with results
+
+For the Couette channel flow exists an analytic solution that can be derived from the Navier-Stokes equations
+$$
+v(x) = \begin{cases} v_0 (\frac{\mu_1}{\mu_1+\mu_2}x + \frac{\mu_2}{\mu_1+\mu_2}) \text{,} & x \ge 0 \\ v_0 (\frac{\mu_2}{\mu_1+\mu_2}x + \frac{\mu_2}{\mu_1+\mu_2}) \text{,} & x < 0 \text{,}\end{cases}
+$$
+where $\mu_1$ denotes the dynamic viscosity in the lower fluid and $\mu_2$ the viscosity in upper fluid.
+
+\subsection{Bubble tracing}
+To verify the correctness of our implementation also for more complex problems, we changed the fluid distribution in our Couette channel flow such that one fluid is a bubble within the other fluid.
+We set all material parameters of the fluids to the same values.
+Thus one would expect that we get the same flow field as for only a single fluid and the interface merely serves as a tracer.
+FIGURE ??
+shows how the bubble that is initialized as circle changes to an elliptic shape caused by the flow field within the channel.
+
+%TODO: name the settings we used
+%TODO: add some nice pictures
 
@@
 
+\bibitem{Lallemand} {\sc P. Lallemand, L.-S. Luo}, {\em Lattice Boltzmann method for moving boundaries}, J. Comput. Phys. 184 (2003) 406-421
+
 \end{thebibliography}

### 2015-11-11 Paper/paper.tex
Kleine Änderungen am Paper
Wir sollten vlt auch noch auf doi:10.1016/j.camwa.2009.02.005
referenzieren (das zweie Thoemmes paper)

--- 2015-11-10 Paper/paper.tex
@@
 \end{equation}
-Here, $u_i$ is the velocity, $p_i$ the pressure, $v_i$ the kinematic viscosity and $\varrho_i$ the mass density.
+Here, $u_i$ is the velocity, $p_i$ the pressure, $\nu_i$ the kinematic viscosity and $\varrho_i$ the mass density.
 
@@
 \begin{equation}
-	u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,}
+	\vec u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,}
 \end{equation}
 \begin{equation}
-	u_i(x,0) = u_{ini,i}(x) \text{, in } \Omega_i \text{.}
+	\vec u_i(x,0) = \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
 \end{equation}
-For the interface $\Gamma$ we have the influence of the surface tension and we assume continuity of the velocities within the fluids. Therefore, we get the following jump conditions:
+For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e.
+continuity of the velocities between the fluid phases.
+Therefore, we get the following jump conditions:
 \begin{equation}
-	[u] = 0 \text{,  } [T]n = 2 \sigma \kappa n \text{.}
+	[\vec u] = 0 \text{,  } [T] \cdot \vec n = 2 \sigma \kappa \vec n \text{.}
 	\label{jumpconditions}
 \end{equation}
-Here, T is the stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its normal $n$. Brackets denote the jump of a quantity at the interface: 
-$[q](x) = \lim_{\epsilon \rightarrow 0} (q(x - \epsilon n) - (q(x + \epsilon n)) \text{ with } x \in \Gamma$ % I also turned this around, according to [p].
+Here, T is the shear stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
+Brackets denote the jump of a quantity at the interface:
+$[q](\vec x) = \lim_{\epsilon \rightarrow 0} (q(\vec x - \epsilon \vec n) - (q(\vec x + \epsilon \vec n)) \text{ with } \vec x \in \Gamma$ % I also turned this around, according to [p].
 . In Fig. \ref{intro_phases} this would be the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
@@
 The method we are presenting uses a hybrid lattice Boltzmann level set method.
-Thereby the surface motion is calculated by the level set method.
+Thereby the interface motion is calculated by the level set method.
 The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
-This method has the advantage that it has a high accuracy but requires only little memory.
+This method has the advantage that it allows for big ranges of density and viscosity ratios between the fluid phases
+and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
+.
 
@@
 \subsection{The Lattice Boltzmann Method}
-To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
+To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method (\cite{Succi}).
 This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with a $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
@@
 \begin{equation}
-	\rho(\vec{x},t) = \sum_{i=0}^{8} f_i(\vec{x},t) \text{, } 
-	\vec{u} = \sum_{i=0}^{8} f_i(\vec{x},t)\vec{c_i} \text{.}
+	\rho(\vec{x},t) = \sum_{i=1}^{9} f_i(\vec{x},t) \text{, } 
+	\vec{u} = \sum_{i=1}^{9} f_i(\vec{x},t)\vec{c_i} \text{.}
 \end{equation}
@@
 \end{equation}
-The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity $\nu = \frac16(2\tau - 1)$.
-$G_i$ is an additional force like gravity or a magnetic field.
+The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity in lattice units $\nu = \frac16(2\tau - 1)$.
+Note, that we assumed the cell spacing $\Delta x$ and the time step $\Delta t$ to be unity here.
+The lattice speed of sound equals to $c_s =\frac{1}{\sqrt{3}}$.
+$G_i$ is an additional force like gravity.
 In our case we set $G_i = 0$.
@@
 \begin{equation}
-	f_i^{eq}(\rho,\vec{u}) = f_i^*(\rho + 3\vec{c_i} \cdot \vec{u} + \frac92(\vec{c_i} \cdot \vec{u})^2 - \frac32{|\vec{u}|}^2)
+	f_i^{eq}(\rho,\vec{u}) = f_i^*(\rho + 3\vec{c_i} \cdot \vec{u} + \frac92(\vec{c_i} \cdot \vec{u})^2 - \frac32 \vec u\cdot \vec u)
 \end{equation}
@@
 \end{itemize}
+% TODO Propagation kurz im Text erklären. vlt Bounce-Back boundary conditions erklaeren?
 
@@
 We deal with the movement of the interface between the two fluids by using the level set method.
-The method captures the surface that represents the interface with a continuous signed distance function which has the interface as the zero level set.
+The method captures the surface that represents the interface with a continuous signed distance function, where the interface is implicitly given as the zero level set.
 
@@
 Within the level set method, $\Gamma_t$ is the zero iso-surface of the level set function $\varphi$.
-Thus for $x \in \Gamma_t$ we have $\varphi(x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
+Thus for $\vec x \in \Gamma_t$ we have $\varphi(\vec x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
 For this level set function we get the level set equation of Osher and Sethian \cite{OsherSethian} for the evolution of free surfaces
 \begin{equation}
-	\varphi_t + v \cdot \nabla \varphi = 0 \text{,}
+  \frac{\partial \varphi}{\partial t} + \vec v \cdot \nabla \varphi = 0 \text{,}
 \end{equation}
-with the velocity $v = v(x(t)) = \dot x(t)$ for $x(t) \in \Gamma_t$.
+with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the lattice Boltzmann method.
 
@@
 
-For the coupling, we create a new boundary condition that is based on a simple bounce back type Dirichlet condition.
+For the coupling, we create a new boundary condition that is based on a bounce back type condition, that prescribes the velocity as  Dirichlet value.
 For example, in Fig.
-\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the boundary we set
+\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set
 \begin{figure}
@@
 \begin{equation}
-	f_i(x_2,t+1) = f_{i*}^+(x_2,t) + 6hf_i^*c_i \cdot \tilde{u} + R_i \text{.}
+	f_i(x_2,t+1) = f_{i*}^+(x_2,t) + 6f_i^*c_i \cdot \tilde{u} + R_i \text{.}
 \end{equation}
@@
 $$
-The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that are caused by the bounce back treatment. $R_i$ is given as:
+The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that is introduced by the first order accurate bounce back treatment. $R_i$ is given as:
 \begin{equation}
-	R_i = 6 h^2 f_i^* \Lambda_i : A \text{ with } A = -q(1-q)[S] - (q - \frac12)S^{(2)} \text{.}
-\end{equation}
-We can rewrite the formula in the form
-\begin{equation}
-	R_i = 6h^2f_i^* \cdot (-q(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S_2 \text{,}
+	R_i = 6 f_i^* \Lambda_i : A \text{ with } A = -q(1-q)[S] - (q - \frac12)S^{(2)} \text{, }
+  \label{add_term2}
 \end{equation}
@@
 \begin{equation}
-\Lambda_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbf{I} \text{,}
+  \Lambda_i = c_i \otimes c_i - \frac12 (c_i \cdot c_i) \mathbf{I} \text{. }
 \end{equation}
+That is, an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction weighted with the interface distance and a compensation term for the interpolation error that arises, when the interface is not on the exact middle between two LBM grid cells.
+The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. We can rewrite formula (\ref{add_term2}) in the form
 \begin{equation}
-	S_k = -\frac{3}{2\tau h^2} \sum_i c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
+  R_i = 6f_i^* (-q)(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S_2 \text{,}
 \end{equation}
-The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. Furthermore, we have
+and use the following first-order estimate to obtain the shear rate from the non-equilibrium parts of the distributions (see \cite{Krueger})
 \begin{equation}
-	\Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - {|c_i|}^2/3) + 2([S]:n \otimes t_k)(n \cdot c_i)(t_k \cdot c_i) \text{,}
+  S_k = -\frac{3}{2\tau } \sum_{i=1}^9 c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
 \end{equation}
-with the terms
+Furthermore, we have
+\begin{equation}
+  \Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - \frac12 (c_i \cdot c_i)) + 2([S]:n \otimes t)(n \cdot c_i)(t \cdot c_i) \text{,}
+\end{equation}
+which is obtained by a coordinate transformation onto a basis $(n, t)$ of normal and tangential vector to the interface.
+From the fluid mechanical jump condition (\ref{jumpconditions}) and the relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen:
 \begin{equation}
@@
 \end{equation}
+and
 \begin{equation}
-	[S]:n \otimes t_k = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t_k \text{.}
+	[S]:n \otimes t = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t \text{.}
 \end{equation}
-Here $n$ is the normal of the interface, $t$ the tangential, $\bar{S} = (S_1 + S_2)/2$ the averaged symmetric velocity gradient, $\kappa$ the curvature, and $\mu$ the dynamic viscosity, with $[\mu] = \mu_2 - \mu_1$ as its jump.
-The pressure jump is formulated by
+Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the visocity jump  $[\mu] = \mu_2 - \mu_1$.
+The pressure jump is approximated by
 \begin{equation}
-	[p] \approx \frac{1}{3 h^2} (\rho(x_2,t)\varrho_2 - \rho(x_1,t)\varrho_1) \text{.}
+	[p] \approx \frac{1}{3} (\rho(x_2,t)\varrho_2 - \rho(x_1,t)\varrho_1) \text{.}
 \end{equation}
+and with that, all variables for the boundary conditions are well defined.
 What is still missing, is a refill method.
@@
 \begin{equation}
-	\tilde{\rho} = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1) \text{.}
+  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1) \text{.}
 \end{equation}
@@
 The Ian-Mitchell toolbox does not provide a function to access this value.
+%TODO das ist misverständlich.
 Therefore, we interpolate the velocity in the same way as we did for the density:
 \begin{equation}
-\tilde{u} = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1) \text{.}
+  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1) \text{.}
 \end{equation}
-We can now calculate the new equilibrium $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add it to the non-equilibrium part that we copy from the direct neighbor:
+We can now calculate the new equilibrium part of the particle densities in $x$, $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add them to the non-equilibrium part which we copy from a nearest neighbor:
 $$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
-We have to repeat the procedure for other fluid.
+This completes the refill algorithm.
+
 \begin{figure}
@@
 \end{figure}
-
 Finally, we can couple the two methods in the following way:
@@
 
-\bibitem{GRcg2} {\sc A.K. Gunstensen, D.H. Rothman}, {\em Macroscopic modeling of immiscible flows in three dimensions by a lattice Boltzman method}, Europhys. Lett. 18 (2) (1998) 157-161
+\bibitem{GRcg2} {\sc A.K. Gunstensen, D.H. Rothman}, {\em Macroscopic modeling of immiscible flows in three dimensions by a lattice Boltzmann method}, Europhys. Lett. 18 (2) (1998) 157-161
 
@@
 
-% Richtige Abkürzung fehlt hier!!!
-\bibitem{Koerner} {\sc C.
-K\"orner, M.
-Thies, T.
-Hofmann, N.
-Th\"urey, U.
-R\"ude}, {\em Lattice Boltzmann Model for Free Surface Flow for Modeling Foaming}, J.
-Statistical Physics Vol.
-121 (2005) 179-196
+\bibitem{Koerner} {\sc C. K\"orner, M. Thies, T. Hofmann, N. Th\"urey, U. R\"ude}, {\em Lattice Boltzmann Model for Free Surface Flow for Modeling Foaming}, J. Stat. Phys. 121 (2005) 179-196
 
@@
 
-\bibitem{LBM3} {\sc Sauro Succi}, {\em The Lattice Boltzmann Equation for Fluid Dynamics and Beyond}, Clarendon Press, Oxford, 2001
+\bibitem{LBM3} {\sc S. Succi}, {\em The Lattice Boltzmann Equation for Fluid Dynamics and Beyond}, Clarendon Press, Oxford, ISBN 978-0-19-850398-9 (2001)
 
@@
 
+\bibitem{Krueger} {\sc T. Kr\"uger, F. Varnik, D. Raabe}, {\em Shear stress in lattice Boltzmann simulations}, Phys. Rev. E 79 (4) (2009) 046704
+
 \end{thebibliography}

### 2015-11-11 Paper/paper.tex

@@
 \subsection{The Lattice Boltzmann Method}
-To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method (\cite{Succi}).
-This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with a $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
+To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
+This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
 The LBM algorithm discretizes with a regular grid in space and with restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
@@
 %TODO das ist misverständlich.
-Therefore, we interpolate the velocity in the same way as we did for the density:
+Therefore, we follow the formula given in \cite{Lallemand} that is basically the same we use for density:
 \begin{equation}

### 2015-11-12 Paper/paper.tex
Paper in progress

@@
 	We implemented the lattice Boltzmann method for immiscible multiphase flow simulations and combined it with the level set method according to the paper of G.
-Th\"ommes \cite{Thoemmes}.
+Th\"ommes et al.
+\cite{Thoemmes}.
 The level set method is used to calculate the movement of the interface between the two phases.
 The input for the level set method is computed by the lattice Boltzmann method.
-We reimplemented the test cases that are mentioned in the paper, to study the method-coupling and its impact on accuracy.
+We verified our implementation with different test cases.
 \end{abstract}
@@
 The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids. 
+%TODO: Hier fehlen Referenzen! ausserdem muessen noch die Gleichungen unten gelabelt werden!!!
 To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (Fig.
@@
 The material properties in each fluid are constant and the interface is assumed to be sharp.
-Thus the material properties are discontinuous and the fluids won't mix.
+Thus the material properties are discontinuous and the fluids will not mix.
 
@@
 	\includegraphics[width=11cm,natwidth=1690,natheight=1174]{skizze.png}
-	\caption{Two fluid domains $\Omega_i$ and the interface $\Gamma$ in between}
+	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
 	\label{intro_phases}
@@
 
-The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations:
+The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations
 \begin{equation}
@@
 
-Furthermore, we need boundary conditions and initial conditions. For our domain-boundaries and the interior we can take for example
+As boundary conditions and initial conditions we can take for example
+\begin{align}
+	\vec u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,} \\
+	\vec u_i(x,0) = \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
+\end{align}
+For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions
+\begin{align}
+	[\vec u] = 0 \text{,  } \\
+	[T] \cdot \vec n = 2 \sigma \kappa \vec n \text{.}
+	\label{jumpconditions}
+\end{align}
+Here, T is the shear stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
+Brackets denote the jump of a quantity at the interface,
 \begin{equation}
-	\vec u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,}
+	[q](\vec x) = \lim_{\epsilon \rightarrow 0} (q(\vec x - \epsilon \vec n) - (q(\vec x + \epsilon \vec n)) \text{ with } \vec x \in \Gamma. % I also turned this around, according to [p].
 \end{equation}
-\begin{equation}
-	\vec u_i(x,0) = \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
-\end{equation}
-For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e.
-continuity of the velocities between the fluid phases.
-Therefore, we get the following jump conditions:
-\begin{equation}
-	[\vec u] = 0 \text{,  } [T] \cdot \vec n = 2 \sigma \kappa \vec n \text{.}
-	\label{jumpconditions}
-\end{equation}
-Here, T is the shear stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
-Brackets denote the jump of a quantity at the interface:
-$[q](\vec x) = \lim_{\epsilon \rightarrow 0} (q(\vec x - \epsilon \vec n) - (q(\vec x + \epsilon \vec n)) \text{ with } \vec x \in \Gamma$ % I also turned this around, according to [p].
-. In Fig. \ref{intro_phases} this would be the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
+In Fig. \ref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
 
@@
 Furthermore there are free surface methods which only take one fluid in account for computation (\cite{Koerner}).
-They work best for big density and viscosity differences.
+They work best for big density and viscosity ratios.
 
-The method we are presenting uses a hybrid lattice Boltzmann level set method.
+In this publication we use a hybrid lattice Boltzmann level set method.
 Thereby the interface motion is calculated by the level set method.
@@
 
-This paper is organized as follows: Section 2 gives an introduction to the numerical methods and the coupling of these.
+This paper is organized as follows: Section 2 gives an introduction to the lattice Boltzmann method and the level set method and explains the coupling of these.
 In section 3 we present our results and finally in section 4 we draw a conclusion.
@@
 
-For the coupling, we create a new boundary condition that is based on a bounce back type condition, that prescribes the velocity as  Dirichlet value.
+For the coupling, we use a bounce back type boundary condition that prescribes the velocity as  Dirichlet value.
 For example, in Fig.
@@
 $$
-The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that is introduced by the first order accurate bounce back treatment. $R_i$ is given as:
+The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that is introduced by the first order accurate bounce back treatment,
 \begin{equation}
@@
   \Lambda_i:[S] = ([S]:n \otimes n)((n \cdot c_i)^2 - \frac12 (c_i \cdot c_i)) + 2([S]:n \otimes t)(n \cdot c_i)(t \cdot c_i) \text{,}
+  \label{Lambda_iTimes_S}
 \end{equation}
 which is obtained by a coordinate transformation onto a basis $(n, t)$ of normal and tangential vector to the interface.
-From the fluid mechanical jump condition (\ref{jumpconditions}) and the relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen:
-\begin{equation}
-	[S]:n \otimes n =  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,}
-\end{equation}
-and
-\begin{equation}
+From the fluid mechanical jump condition (\ref{jumpconditions}) and the relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen,
+\begin{align}
+	[S]:n \otimes n =  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,} \\
 	[S]:n \otimes t = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t \text{.}
-\end{equation}
+\end{align}
 Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the visocity jump  $[\mu] = \mu_2 - \mu_1$.
@@
 %TODO das ist misverständlich.
-Therefore, we follow the formula given in \cite{Lallemand} that is basically the same we use for density:
+Therefore, we follow the formula given in \cite{Lallemand} that is basically the same we use for density,
 \begin{equation}
@@
 \end{equation}
-We can now calculate the new equilibrium part of the particle densities in $x$, $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add them to the non-equilibrium part which we copy from a nearest neighbor:
+We can now calculate the new equilibrium part of the particle densities in $x$, $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add them to the non-equilibrium part which we copy from a nearest neighbor,
 $$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
@@
 \section{Results and Examples}
-To verify the correctness of our implementation we firstly created a Couette flow and compared our results with the one we get from the analytic solution.
-Secondly, we used the same LBM setup but with a different fluid distribution to check the behavior of our implementation for more complex problems.
+To verify the correctness of our implementation we firstly built a Couette flow and compared our results with the one we get from the analytic solution.
+Secondly, we used the Young-Laplace experiment for a bubble to validate the implementation of surface tension.
 
@@
 At these walls we use no-slip boundary conditions.
-To create a channel flow, we use periodic boundary conditions for the boundaries at the inflow $x=0$ and the outflow $x=1$.
+To generate a channel flow, we use periodic boundary conditions for the boundaries at the inflow $x=0$ and the outflow $x=1$.
 The two fluids are distributed in a way that the interface is parallel to our walls.
@@
 
-\subsection{Bubble tracing}
-To verify the correctness of our implementation also for more complex problems, we changed the fluid distribution in our Couette channel flow such that one fluid is a bubble within the other fluid.
-We set all material parameters of the fluids to the same values.
-Thus one would expect that we get the same flow field as for only a single fluid and the interface merely serves as a tracer.
-FIGURE ??
-shows how the bubble that is initialized as circle changes to an elliptic shape caused by the flow field within the channel.
+\subsection{Young-Laplace experiment for a bubble}
+The Couette-Flow is not influenced by surface tension due to the fact that the surface tension is multiplied with the curvature in Equation \ref{Lambda_iTimes_S} and the curvature is zero in the Couette-Flow.
+We use the Young-Laplace experiment to validate the implementation of surface tension.
+The pressure $p$ inside a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the Young-Laplace law
+\begin{equation}
+	p = \frac{2\sigma}{r} = 2 \sigma \kappa .
+\end{equation}
 

### 2015-11-12 ian_mitchell-toolbox/lbm/Grid.m
Laplace Testcase so halb
Es oszilliert abfallend.. allerdings muss irgendwo noch sehr viel
entdimensionalisiert werden, sonst klappen keine großen
Dichteverhältnisse.. Die Blase verändert sich fast gar nicht..

@@ -5,7 +5,6 @@ classdef Grid
     nx
     ny
     omega % Use 2-dim-Vector.... a little ugly
-    c_s
     lidVel % die gibt es nur einmal
     cells
     cells_new

### 2015-11-13 Paper/paper.tex
Laplace Testcase so halb
Es oszilliert abfallend.. allerdings muss irgendwo noch sehr viel
entdimensionalisiert werden, sonst klappen keine großen
Dichteverhältnisse.. Die Blase verändert sich fast gar nicht..
Korrekturen angefangen

@@
 The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids. 
-%TODO: Hier fehlen Referenzen! ausserdem muessen noch die Gleichungen unten gelabelt werden!!!
+%TODO Regina: Hier fehlen Referenzen! ausserdem muessen noch die Gleichungen unten gelabelt werden!!!
 To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (Fig.
@@
 
-The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations
+The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations,
 \begin{equation}
@@
 
-As boundary conditions and initial conditions we can take for example
+As boundary conditions and initial conditions we can take for example,
 \begin{align}
@@
 \end{align}
-For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions
+For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions,
 \begin{align}
@@
 \section{Numerical Methods}
-The algorithm uses two numerical methods. Before we show how these can be coupled, we will shortly introduce the numerical methods independently.
+The algorithm we describe in this paper uses the lattice Boltzmann method and the level set method.
+With the lattice Boltzmann method we calculate the velocity field for each fluid independently.
+The level set method uses this velocity field to compute the movement of the interface.
+We will shortly introduce both methods and show how they can be coupled.
 
@@
 \ref{lbmc_i}).
+%TODO Regina: Man kann auch Cref benutzen zum Zitieren
 \begin{figure}
 	\hfill\includegraphics[width=6cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
-	\caption{The vectors of one cell in LBM}
+	\caption{The vectors of one cell in LBM.}
 	\label{lbmc_i}
 \end{figure}
-The vectors are given by the columns of the matrix
+The vectors are given by the columns of the matrix,
 \begin{equation}
@@
 \end{equation}
-The corresponding particle distributions are denoted by $f_i(\vec{x},t) = f(\vec{x},\vec{c_i},t)$. We get the density and velocity from the particle distribution functions with:
+The corresponding particle distributions are denoted by $f_i(\vec{x},t) = f(\vec{x},\vec{c_i},t)$. We get the density and velocity from the particle distribution functions with,
 \begin{equation}
-	\rho(\vec{x},t) = \sum_{i=1}^{9} f_i(\vec{x},t) \text{, } 
+	\rho(\vec{x},t) = \sum_{i=1}^{9} f_i(\vec{x},t) \text{, } \quad
 	\vec{u} = \sum_{i=1}^{9} f_i(\vec{x},t)\vec{c_i} \text{.}
@@
 The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity in lattice units $\nu = \frac16(2\tau - 1)$.
-Note, that we assumed the cell spacing $\Delta x$ and the time step $\Delta t$ to be unity here.
+Note, that we assume the cell spacing $\Delta x$ and the time step $\Delta t$ to be unity here.
 The lattice speed of sound equals to $c_s =\frac{1}{\sqrt{3}}$.
-$G_i$ is an additional force like gravity.
+$G_i$ is an additional force, e.g.
+gravity.
 In our case we set $G_i = 0$.
-Furthermore, we use the equilibrium distribution
+Furthermore, we use the equilibrium distribution,
 \begin{equation}
@@
 \end{equation}
-with the corresponding D2Q9 weight factors
+with the corresponding D2Q9 weight factors,
 $$
@@
 \end{itemize}
-% TODO Propagation kurz im Text erklären. vlt Bounce-Back boundary conditions erklaeren?
+%TODO Regina: Propagation kurz im Text erklären! 
+%TODO Regina: Bounce-Back boundary conditions erklaeren!
 
@@
 Within the level set method, $\Gamma_t$ is the zero iso-surface of the level set function $\varphi$.
-Thus for $\vec x \in \Gamma_t$ we have $\varphi(\vec x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
-For this level set function we get the level set equation of Osher and Sethian \cite{OsherSethian} for the evolution of free surfaces
+Thus, for $\vec x \in \Gamma_t$ we have $\varphi(\vec x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
+For this level set function we get the level set equation introduced by Osher and Sethian in \cite{OsherSethian} for the evolution of free surfaces,
 \begin{equation}
@@
 with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the lattice Boltzmann method.
+%TODO Regina: LBM als Abkürzung einführen
 
@@
 The toolbox also provides functions to calculate the normal and the curvature of the surface.
-We will need this informations for the coupling of the methods.
+We will need this information for the coupling of the methods.
+
+%TODO Regina: die Toolbox muss anders referenziert werden in der Bibliography.
+Als URL link oder eben die Homepage, wo man das runterladen kann und wann ihr es runtergeladen haben.
+Gibt dafuer MISC in bibtex
 
@@
 The lattice Boltzmann method requires a boundary treatment at the interface which implements the jump conditions (\ref{jumpconditions}).
-For sake of simplicity, we don't write arrows for every vector, i.e.
-$\vec{u} \rightarrow u$.
+For sake of simplicity, we do not write arrows for every vector, i.e., $\vec{u} \rightarrow u$.
 One should consider that every position, direction, and velocity is two-dimensional.
@@
 For the coupling, we use a bounce back type boundary condition that prescribes the velocity as Dirichlet value. 
-For example, in Fig.
-\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set
+%TODO Regina: REF!!!
+For example, in Fig. \ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set,
 \begin{figure}
 	\hfill\includegraphics[width=10cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
-	\caption{link between two points in different fluids}
+	\caption{Link between two points in different fluids.}
 	\label{coupling}
@@
 That is, an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction weighted with the interface distance and a compensation term for the interpolation error that arises, when the interface is not on the exact middle between two LBM grid cells.
-The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. We can rewrite formula (\ref{add_term2}) in the form
+%TODO Regina: sehr langer Satz, 2-3 einfache Saetze draus machen!
+The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. We can rewrite formula (\ref{add_term2}) in the form,
 \begin{equation}
@@
 \end{equation}
-Furthermore, we have
+Furthermore, we have,
 \begin{equation}
@@
 \end{align}
-Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the visocity jump  $[\mu] = \mu_2 - \mu_1$.
-The pressure jump is approximated by
+Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the viscosity jump  $[\mu] = \mu_2 - \mu_1$.
+The pressure jump is approximated by,
 \begin{equation}
@@
 and with that, all variables for the boundary conditions are well defined.
-What is still missing, is a refill method.
+A refill method is still missing.
 Due to the fact that the interface moves, some cells change their fluid type.
-We use an equilibrium/non-equilibrium refill as it is described in \cite{Caiazzo} that consists out of four steps:
+We use an equilibrium/non-equilibrium refill as it is described in \cite{Caiazzo} consisting out of the four following steps:
 \begin{itemize}
-	\item[1] Interpolate density and velocity from interior neighbors
-	\item[2] Compute the corresponding equilibrium
-	\item[3] Copy the non-equilibrium part from a direct interior neighbor
-	\item[4] Reinitialise by adding equilibrium and non-equilibrium parts
+	\item[1] Interpolate density and velocity from interior neighbors.
+	\item[2] Compute the corresponding equilibrium.
+	\item[3] Copy the non-equilibrium part from a direct interior neighbor.
+	\item[4] Reinitialise by adding equilibrium and non-equilibrium parts.
 \end{itemize}
-Suppose we choose an inward pointing direction $c_i$ in a boundary point $x \in \Omega_1$, e.g. the direction of biggest angle with the surface normal. Then the density is interpolated by
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x \in \Omega_1$, e.g., the direction of biggest angle with the surface normal. Then the density is interpolated by,
 \begin{equation}
-  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1) \text{.}
+  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1).
 \end{equation}
@@
 	\hfill\includegraphics[width=8cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
-	\caption{Cells that are used for the refill method}
+	\caption{Cells that are used for the refill method.}
 	\label{refill}
@@
 %TODO das ist misverständlich.
-Therefore, we follow the formula given in \cite{Lallemand} that is basically the same we use for density,
+Therefore, we use the formula given in \cite{Lallemand} that is basically the same we use for density,
 \begin{equation}
-  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1) \text{.}
+  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1).
 \end{equation}
@@
 	\hfill\includegraphics[width=8cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
-	\caption{Data exchange between LBM and level set method}
+	\caption{Data exchange between LBM and level set method.}
 	\label{dataexchange}
@@
 \begin{itemize}
-	\item[1.] Create the initial interface $\Gamma_0$
-	\item[2.] Run the level set code once to create the surface description for LBM
+	\item[1.] Create the initial interface $\Gamma_0$.
+	\item[2.] Run the level set code once to create the surface description for LBM.
 	\item[3.] Run the LBM using the data from the level set for a prescribed number of steps
-	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. \ref{dataexchange})
+	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. \ref{dataexchange}).
 	\item[5.] Repeat step 3 and 4 until the end of the simulation.
@@
 The two fluids are distributed in a way that the interface is parallel to our walls.
+%TODO Regina: kleines Bild, was die RB angibt und vielleicht auch die Werte?
 %TODO: give information about the parameter

### 2015-11-13 Paper/paper.tex
Korrekturen am Paper

@@
 Cauerstr. 11, 91058 Erlangen, Germany\\
-lorenz.hufnagel@studium.uni-erlangen.de\\
+lorenz.hufnagel@fau.de\\
 daniel.zint@fau.de % ist das so richtig?
@@
 
-The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids. 
-%TODO Regina: Hier fehlen Referenzen! ausserdem muessen noch die Gleichungen unten gelabelt werden!!!
+The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids (Eq. \ref{nse1}, \ref{nse2}). 
+%TODO Regina: Hier fehlen Referenzen!
 To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (Fig.
@@
 The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations,
-\begin{equation}
+\begin{gather}
 	\nabla \cdot  \vec u_i = 0 \text{  in } \Omega_i \text{,}
-\end{equation}
-\begin{equation}
+	\label{nse1} \\
 	\frac{\partial \vec u_i}{\partial t} + \left(\vec  u_i\cdot \nabla \right) \vec u_i
@@
 	-\frac{1}{\varrho_i}\nabla p_i + \nu_i \nabla^2 \vec u_i \text{  in } \Omega_i \text{.}
-\end{equation}
+	\label{nse2}
+\end{gather}
 Here, $u_i$ is the velocity, $p_i$ the pressure, $\nu_i$ the kinematic viscosity and $\varrho_i$ the mass density.
@@
 As boundary conditions and initial conditions we can take for example,
-\begin{align}
+\begin{gather}
 	\vec u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,} \\
 	\vec u_i(x,0) = \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
-\end{align}
+\end{gather}
 For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions,
-\begin{align}
+\begin{gather}
 	[\vec u] = 0 \text{,  } \\
@@
 	\label{jumpconditions}
-\end{align}
+\end{gather}
 Here, T is the shear stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
@@
 They work best for big density and viscosity ratios.
+%TODO: Mehr Referenzen, siehe Mail
 
@@
 \subsection{The Lattice Boltzmann Method}
-To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
+To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method (LBM).
 This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
@@
 \end{equation}
-For the collision step we use the Bhatnagar-Gross-Krook (BGK) approximation \cite{BGK}
+
+In the interior, the LBM alternates collision step and propagation step. For the collision step we use the Bhatnagar-Gross-Krook (BGK) approximation \cite{BGK},
 \begin{equation}
-	f_i(\vec{x}+\vec{c_i},t+1) = f_i(\vec{x},t) - \frac1\tau(f_i-f_i^{eq}) + G_i \text{.}
+	f_i^+(\vec{x}+\vec{c_i},t+1) = f_i(\vec{x},t) - \frac1\tau(f_i-f_i^{eq}) + G_i \text{.}
+\end{equation}
+The propagation step is denoted by,
+\begin{equation}
+	f_i(\vec{x}+\vec{c_i},t+1) = f_i^+(\vec{x},t+1).
 \end{equation}
@@
 
+%Boundary Conditions: Bounce-back & moving no-slip & inflow-outflow
+We use two types of boundary conditions. To simulate static walls, we use simple bounce-back boundary conditions,
+\begin{equation}
+	\tilde{f_i} = f_{i^*}^+(\vec{x_b},t) \text{, with } \vec{x_b} \in \delta\Omega \text{,}
+\end{equation}
+where $i^*$ is the index of the opposite direction $c_{i^*} = -c_i$. To simulate a flow, we use moving no-slip boundary conditions,
+\begin{equation}
+	\tilde{f_i} = f_{i^*}^+(\vec{x_b},t) + 6 f_i^*\vec{c_i} \vec{v} \text{, with } \vec{x_b} \in \delta\Omega,
+\end{equation}
+where $\vec{v}$ is the speed of the moving wall. To enable inflow and outflow of fluids we have periodic boundary conditions,
+\begin{equation}
+	\tilde{f_i}(\vec{x_a},t) = f_i^+(\vec{x_b},t) \text{,}
+\end{equation}
+where $x_a$ and $x_b$ are points of opposite boundaries.
+
 One time step in the LBM algorithm is achieved by the following sub-steps:
@@
 \end{itemize}
-%TODO Regina: Propagation kurz im Text erklären! 
-%TODO Regina: Bounce-Back boundary conditions erklaeren!
 
@@
 \end{equation}
-with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the lattice Boltzmann method.
-%TODO Regina: LBM als Abkürzung einführen
+with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the LBM.
 
@@
 
-%TODO Regina: die Toolbox muss anders referenziert werden in der Bibliography.
-Als URL link oder eben die Homepage, wo man das runterladen kann und wann ihr es runtergeladen haben.
-Gibt dafuer MISC in bibtex
-
 \subsection{Coupling of LBM and level set method}
@@
 
-For the coupling, we use a bounce back type boundary condition that prescribes the velocity as Dirichlet value. 
-%TODO Regina: REF!!!
-For example, in Fig. \ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set,
+For the coupling, we use a bounce back type boundary condition that prescribes the velocity as Dirichlet value as described in \cite[p.
+1146]{Thoemmes}.
+For example, in Fig.
+\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set,
 \begin{figure}
@@
 \end{equation}
-That is, an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction weighted with the interface distance and a compensation term for the interpolation error that arises, when the interface is not on the exact middle between two LBM grid cells.
-%TODO Regina: sehr langer Satz, 2-3 einfache Saetze draus machen!
-The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$. We can rewrite formula (\ref{add_term2}) in the form,
+That is an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction weighted with the interface distance and a compensation term for the interpolation error.
+This error arises, when the interface is not on the exact middle between two LBM grid cells.
+The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$.
+We can rewrite formula (\ref{add_term2}) in the form,
 \begin{equation}
@@
 From the fluid mechanical jump condition (\ref{jumpconditions}) and the relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen,
-\begin{align}
+\begin{gather}
 	[S]:n \otimes n =  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,} \\
 	[S]:n \otimes t = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t \text{.}
-\end{align}
+\end{gather}
 Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the viscosity jump  $[\mu] = \mu_2 - \mu_1$.
@@
 \end{equation}
+%TODO: Kommentar, dass hier ein Fehler im Thömmes-paper ist
 and with that, all variables for the boundary conditions are well defined.
@@
 
-\bibitem{Thoemmes} {\sc G. Th\"ommes, J. Becker}, {\em A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}, J. Comput. Phys. 228 (2009), 1139-1156
+\bibitem{Thoemmes} {\sc G. TH\"OMMES, J. BECKER}, A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method, J. Comput. Phys. 228 (2009), 1139-1156.
 
-\bibitem{Adalsteinsson} {\sc D. Adalsteinsson, J.A. Sethian}, {\em A fast level set method for propagating interfaces}, J. Comput. Phys. 118 (2) (1995) 269-277
+\bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, A fast level set method for propagating interfaces, J. Comput. Phys. 118 (2) (1995) 269-277.
 
-\bibitem{GRcg1} {\sc A.K. Gunstensen, D.H. Rothman, S. Zaleski, G. Zanetti}, {\em Lattice Boltzmann model of immiscible fluids}, Phys. Rev. A 43 (8) (1991) 4320-4327
+\bibitem{GRcg1} {\sc A.K. GUNSTENSEN, D.H. ROTHMAN, S. ZALESKI, G. ZANETTI}, Lattice Boltzmann model of immiscible fluids, Phys. Rev. A 43 (8) (1991) 4320-4327.
 
-\bibitem{GRcg2} {\sc A.K. Gunstensen, D.H. Rothman}, {\em Macroscopic modeling of immiscible flows in three dimensions by a lattice Boltzmann method}, Europhys. Lett. 18 (2) (1998) 157-161
+\bibitem{GRcg2} {\sc A.K. GUNSTENSEN, D.H. ROTHMAN}, Macroscopic modeling of immiscible flows in three dimensions by a lattice Boltzmann method, Europhys. Lett. 18 (2) (1998) 157-161.
 
 \bibitem{GRcg3} {\sc K.
-Sankaranarayanan, I.G.
-Kevrekidies, S.
-Sundaresan, J.
-Lu, G.
-Tryggvason}, {\em A comparative study of lattice Boltzmann and front-tracking finite-difference methods for bubble simulations}, Int.
+SANKARANARAYANAN, I.G.
+KEVREKIDIES, S.
+SUNDARESAN, J.
+LU, G.
+TRYGGVASON}, A comparative study of lattice Boltzmann and front-tracking finite-difference methods for bubble simulations, Int.
 J.
-Multiphase Flow 29 (1) (2003) 109-116
+Multiphase Flow 29 (1) (2003) 109-116.
 
-\bibitem{ShanChen1} {\sc X. Shan, H. Chen}, {\em Lattice Boltzmann model for simulation flows with multiple phases and components}, Phys. Rev. E 47 (3) (1999) 567-603
+\bibitem{ShanChen1} {\sc X. SHAN, H. CHEN}, Lattice Boltzmann model for simulation flows with multiple phases and components, Phys. Rev. E 47 (3) (1999) 567-603.
 
-\bibitem{ShanChen2} {\sc X. Shan, H. Chen}, {\em Simulation of nonideal gases and liquid-gas phase transition by the Lattice Boltzmann equation}, Phys. Rev. E 49 (4) (1994) 2941
+\bibitem{ShanChen2} {\sc X. SHAN, H. CHEN}, Simulation of nonideal gases and liquid-gas phase transition by the Lattice Boltzmann equation, Phys. Rev. E 49 (4) (1994) 2941.
 
-\bibitem{Koerner} {\sc C. K\"orner, M. Thies, T. Hofmann, N. Th\"urey, U. R\"ude}, {\em Lattice Boltzmann Model for Free Surface Flow for Modeling Foaming}, J. Stat. Phys. 121 (2005) 179-196
+\bibitem{Koerner} {\sc C. K\"ORNER, M. THIES, T. HOFMANN, N. TH\"UREY, U. R\"UDE}, Lattice Boltzmann Model for Free Surface Flow for Modeling Foaming, J. Stat. Phys. 121 (2005) 179-196.
 
-\bibitem{LBM1} {\sc S. Chen, G.D. Doolenm}, {\em Lattice Boltzmann method for fluid flows}, Ann. Rev. Fluid Mech. 30 (1998) 329-364
+\bibitem{LBM1} {\sc S. CHEN, G.D. DOOLENM}, Lattice Boltzmann method for fluid flows, Ann. Rev. Fluid Mech. 30 (1998) 329-364.
 
-\bibitem{LBM2} {\sc X. He, L.S. Luo}, {\em Lattice Boltzmann model for the incompressible Navier-Stokes equation}, J. Stat. Phys. 88 (1997) 927-944
+\bibitem{LBM2} {\sc X. HE, L.S. LUO}, Lattice Boltzmann model for the incompressible Navier-Stokes equation, J. Stat. Phys. 88 (1997) 927-944.
 
-\bibitem{LBM3} {\sc S. Succi}, {\em The Lattice Boltzmann Equation for Fluid Dynamics and Beyond}, Clarendon Press, Oxford, ISBN 978-0-19-850398-9 (2001)
+\bibitem{LBM3} {\sc S. SUCCI}, The Lattice Boltzmann Equation for Fluid Dynamics and Beyond, Clarendon Press, Oxford, ISBN 978-0-19-850398-9 (2001).
 
-\bibitem{LBM4} {\sc D.A. Wolf-Gladow}, {\em Lattice-Gas Cellular Automata and Lattice Boltzmann Models}, An Introduction, Springer, 2000
+\bibitem{LBM4} {\sc D.A. WOLF-GLADOW}, Lattice-Gas Cellular Automata and Lattice Boltzmann Models, An Introduction, Springer, 2000.
 
-\bibitem{BGK} {\sc P.
-Bhatnagar, E.
-Gross, M.
-Krook}, {\em A model for collision processes in gases: 1.
-Small amplitude processes in charged and neutral one-component systems}, Phys.
-Rev.
-94 (1954) 511
+\bibitem{BGK} {\sc P. BHATNAGAR, E. GROSS, M. KROOK}, A model for collision processes in gases: 1. Small amplitude processes in charged and neutral one-component systems, Phys. Rev. 94 (1954) 511.
 
-\bibitem{OsherSethian} {\sc S. Osher, J. Sethian}, {\em Fronts propagating with curvature-dependent speed: algorithms based on Hamlton-Jacobi formulations}, J. Comput. Phys. 79 (1988) 12-49
+\bibitem{OsherSethian} {\sc S. OSHER, J. SETHIAN}, Fronts propagating with curvature-dependent speed: algorithms based on Hamlton-Jacobi formulations, J. Comput. Phys. 79 (1988) 12-49.
 
-\bibitem{mitchell}
-Mitchell, Ian, A Toolbox of Level Set Methods
+\bibitem{mitchell}I. MITCHELL, A Toolbox of Level Set Methods, August 2015, URL: \url{http://www.cs.ubc.ca/~mitchell/ToolboxLS/}.
 
-\bibitem{Caiazzo} {\sc A. Caiazzo}, {\em Asymptotic analysis of lattice Boltzmann method for fluid-structure interaction problems}, Ph.D. Thesis, Kaiserslautern (Germany) and Pisa (Italy), 2007
+\bibitem{Caiazzo} {\sc A. CAIAZZO}, Asymptotic analysis of lattice Boltzmann method for fluid-structure interaction problems, Ph.D. Thesis, Kaiserslautern (Germany) and Pisa (Italy), 2007.
 
-\bibitem{Krueger} {\sc T. Kr\"uger, F. Varnik, D. Raabe}, {\em Shear stress in lattice Boltzmann simulations}, Phys. Rev. E 79 (4) (2009) 046704
+\bibitem{Krueger} {\sc T. KR\"UGER, F. VARNIK, D. RAABE}, Shear stress in lattice Boltzmann simulations, Phys. Rev. E 79 (4) (2009) 046704.
 
-\bibitem{Lallemand} {\sc P. Lallemand, L.-S. Luo}, {\em Lattice Boltzmann method for moving boundaries}, J. Comput. Phys. 184 (2003) 406-421
+\bibitem{Lallemand} {\sc P. LALLEMAND, L.-S. LUO}, Lattice Boltzmann method for moving boundaries, J. Comput. Phys. 184 (2003) 406-421.
 

### 2015-11-13 ian_mitchell-toolbox/Kernel/Helper/Visualization/visualizeLevelSet.m
More cleaning on the code

@@ -116,7 +116,8 @@ function h = visualizeLevelSet(g, data, display_type, level, title_string)
     switch(display_type)
      case 'contour'
       [ ~, h ] = contour(g.xs{1}, g.xs{2}, data, level, 'b');
-      axis square;  axis manual;
+     % axis square;  
+      axis manual;
      case 'surf'
       h = surf(g.xs{1}, g.xs{2}, data);
      otherwise

### 2015-11-13 ian_mitchell-toolbox/lbm/main.m

@@ -1,42 +1,48 @@
 clear;
-% Remark: Origin (1,1) is bottom left!
-%
-%   ^
-% y |__>
-%     x
+% D2Q9 Lattice-Boltzmann/Level-Set Code for Multiphase flow 
+% According to doi:10.1016/j.camwa.2009.02.005
+% Uses:
+% -Toolbox of Level Set Methods, Copyright © 2007 by Ian M. Mitchell.
+% http://www.cs.ubc.ca/~mitchell/ToolboxLS
+% -Polygon intersection function, by Douglas M. Schwarz, BSD
+% http://www.mathworks.com/matlabcentral/fileexchange/11837-fast-and-robust-curve-intersections
 
-t_end = 10; % [s]
+%Physical setup
+t_end = 20; % [s]
 x_len = 1; % [m]
-y_len = 1; % [m] %Ignoriert von Level-Set Bibilothek!
-rho_phys(1) = 1000; % [kg/m^3] % Mass-density of Fluid 1, e.g. ~1000 for Water, 1,2 for Air. In Lattice-Boltzmann-Units Cell-density is varying around 1!
-rho_phys(2) = 1; % [kg/m^3] %
-lidVel = 0; % [m/s]
-visc(1) = 16;% [m^2/s] kinematic viscosity of fluid 1
-visc(2) = 16;% [m^2/s] kinematic viscosity of fluid 2
-sigma = 1.6e-8;  % [kg/s^2] surface tension the two phases, e.g. ~ 76*10^-3 between water and air
-lbm_it = 10; % Number of LBM-iterations until level-set update
+y_len = 2; % [m] 
+rho_phys(1) = 1.0; % [kg/m^3] % Mass-density of Fluid 1, 
+rho_phys(2) = 1; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
+visc(1) = 1;% [m^2/s] kinematic viscosity of fluid 1
+visc(2) = 7;% [m^2/s] kinematic viscosity of fluid 2
+sigma = 1.6e-6;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air
 
-% Diese Zahl sollte mMn folgendermaßen beschränkt sein:
-% Delta_T = lbm_it * lbm_g.dt ist das Zeitinterval, in dem sich Level-Set und LBM abwechseln.
[…]

### 2015-11-14 Paper/paper.tex
More cleaning on the code
Paper

@@
-%%
-%% This is file `docultexmm.tex', 
-%% Documentation for siam multimedia macros for use with LaTeX 2e
-%% 
-%% December 19, 2013
-%%
-%% Version 1.0.1
-%% 
-%% You are not allowed to change this file. 
-%% 
-%% You are allowed to distribute this file under the condition that 
-%% it is distributed together with all of the files in the siam macro 
-%% distribution. These are:
-%%
-%%  siamltexmm.cls (this file)
-%%  siam11.clo   (required size option for 11pt papers)
-%%  subeqn.clo   (allows equation numbers with lettered subelements)
-%%  siam.bst     (bibliographic style file for BibTeX)
-%%  docultexmm.tex (documentation file)
-%%
-%% If you receive only some of these files from someone, please contact: 
-%% multimedia@siam.org  
-%% 
-%% You are not allowed to distribute this file alone. You are not 
-%% allowed to take money for the distribution or use of either this 
-%% file or a changed version, except for a nominal charge for copying 
-%% etc.
-%%
-%% \CharacterTable
-%%  {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
-%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
-%%   Digits        \0\1\2\3\4\5\6\7\8\9
-%%   Exclamation   \!     Double quote  \"     Hash (number) \#
-%%   Dollar        \$     Percent       \%     Ampersand     \&
-%%   Acute accent  \'     Left paren    \(     Right paren   \)
-%%   Asterisk      \*     Plus          \+     Comma         \,
-%%   Minus         \-     Point         \.     Solidus       \/
-%%   Colon         \:     Semicolon     \;     Less than     \<
-%%   Equals        \=     Greater than  \>     Question mark \?
-%%   Commercial at \@     Left bracket  \[     Backslash     \\
-%%   Right bracket \]     Circumflex    \^     Underscore    \_
-%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
-%%   Right brace   \}     Tilde         \~}
-
 \documentclass[final,leqno,onefignum,onetabnum]{siamltexmm}
@@
 \usepackage{amsmath}
+\usepackage{cleveref}
 
-\title{Implementation of a lattice Boltzmann method for immiscible multiphase flow simulations using the level set method}
+\title{Implementation of a lattice Boltzmann method for immiscible two-phase flow simulations using the level set method}
 
@@
 Cauerstr. 11, 91058 Erlangen, Germany\\
-lorenz.hufnagel@fau.de\\
-daniel.zint@fau.de % ist das so richtig?
+lorenz.hufnagel@fau.de, daniel.zint@fau.de % ist das so richtig?
 }
@@
 \cite{Thoemmes}.
-The level set method is used to calculate the movement of the interface between the two phases.
+The level set method is used to compute the movement of the interface between the two phases.
 The input for the level set method is computed by the lattice Boltzmann method.
@@
 %Something about the two-phase problem and some other algorithms that solve it. We could do this according to the presentation-slides.
-In engineering the immiscible two-phase flow problem often needs to be considered.
+In engineering the immiscible multiphase flow problem often needs to be considered.
 For example, bubble dynamics are decisive for the design of chemical reactors.
-Also fingering in oil recovery is a common two-phase problem.
+Also, fingering in oil recovery is a common multiphase problem.
 
-The two-phase flow problem can be described with the Navier-Stokes equations for two incompressible fluids (Eq. \ref{nse1}, \ref{nse2}). 
+In the following we will restrict ourselves to two fluid phases, but the procedure is also applicable for multiple phases. 
+There are different approaches to solve the immiscible two-phase problem.
+The most spread among these is the colour gradient method of Gunstensen and Rothman \cite{GRcg1,GRcg2,GRcg3}.
+The downside of this method is that it is only applicable for small density and viscosity differences.
+Another approach is the concept of {\it interaction potentials} by Shan and Chen \cite{ShanChen1,ShanChen2}.
+This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
+Furthermore, there are free surface methods which only take one fluid in account for computation \cite{Koerner}.
+They work best for large density and viscosity ratios.
+%TODO: Mehr Referenzen, siehe Mail
+
+In this publication we use a hybrid lattice Boltzmann level set method.
+The motion of the interface is modelled by the level set method.
+The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
+This method has the advantage that it allows for large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp inteface.
+
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (Eq. \ref{nse1}, \ref{nse2}). 
 %TODO Regina: Hier fehlen Referenzen!
-To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface (Fig.
-\ref{intro_phases}).
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface inbetween (\cref{intro_phases}).
 The material properties in each fluid are constant and the interface is assumed to be sharp.
-Thus the material properties are discontinuous and the fluids will not mix.
+Thus, the overall material properties are discontinuous and the fluids will not mix.
 
@@
 
-The evolution of the flow fields within each fluid can be expressed with the incompressible Navier-Stokes equations,
-\begin{gather}
-	\nabla \cdot  \vec u_i = 0 \text{  in } \Omega_i \text{,}
+The change of momentum within each fluid can be expressed as
+\begin{align}
+  \nabla \cdot  \vec u_i &= 0 \text{  in } \Omega_i \text{,}
 	\label{nse1} \\
 	\frac{\partial \vec u_i}{\partial t} + \left(\vec  u_i\cdot \nabla \right) \vec u_i
-	=
+  &=
 	-\frac{1}{\varrho_i}\nabla p_i + \nu_i \nabla^2 \vec u_i \text{  in } \Omega_i \text{.}
 	\label{nse2}
-\end{gather}
-Here, $u_i$ is the velocity, $p_i$ the pressure, $\nu_i$ the kinematic viscosity and $\varrho_i$ the mass density.
+\end{align}
+Here, $\vec u_i$ is the velocity, $p_i$ the pressure, $\nu_i$ the kinematic viscosity and $\varrho_i$ the mass density.
 
-As boundary conditions and initial conditions we can take for example,
-\begin{gather}
-	\vec u_i(x,t) = 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,} \\
-	\vec u_i(x,0) = \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
-\end{gather}
-For the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions,
-\begin{gather}
-	[\vec u] = 0 \text{,  } \\
-	[T] \cdot \vec n = 2 \sigma \kappa \vec n \text{.}
+As boundary conditions and initial conditions we use,
+\begin{align}
+  \vec u_i(x,t) &= 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,} \\
+  \vec u_i(x,0) &= \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
+\end{align}
+At the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions,
+\begin{align}
+  [\vec u] &= 0 \text{,  } \\
+  [2\mu S - p \mathbf{I}] \cdot \vec n &= 2 \sigma \kappa \vec n \text{.}
 	\label{jumpconditions}
-\end{gather}
-Here, T is the shear stress tensor, $\sigma$ the surface tension, and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
+\end{align}
+Here, S is the shear rate tensor $S=\frac12 \left( \nabla \vec u + \nabla {\vec u}^T\right)$, $\sigma$ the surface tension, $\mu = \varrho \nu$ the dynamic viscosity and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
 Brackets denote the jump of a quantity at the interface,
@@
 \end{equation}
-In Fig. \ref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
+In \cref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
 
-There are different approaches to solve the immiscible two-phase problem.
-The most spread among these approaches is the colour gradient method of Gunstensen and Rothman \cite{GRcg1,GRcg2,GRcg3}.
-The downside of this method is that it is only applicable for small density and viscosity differences.
-Another approach is the concept of {\it interaction potentials} by Shan and Chen \cite{ShanChen1,ShanChen2}.
-This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
-Furthermore there are free surface methods which only take one fluid in account for computation (\cite{Koerner}).
-They work best for big density and viscosity ratios.
-%TODO: Mehr Referenzen, siehe Mail
-
-In this publication we use a hybrid lattice Boltzmann level set method.
-Thereby the interface motion is calculated by the level set method.
-The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
-This method has the advantage that it allows for big ranges of density and viscosity ratios between the fluid phases
-and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
-.
-
-This paper is organized as follows: Section 2 gives an introduction to the lattice Boltzmann method and the level set method and explains the coupling of these.
+This paper is organized as follows: Section 2 gives an introduction to the LBM and the level set method and explains the coupling of these.
 In section 3 we present our results and finally in section 4 we draw a conclusion.
@@
 \section{Numerical Methods}
-The algorithm we describe in this paper uses the lattice Boltzmann method and the level set method.
-With the lattice Boltzmann method we calculate the velocity field for each fluid independently.
-The level set method uses this velocity field to compute the movement of the interface.
+The algorithm we describe in this paper uses the LBM and the level set method.
+The lattice Boltzmann method covers the description of the velocity and density field for each fluid, as it can be shown to reproduce the Navier-Stokes-equations in the asymptotic limit with Chapman-Enskog expansion \cite{LBM3}.
+The level set method uses a velocity field to model the movement of the interface.
 We will shortly introduce both methods and show how they can be coupled.
@@
 To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method (LBM).
-This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ in phase space, with $(\vec{x},\vec{v})$ as the phase space variables and $t$ as time.
-The LBM algorithm discretizes with a regular grid in space and with restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
-We use the D2Q9 model in 2D, which has 9 velocity vectors on a plane grid with unit spacing including one zero velocity (Fig.
-\ref{lbmc_i}).
-%TODO Regina: Man kann auch Cref benutzen zum Zitieren
+This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ of the Boltzmann equation in phase space, with $(\vec{x},\vec{v})$ as the phase space variables over time.
+For the LBM algorithm the geometrical domain is discretized with a cartesian grid and the velocity space with a restricted number of velocities adapted to this grid \cite{LBM1,LBM2,LBM3,LBM4}.
+We use the D2Q9 model in 2D, which has 9 velocity vectors on a plane grid with unit spacing including one zero velocity (\cref{lbmc_i}).
 \begin{figure}
@@
 	\text{.}
+  \label{disc_vel}
 \end{equation}
-The corresponding particle distributions are denoted by $f_i(\vec{x},t) = f(\vec{x},\vec{c_i},t)$. We get the density and velocity from the particle distribution functions with,
+The corresponding particle distributions are denoted by $f_i(\vec{x},t) = f(\vec{x},\vec{c_i},t)$. We get the density and velocity from the moments of the particle distribution functions with,
 \begin{equation}
@@
 
-In the interior, the LBM alternates collision step and propagation step. For the collision step we use the Bhatnagar-Gross-Krook (BGK) approximation \cite{BGK},
+The LBM algorithm alternates between a collision step and propagation step, where for the collision step we use the Bhatnagar-Gross-Krook (BGK) collision operator \cite{BGK},
 \begin{equation}
@@
 \end{equation}
-The propagation step is denoted by,
-\begin{equation}
-	f_i(\vec{x}+\vec{c_i},t+1) = f_i^+(\vec{x},t+1).
-\end{equation}
-The parameter $\tau$ is the relaxation parameter for the BGK collision operator and controls the kinematic viscosity in lattice units $\nu = \frac16(2\tau - 1)$.
+The parameter $\tau$ is the relaxation parameter for the collision and controls the kinematic viscosity in lattice units $\nu = \frac16(2\tau - 1)$.
 Note, that we assume the cell spacing $\Delta x$ and the time step $\Delta t$ to be unity here.
@@
 \begin{equation}
-	f_i^{eq}(\rho,\vec{u}) = f_i^*(\rho + 3\vec{c_i} \cdot \vec{u} + \frac92(\vec{c_i} \cdot \vec{u})^2 - \frac32 \vec u\cdot \vec u)
+	f_i^{eq}(\rho,\vec{u}) = f_i^*(\rho + 3\vec c_i \cdot \vec{u} + \frac92(\vec c_i  \cdot \vec{u})^2 - \frac32 \vec u\cdot \vec u)
+  \label{equil}
 \end{equation}
@@
 $$
-
+The propagation step is denoted by,
+\begin{equation}
+	f_i(\vec{x}+\vec c_i,t+1) = f_i^+(\vec{x},t+1),
+\end{equation}
 %Boundary Conditions: Bounce-back & moving no-slip & inflow-outflow
-We use two types of boundary conditions. To simulate static walls, we use simple bounce-back boundary conditions,
+where two types of boundary conditions are used. To simulate static walls we use bounce-back boundary conditions,
 \begin{equation}
@@
 \end{equation}
-where $i^*$ is the index of the opposite direction $c_{i^*} = -c_i$. To simulate a flow, we use moving no-slip boundary conditions,
+where $i^*$ is the index of the opposite direction $\vec c_{i^*} = -\vec c_i$. To simulate a solid boundary with nonzero tangential velocity, we use moving no-slip boundary conditions,
 \begin{equation}
-	\tilde{f_i} = f_{i^*}^+(\vec{x_b},t) + 6 f_i^*\vec{c_i} \vec{v} \text{, with } \vec{x_b} \in \delta\Omega,
+	\tilde{f_i} = f_{i^*}^+(\vec x_b,t) + 6 f_i^*\vec c_i \vec{v} \text{, with } \vec x_b  \in \delta\Omega,
 \end{equation}
-where $\vec{v}$ is the speed of the moving wall. To enable inflow and outflow of fluids we have periodic boundary conditions,
+where $\vec{v}$ is the speed of the moving wall. To model infinitely long domains we use periodic boundary conditions,
 \begin{equation}
-	\tilde{f_i}(\vec{x_a},t) = f_i^+(\vec{x_b},t) \text{,}
+	\tilde{f_i}(\vec x_a ,t) = f_i^+(\vec x_b ,t) \text{,}
 \end{equation}
@@
 	\item[1. ] Collision step: $f_i^+ = f_i - \frac1\tau(f_i - f_i ^{eq}) + G_i$
-	\item[2. ] Propagation step: $f_i(\vec{x}+\vec{c_i},t+1) = f_i^+(x,t)$, for interior nodes
-	\item[3. ] Boundary conditions: $f_i(\vec{x}+\vec{c_i},t+1) = f_i(\vec{x}+\vec{c_i},t)$, if $\vec{x} \notin \Omega$
+	\item[2. ] Propagation step: $f_i(\vec{x}+\vec c_i ,t+1) = f_i^+(x,t)$, for $\vec{x} \in \Omega$
+	\item[3. ] Boundary treatment: $f_i(\vec{x}+\vec c_i ,t+1) = f_i(\vec{x}+\vec c_i ,t)$, if $\vec{x} \notin \Omega$
 \end{itemize}
 
+We remark, that the propagation step is the only non-local operation in the LBM algorithm, as it access nearest neighbors. This allows for highly efficient parallel implementations of the LBM.
 \subsection{The Level Set Method}
-We deal with the movement of the interface between the two fluids by using the level set method.
+We deal with the advection of the interface between the two fluids by using the level set method.
 The method captures the surface that represents the interface with a continuous signed distance function, where the interface is implicitly given as the zero level set.
@@
 Thus, for $\vec x \in \Gamma_t$ we have $\varphi(\vec x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
-For this level set function we get the level set equation introduced by Osher and Sethian in \cite{OsherSethian} for the evolution of free surfaces,
+For this level set function we get the level set equation introduced by Osher and Sethian in \cite{OsherSethian} for the evolution of surfaces,
 \begin{equation}
@@
 This toolbox takes as input the velocity field we get from the lattice Boltzmann method and computes the movement of the interface.
-The toolbox also provides functions to calculate the normal and the curvature of the surface.
+The toolbox also provides functions to compute the normal and the curvature of the surface.
 We will need this information for the coupling of the methods.
@@
 \subsection{Coupling of LBM and level set method}
-The lattice Boltzmann method requires a boundary treatment at the interface which implements the jump conditions (\ref{jumpconditions}).
-For sake of simplicity, we do not write arrows for every vector, i.e., $\vec{u} \rightarrow u$.
+The lattice Boltzmann method requires a boundary treatment at the interface which implements the macroscopic jump conditions (\ref{jumpconditions}).
+For the sake of simplicity, we do not write arrows for every vector, i.e., $\vec{u} \rightarrow u$.
 One should consider that every position, direction, and velocity is two-dimensional.
@@
 1146]{Thoemmes}.
-For example, in Fig.
-\ref{coupling} for a point $x_2 \in \Omega_2$ that is next to the phase interface we set,
+Consider a point $x_2 \in \Omega_2$ that is next to the phase interface, where the link $c_i$ crosses the interface, see \cref{coupling}.
+We set,
 \begin{figure}
@@
 $$
-The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error terms that is introduced by the first order accurate bounce back treatment,
+The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error that is introduced by the first order accurate bounce back treatment,
 \begin{equation}
-	R_i = 6 f_i^* \Lambda_i : A \text{ with } A = -q(1-q)[S] - (q - \frac12)S^{(2)} \text{, }
-  \label{add_term2}
+  R_i = 6f_i^* \left(q(q-1)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S(x_2) \right) \text{,}
+  \label{R_i}
 \end{equation}
@@
 \end{equation}
-That is an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction weighted with the interface distance and a compensation term for the interpolation error.
-This error arises, when the interface is not on the exact middle between two LBM grid cells.
+That is an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction.
+This projection is weighted with the interface distance and a compensation term for the interpolation error.
+This error arises, when the interface is not on the exact center between two LBM grid cells.
 The tensor product is $a \otimes b = ab^T$ and the double contraction $A:B = \mathrm{trace}(AB^T)$.
-We can rewrite formula (\ref{add_term2}) in the form,
-\begin{equation}
-  R_i = 6f_i^* (-q)(1-q)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S_2 \text{,}
-\end{equation}
-and use the following first-order estimate to obtain the shear rate from the non-equilibrium parts of the distributions (see \cite{Krueger})
+Furthermore, we use the following first-order estimate to obtain the shear rate from the non-equilibrium parts of the distributions, see also \cite{Krueger},
 \begin{equation}
@@
 \end{equation}
-Furthermore, we have,
+Now we have,
 \begin{equation}
@@
 \end{equation}
-which is obtained by a coordinate transformation onto a basis $(n, t)$ of normal and tangential vector to the interface.
-From the fluid mechanical jump condition (\ref{jumpconditions}) and the relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen,
-\begin{gather}
-	[S]:n \otimes n =  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,} \\
-	[S]:n \otimes t = - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t \text{.}
-\end{gather}
-Here $\mu_k = \varrho_k \nu_k$ are the dynamic viscosities, with $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ as averaged quantities, $\kappa$ the interface curvature, and the viscosity jump  $[\mu] = \mu_2 - \mu_1$.
-The pressure jump is approximated by,
+which is obtained by a coordinate transformation of (\ref{R_i}) onto a basis $(n, t)$ of normal and tangential vector to the interface.
+From the fluid mechanical jump condition (\ref{jumpconditions}) and the general relation $[\mu S] = \bar{\mu}[S] + [\mu]\bar{S} $ it can be seen,
+\begin{align}
+  [S]:n \otimes n &=  \frac{1}{2 \bar\mu} ([p] + 2 \sigma \kappa) - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes n \text{,} \\
+  [S]:n \otimes t &= - \frac{[\mu]}{\bar{\mu}} \bar{S} : n \otimes t \text{.}
+\end{align}
+Here $\bar{\mu} = (\mu_1 + \mu_2)/2$ and $\bar{S} = (S_1 + S_2)/2$ are averaged quantities, $\kappa$ the interface curvature, and  $[\mu] = \mu_2 - \mu_1$ the viscosity jump.
+
+With respect to the given definition of the discrete lattice velocities (\ref{disc_vel}), the pressure jump is approximated by,
 \begin{equation}
@@
 \end{equation}
-%TODO: Kommentar, dass hier ein Fehler im Thömmes-paper ist
-and with that, all variables for the boundary conditions are well defined.
+and thus, all variables for the boundary conditions are defined.
+
 A refill method is still missing.
 Due to the fact that the interface moves, some cells change their fluid type.
-We use an equilibrium/non-equilibrium refill as it is described in \cite{Caiazzo} consisting out of the four following steps:
+We use an equilibrium/non-equilibrium refill as it is described in \cite{Caiazzo} consisting of the following four steps:
 \begin{itemize}
-	\item[1] Interpolate density and velocity from interior neighbors.
+	\item[1] Extrapolate density and velocity from interior neighbors.
 	\item[2] Compute the corresponding equilibrium.
 	\item[3] Copy the non-equilibrium part from a direct interior neighbor.
-	\item[4] Reinitialise by adding equilibrium and non-equilibrium parts.
+	\item[4] Reinitialize by adding equilibrium and non-equilibrium parts.
 \end{itemize}
-Suppose we choose an inward pointing direction $c_i$ in a boundary point $x \in \Omega_1$, e.g., the direction of biggest angle with the surface normal. Then the density is interpolated by,
+Suppose we choose an inward pointing direction $c_i$ in a boundary point $x \in \Omega_1$, e.g. the direction with the largest angle to the surface normal. Then the density is extrapolated by,
 \begin{equation}
-  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1).
+  \tilde{\rho}(x) = 3\rho(x+c_i,t) - 3\rho(x+2c_i,t) + \rho(x+3c_i,t).
 \end{equation}
@@
 \end{figure}
-Figure \ref{refill} shows the cells we use for the interpolation.
-In \cite{Thoemmes} the velocity is interpolated by using the velocity of the interface.
-The Ian-Mitchell toolbox does not provide a function to access this value.
-%TODO das ist misverständlich.
-Therefore, we use the formula given in \cite{Lallemand} that is basically the same we use for density,
+Figure \ref{refill} shows the cells we use for the extrapolation.
+In \cite{Thoemmes} the velocity is extrapolated using the extension velocity of the interface \cite{Adalsteinsson}.
+In contrast, we use the formula given in \cite{Lallemand}, analogous to the formula for the density,
 \begin{equation}
-  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1).
+  \tilde{u}(x) = 3u(x+c_i,t) - 3u(x+2c_i,t) + u(x+3c_i,t),
 \end{equation}
-We can now calculate the new equilibrium part of the particle densities in $x$, $f_i^{eq}(\tilde{\rho},\tilde{u})$ and add them to the non-equilibrium part which we copy from a nearest neighbor,
+which yields similar results, as reported in \cite{Lallemand}.
+We can now compute the equilibrium part $f_i^{eq}(\tilde{\rho},\tilde{u})$ according to (\ref{equil}) and add it to the non-equilibrium part which we copy from a nearest neighbor,
 $$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
@@
 \end{figure}
-Finally, we can couple the two methods in the following way:
+Finally, the complete coupling the lattice Boltzmann and the level set method reads (see also \cref{dataexchange}):
 \begin{itemize}
@@
 	\item[2.] Run the level set code once to create the surface description for LBM.
-	\item[3.] Run the LBM using the data from the level set for a prescribed number of steps
-	\item[4.] Pass the current velocity field to the level set code and run it for the same number of steps (see Fig. \ref{dataexchange}).
+	\item[3.] Run the LBM  for a prescribed time interval, using normal, curvature and interface position from the level set
+	\item[4.] Pass the velocity field to the level set code and run it for the same time interval
 	\item[5.] Repeat step 3 and 4 until the end of the simulation.
@@
 \section{Results and Examples}
-To verify the correctness of our implementation we firstly built a Couette flow and compared our results with the one we get from the analytic solution.
+To verify the correctness of our implementation we first built a Couette flow with two stacked fluid layers.
 Secondly, we used the Young-Laplace experiment for a bubble to validate the implementation of surface tension.
@@
 \subsection{Couette channel flow}
-The Couette channel flow consists of a fixed lower wall at $y=0$ and an upper wall at $y=1$ that is moving with a constant velocity.
-At these walls we use no-slip boundary conditions.
-To generate a channel flow, we use periodic boundary conditions for the boundaries at the inflow $x=0$ and the outflow $x=1$.
-The two fluids are distributed in a way that the interface is parallel to our walls.
-%TODO Regina: kleines Bild, was die RB angibt und vielleicht auch die Werte?
-%TODO: give information about the parameter
-%TODO: show graph with results
+The Couette channel flow consists of a lower wall $y=0$ at rest and an upper wall $y=1$ that is moving tangentially with a prescribed constant velocity.
+At these walls no-slip boundary conditions hold.
+Along the $x$-direction periodic boundary conditions are prescribed.
+The two fluids layers are oriented such that their interface is parallel to the no-slip walls, and no external pressure gradient is applied.
+For this flow scenario an analytic solution can be derived from the Navier-Stokes equations, namely they simplify to $\frac{\partial }{\partial y}\left( \eta\frac{\partial u}{\partial y}\right) =0$.
+In combination with the no-slip conditions at top and bottom and wall this means, that the horizontal velocity has a linear profile with a kink at the fluid interface.
+The respective slopes between both phases are related by $\frac{\partial_y u^{(1)}}{\partial_y u^{(2)}} = \frac{\eta^{(2)}}{\eta^{(1)}}$.
 
-For the Couette channel flow exists an analytic solution that can be derived from the Navier-Stokes equations
-$$
-v(x) = \begin{cases} v_0 (\frac{\mu_1}{\mu_1+\mu_2}x + \frac{\mu_2}{\mu_1+\mu_2}) \text{,} & x \ge 0 \\ v_0 (\frac{\mu_2}{\mu_1+\mu_2}x + \frac{\mu_2}{\mu_1+\mu_2}) \text{,} & x < 0 \text{,}\end{cases}
-$$
-where $\mu_1$ denotes the dynamic viscosity in the lower fluid and $\mu_2$ the viscosity in upper fluid.
+We used identic densities $\varrho_1 = \varrho_2 = 1$ and $5 \times 20$ cells along $x \times y$ direction, as well as a LBM timestep of $\Delta t=0.0025$.
+In \cref{couette1} we show the simulated values and the analytic solution for viscosities $\mu^{(1)} = 1/2$ and $\mu^{(2)} = 10$, where interface was located at $y=0.42$.
+One can see that the values agree very well and in fact an overall relative error below $0.01\%$ was attained after 1000 LBM iterations.
+\begin{figure}[h!]
+	\flushright
+	\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.7\textwidth, natwidth=595,natheight=842]{couette1.pdf}
+	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+	\label{couette1}
+\end{figure}
 
+Figure \ref{couette2} shows a second scenario with $5 \times 10$ cells along $x \times y$ direction and viscosities $\mu^{(1)} = 1$ and $\mu^{(2)} = 0.2$ with the interface located at $y=0.75$.
+Again the numerically approximated values agree very well with the analytic ones and the simulation converged at a relative error of $1.4\cdot10^{-4}$ after 2000 LBM iterations.
+\begin{figure}[h!]
+	\flushright
+	\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.7\textwidth, natwidth=595,natheight=842]{couette2.pdf}
+	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+	\label{couette2}
+\end{figure}
+We conclude from this that the implemented LBM boundary conditions successfully model viscosity jumps at the fluid interface.
 \subsection{Young-Laplace experiment for a bubble}
@@
 \section{Conclusion}
+%% Danksagung?
 
@@
 
-\bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, A fast level set method for propagating interfaces, J. Comput. Phys. 118 (2) (1995) 269-277.
+\bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.
 

### 2015-11-14 Paper/paper.tex
Reference

@@
 
-With respect to the given definition of the discrete lattice velocities (\ref{disc_vel}), the pressure jump is approximated by,
+With respect to the given definition of the discrete lattice velocities (\ref{disc_vel}, see also \cite{Thoemmes2}), the pressure jump is approximated by,
 \begin{equation}
@@
 
-\bibitem{Thoemmes} {\sc G. TH\"OMMES, J. BECKER}, A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method, J. Comput. Phys. 228 (2009), 1139-1156.
+\bibitem{Thoemmes} {\sc G.
+TH\"OMMES, J.
+BECKER, M.
+JuNK, A.K.
+VAIKUNTAM, D.
+KEHRWALD, A.
+KLAR, K.
+STEINER, A.
+WIEGMANN}, A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method, J.
+Comput.
+Phys.
+228 (2009), 1139-1156.
 
+\bibitem{Thoemmes2} {\sc J.
+BECKER, M.
+JUNK, D.
+KEHRWALD, G.
+TH\"OMMES, Z.
+YANG}, A combined lattice BGK/level set method for immiscible two-phase flows, Computers and Mathematics with Applications, 58(5):950–964, 2009.
 \bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.

### 2015-11-14 Paper/paper.tex
Paper in PDF Version

--- 2015-11-13 Paper/paper.tex
@@
 In this publication we use a hybrid lattice Boltzmann level set method.
-Thereby the interface motion is calculated by the level set method.
+Thereby, the interface motion is calculated by the level set method.
 The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
-This method has the advantage that it allows for big ranges of density and viscosity ratios between the fluid phases
+This method has the advantage that it allows big ranges of density and viscosity ratios between the fluid phases
 and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
@@
 \begin{equation}
-  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1).
+  \tilde{\rho}(x) = 3\rho(x+c_i,t) - 3\rho(x+2c_i,t) + \rho(x+3c_i,t).
 \end{equation}
@@
 \begin{equation}
-  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1).
+  \tilde{u}(x) = 3u(x+c_i,t) - 3u(x+2c_i,t) + u(x+3c_i,t).
 \end{equation}

### 2015-11-14 Paper/paper.tex

--- 2015-11-14 Paper/paper.tex
@@
 \end{equation}
+In Fig. \ref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
+
+There are different approaches to solve the immiscible two-phase problem.
+The most spread among these approaches is the colour gradient method of Gunstensen and Rothman \cite{GRcg1,GRcg2,GRcg3}.
+The downside of this method is that it is only applicable for small density and viscosity differences.
+Another approach is the concept of {\it interaction potentials} by Shan and Chen \cite{ShanChen1,ShanChen2}.
+This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
+Furthermore there are free surface methods which only take one fluid in account for computation (\cite{Koerner}).
+They work best for big density and viscosity ratios.
+%TODO: Mehr Referenzen, siehe Mail
+
+In this publication we use a hybrid lattice Boltzmann level set method.
+Thereby, the interface motion is calculated by the level set method.
+The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
+This method has the advantage that it allows big ranges of density and viscosity ratios between the fluid phases
+and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
+.
 In \cref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.

### 2015-11-14 Paper/paper.tex
Figures rearanged

@@
 \subsection{Couette channel flow}
+\begin{figure}[b!]
+	\flushright
+	\hfill\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.8\textwidth, natwidth=595,natheight=842]{couette1.pdf}\hspace*{\fill}
+	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+	\label{couette1}
+\end{figure}
 The Couette channel flow consists of a lower wall $y=0$ at rest and an upper wall $y=1$ that is moving tangentially with a prescribed constant velocity.
@@
 One can see that the values agree very well and in fact an overall relative error below $0.01\%$ was attained after 1000 LBM iterations.
-\begin{figure}[h!]
-	\flushright
-	\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.7\textwidth, natwidth=595,natheight=842]{couette1.pdf}
-	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
-	\label{couette1}
-\end{figure}
 
@@
 	\flushright
-	\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.7\textwidth, natwidth=595,natheight=842]{couette2.pdf}
+	\hfill\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.8\textwidth, natwidth=595,natheight=842]{couette2.pdf}\hspace*{\fill}
 	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
@@
 We use the Young-Laplace experiment to validate the implementation of surface tension.
-The pressure $p$ inside a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the Young-Laplace law
+The pressure $p$ inside a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the Young-Laplace law,
 \begin{equation}

### 2015-11-14 Paper/paper.tex
Conclusion first try, but not good i think..

@@
 
-The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (Eq. \ref{nse1}, \ref{nse2}). 
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}). 
 %TODO Regina: Hier fehlen Referenzen!
@@
 	\flushright
-	\includegraphics[width=11cm,natwidth=1690,natheight=1174]{skizze.png}
+	\hfill\includegraphics[width=9cm,natwidth=1690,natheight=1174]{skizze.png}\hspace*{\fill}
 	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
@@
 \begin{figure}
-	\hfill\includegraphics[width=6cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
+	\hfill\includegraphics[width=4cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
 	\caption{The vectors of one cell in LBM.}
@@
 \begin{figure}
-	\hfill\includegraphics[width=10cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
+	\hfill\includegraphics[width=8cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
 	\caption{Link between two points in different fluids.}
@@
 \end{equation}
-and thus, all variables for the boundary conditions are defined.
+and thus, all variables for the boundary conditions are defined. % sagen wir hier noch, dass im Thömmes-paper ein Fehler war, der im zweiten Paper korrigiert wurde?
 
@@
 \begin{figure}
-	\hfill\includegraphics[width=8cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
+	\hfill\includegraphics[width=6cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
 	\caption{Cells that are used for the refill method.}
@@
 \begin{figure}
-	\hfill\includegraphics[width=8cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
+	\hfill\includegraphics[width=6cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
 	\caption{Data exchange between LBM and level set method.}
@@
 Again the numerically approximated values agree very well with the analytic ones and the simulation converged at a relative error of $1.4\cdot10^{-4}$ after 2000 LBM iterations.
-\begin{figure}[h!]
+\begin{figure}[t!]
 	\flushright
@@
 \section{Conclusion}
-%% Danksagung?
+%% Danksagung? - Ian Mitchell, Thömmes et al. ?
+%% Zusammenfassung/Wiederholung des Abstracts
+We implemented a hybrid lattice Boltzmann method that uses the level set method to model the movement of the interface.
+The implementation was done in Matlab for a two dimensional case.
+We adapted the formulas given in \cite{Thoemmes} to fit in our environment.
+Finally, we verified our implementation with different test cases.
+
+We want to thank Th\"ommes et al. for the awesome paper. % oder so ähnlich
+Furthermore, we want to thank Ian Mitchell for providing the toolbox for level set methods.
 
@@
 YANG}, A combined lattice BGK/level set method for immiscible two-phase flows, Computers and Mathematics with Applications, 58(5):950–964, 2009.
+
 \bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.

### 2015-11-14 Paper/paper.tex
Header on first page removed
kleine Korrekturen

@@
 \newcommand{\slugmaster}{%
-\slugger{siads}{xxxx}{xx}{x}{x--x}}%slugger should be set to juq, siads, sifin, or siims
+\slugger{}{}{}{}{}}%slugger should be set to juq, siads, sifin, or siims
 
@@
 
-\begin{AMS}\end{AMS}
+%\begin{AMS}\end{AMS}
 
@@
 The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
-This method has the advantage that it allows for large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp inteface.
+This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp inteface.
 
@@
 \end{align}
-Here, S is the shear rate tensor $S=\frac12 \left( \nabla \vec u + \nabla {\vec u}^T\right)$, $\sigma$ the surface tension, $\mu = \varrho \nu$ the dynamic viscosity and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
+Here, $S$ is the shear rate tensor $S=\frac12 \left( \nabla \vec u + \nabla {\vec u}^T\right)$, $\sigma$ the surface tension, $\mu = \varrho \nu$ the dynamic viscosity and $\kappa$ the curvature of the interface with respect to its outer normal $\vec n$.
 Brackets denote the jump of a quantity at the interface,
@@
 \end{equation}
-In Fig. \ref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
+In \cref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
 
@@
 .
-In \cref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
 
@@
 \subsection{The Lattice Boltzmann Method}
-To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method (LBM).
+To solve the incompressible Navier-Stokes equations, we use the lattice Boltzmann method.
 This method describes the evolution of the particle density $f(\vec{x},\vec{v},t)$ of the Boltzmann equation in phase space, with $(\vec{x},\vec{v})$ as the phase space variables over time.
@@
 
-We remark, that the propagation step is the only non-local operation in the LBM algorithm, as it access nearest neighbors. This allows for highly efficient parallel implementations of the LBM.
+We remark that the propagation step is the only non-local operation in the LBM algorithm, as it accesses nearest neighbors. This allows highly efficient parallel implementations of the LBM.
 \subsection{The Level Set Method}
@@
 \begin{equation}
-  S_k = -\frac{3}{2\tau } \sum_{i=1}^9 c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
+  S(x_k) = -\frac{3}{2\tau } \sum_{i=1}^9 c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
 \end{equation}
@@
 which yields similar results, as reported in \cite{Lallemand}.
-We can now compute the equilibrium part $f_i^{eq}(\tilde{\rho},\tilde{u})$ according to (\ref{equil}) and add it to the non-equilibrium part which we copy from a nearest neighbor,
+We can now compute the equilibrium part $f_i^{eq}(\tilde{\rho},\tilde{u})$ according to \cref{equil} and add it to the non-equilibrium part which we copy from a nearest neighbor,
 $$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
@@
 \end{figure}
-Finally, the complete coupling the lattice Boltzmann and the level set method reads (see also \cref{dataexchange}):
+Finally, the complete coupling of the lattice Boltzmann and the level set method reads (see also \cref{dataexchange}):
 \begin{itemize}
@@
 
-We want to thank Th\"ommes et al. for the awesome paper. % oder so ähnlich
-Furthermore, we want to thank Ian Mitchell for providing the toolbox for level set methods.
+We particularly want to thank Ian Mitchell for providing the toolbox for level set methods.
 

### 2015-11-14 Paper/paper.tex
Kleinigkeit

--- 2015-11-14 Paper/paper.tex
@@
 \begin{equation}
-  R_i = 6f_i^* \left(q(q-1)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S(x_2) \right) \text{,}
+  R_i = 6f_i^* \left(q(q-1)\Lambda_i:[S] - (q-\frac12)\Lambda_i:S_2 \right) \text{,}
   \label{R_i}
@@
 	\hfill\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.8\textwidth, natwidth=595,natheight=842]{couette1.pdf}\hspace*{\fill}
-	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+  \caption{Two horizontal fluid layers $\Omega_i$ separated by an interface. The top boundary is moving horizontally, while the lower one is at rest}
 	\label{couette1}
@@
 \subsection{Young-Laplace experiment for a bubble}
-The Couette-Flow is not influenced by surface tension due to the fact that the surface tension is multiplied with the curvature in Equation \ref{Lambda_iTimes_S} and the curvature is zero in the Couette-Flow.
-We use the Young-Laplace experiment to validate the implementation of surface tension.
-The pressure $p$ inside a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the Young-Laplace law,
+Our Couette flow scenario does not account for the influence of surface tension as the fluid interface is not curved.
+If it would get distorded, surface tension would have a stabilizing effect although.
+Hence, we use the Young-Laplace law for the pressure drop across curved surfaces, to validate the implementation of surface tension.
+The pressure inside of a convex surfaces is higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to thefollowing relationship,
 \begin{equation}
-	p = \frac{2\sigma}{r} = 2 \sigma \kappa .
+	\Delta p = \frac{2\sigma}{r} = 2 \sigma \kappa .
 \end{equation}

### 2015-11-14 Paper/paper.tex
Der eine Absatz war doppelt

@@
 	Level set method,
-	Free surface,
+	Two-phase,
 	Multiphase
@@
 In \cref{intro_phases} this is the jump from $\Omega_1$ to $\Omega_2$. For the other direction the sign changes.
-
-There are different approaches to solve the immiscible two-phase problem.
-The most spread among these approaches is the colour gradient method of Gunstensen and Rothman \cite{GRcg1,GRcg2,GRcg3}.
-The downside of this method is that it is only applicable for small density and viscosity differences.
-Another approach is the concept of {\it interaction potentials} by Shan and Chen \cite{ShanChen1,ShanChen2}.
-This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
-Furthermore there are free surface methods which only take one fluid in account for computation (\cite{Koerner}).
-They work best for big density and viscosity ratios.
-%TODO: Mehr Referenzen, siehe Mail
-
-In this publication we use a hybrid lattice Boltzmann level set method.
-Thereby, the interface motion is calculated by the level set method.
-The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid.
-This method has the advantage that it allows big ranges of density and viscosity ratios between the fluid phases
-and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
-.
 

### 2015-11-15 Paper/paper.tex
Referenz fuer NSE

@@
 The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
-This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp inteface.
+This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
 
-The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}). 
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}). 
 %TODO Regina: Hier fehlen Referenzen!
-To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface inbetween (\cref{intro_phases}).
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
 The material properties in each fluid are constant and the interface is assumed to be sharp.
@@
 Let $\Gamma_t$ be our interface at time t.
-Within the level set method, $\Gamma_t$ is the zero iso-surface of the level set function $\varphi$.
+Within the level set method, $\Gamma_t$ is the zero isosurface of the level set function $\varphi$.
 Thus, for $\vec x \in \Gamma_t$ we have $\varphi(\vec x,t) = 0$, in direction of the surface normal we get $\varphi > 0$, and in the other direction we get $\varphi < 0$.
@@
 \end{equation}
-and thus, all variables for the boundary conditions are defined. % sagen wir hier noch, dass im Thömmes-paper ein Fehler war, der im zweiten Paper korrigiert wurde?
+and thus, all variables for the boundary conditions are defined.
 
@@
 Our Couette flow scenario does not account for the influence of surface tension as the fluid interface is not curved.
-If it would get distorded, surface tension would have a stabilizing effect although.
+If it would get distorted, surface tension would have a stabilizing effect although.
 Hence, we use the Young-Laplace law for the pressure drop across curved surfaces, to validate the implementation of surface tension.
-The pressure inside of a convex surfaces is higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to thefollowing relationship,
+The pressure inside of a convex surfaces is higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the following relationship,
 \begin{equation}
@@
 
+\bibitem{ferziger} {\sc J. FERZIGER, M. PERIC.}, Computational methods for fluid dynamics. Springer Science \& Business Media, ISBN 978-3540420743 (2012).
+
 \bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.
@@
 
-\bibitem{LBM4} {\sc D.A. WOLF-GLADOW}, Lattice-Gas Cellular Automata and Lattice Boltzmann Models, An Introduction, Springer, 2000.
+\bibitem{LBM4} {\sc D.A. WOLF-GLADOW}, Lattice-Gas Cellular Automata and Lattice Boltzmann Models, An Introduction, Springer, (2000).
 

### 2015-11-15 Paper/paper.tex
Laplace testcase

@@
 Furthermore, there are free surface methods which only take one fluid in account for computation \cite{Koerner}.
-They work best for large density and viscosity ratios.
+They work best for large viscosity and density ratios.
 %TODO: Mehr Referenzen, siehe Mail
 
-In this publication we use a hybrid lattice Boltzmann level set method.
+Gn this publication we use a hybrid lattice Boltzmann level set method.
 The motion of the interface is modelled by the level set method.
 The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
-This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
+This method has the advantage that it allows for large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
 
@@
 	\rho(\vec{x},t) = \sum_{i=1}^{9} f_i(\vec{x},t) \text{, } \quad
-	\vec{u} = \sum_{i=1}^{9} f_i(\vec{x},t)\vec{c_i} \text{.}
+	\vec{u} = \sum_{i=1}^{9} f_i(\vec{x},t)\vec{c_i} \text{,}
 \end{equation} 
+while the pressure is related to the lattice density $\rho$ as $p=\varrho * \rho/3$.
 
@@
 
-We remark that the propagation step is the only non-local operation in the LBM algorithm, as it accesses nearest neighbors. This allows highly efficient parallel implementations of the LBM.
+We remark that the propagation step is the only non-local operation in the LBM algorithm, as it accesses nearest neighbors. This allows for highly efficient parallel implementations of the LBM.
 \subsection{The Level Set Method}
@@
 with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the LBM.
+It is easily visible, that the normal of the surface is determined as $\vec n(x) = \frac{\nabla \varphi(x)}{\|\varphi(x)\|}$ and accordingly the curvature as the divergence of the normal $\kappa = \nabla \cdot \nabla \varphi = \Delta \varphi$.
 
@@
 \begin{equation}
-  S(x_k) = -\frac{3}{2\tau } \sum_{i=1}^9 c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
+  S_k = -\frac{3}{2\tau } \sum_{i=1}^9 c_i \otimes c_i(f_i-f_i^{eq})(t,x_k) \text{.}
 \end{equation}
@@
 	\hfill\includegraphics[trim = 0mm 8cm 0mm 8cm, clip, width=.8\textwidth, natwidth=595,natheight=842]{couette2.pdf}\hspace*{\fill}
-	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+	\caption{Two fluid domains $\Omega_i$ in a Coutte flow}
 	\label{couette2}
@@
 We conclude from this that the implemented LBM boundary conditions successfully model viscosity jumps at the fluid interface.
+Furthermore, we were able to use viscosity ratios greater than $100:1$ in our tests.
 \subsection{Young-Laplace experiment for a bubble}
-Our Couette flow scenario does not account for the influence of surface tension as the fluid interface is not curved.
+The Couette flow scenario does not account for the influence of surface tension as the fluid interface is not curved.
 If it would get distorted, surface tension would have a stabilizing effect although.
 Hence, we use the Young-Laplace law for the pressure drop across curved surfaces, to validate the implementation of surface tension.
-The pressure inside of a convex surfaces is higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the following relationship,
+Due to surface tension the pressure inside of convex surfaces is generally higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the following relationship,
 \begin{equation}
@@
 
-%TODO: name the settings we used
-%TODO: add some nice pictures
+Figure \ref{laplace} shows the simulation results we obtained for a $40 \times 40$ cells grid over a $[0,1]\times[0,1]$-domain with periodic boundaries.
+At the center, a sphere of radius $0.25$ was placed with $\varrho_2 = 1.1$ while the exterior contained a fluid with $\varrho_1 = 1$.
+It is visible, how the approximated values attain the analytical solution in a oscillatory motion decaying amplitude, until both values agree.
+The algorithm needed 1000 LBM-iterations, where every ten iterations, a call to the level-set routine was executed.
+Both fluids had an identical viscosity of $\nu = 1/6$.
+\begin{figure}[t!]
+	\flushright
+	\hfill\includegraphics[trim = 0mm 7.75cm 0mm 8.06cm, clip, width=.8\textwidth, natwidth=595,natheight=842]{laplace.pdf}\hspace*{\fill}
+	\caption{The pressure drop of a spherical bubble over LBM iterations}
+	\label{laplace}
+\end{figure}
+We noted that the velocity close to the interface contained erroneous components, which lead to a slight distortion of the spherical shape.
+We explain those fluxes as inaccuracies stemming from the used level set subroutines, according to the analysis shown in \cite{Thoemmes2}.
+Additionally, we want to state, that we were not able attain stable results for surface tension coefficients $\sigma > \mathrm{O(10^{-3})}$.
+Large densitiy ratios were limited to big viscosity regimes, or refined spatial resolution in our tests.
 
@@
 Finally, we verified our implementation with different test cases.
+Possible applications for our algorithm are shown in figures TODO \& TODO, which show the transient movement of an oil drop in a lid driven cavity.
+%Fig TODO shows two rising and coalescing bubbles in a fluid, produced with our code.
 
 We particularly want to thank Ian Mitchell for providing the toolbox for level set methods.
+
+%TODO: add some nice pictures
 

### 2015-11-15 ian_mitchell-toolbox/lbm/main.m

@@ -16,11 +16,11 @@ clear;
 t_end = 50; % [s]
 x_len = 1; % [m]
 y_len = 1; % [m]
-rho_phys(1) = 1.05; % [kg/m^3] % Mass-density of Fluid 1,
+rho_phys(1) = 1.1; % [kg/m^3] % Mass-density of Fluid 1,
 rho_phys(2) = 1; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
 visc(1) = 1/6;% [m^2/s] kinematic viscosity of fluid 1
 visc(2) = 1/6;% [m^2/s] kinematic viscosity of fluid 2
-sigma = 1e-6;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air
+sigma = 1e-5;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air
 
 use_periodic_x = 1; % Use periodic boundaries on left/right domain border?
 % -> Otherwise No-Slip/Bounce-Back
@@ -569,10 +569,12 @@ while(t_end - tNow > 100 * eps * t_end)
     plot(pressure_vek+(rho_phys(1)-rho_phys(2))/3); %Offset by p_0
     hold on
     pressure_jump_analytic = 2*sigma/radius+(rho_phys(1)-rho_phys(2))/3;
-    plot(pressure_jump_analytic*ones(size(pressure_vek)),'g:');
+    plot(pressure_jump_analytic*ones(size(pressure_vek)),'k--');
     title(['\Delta P over \Delta T (:=' num2str(lbm_it) ' LBM-Iterations each)']);
     %axis([0, length(pressure_vek), 0,2*pressure_jump_analytic]);
     legend({'LBM','analytic'},'Location','SouthEast')
+    xlabel('10 LBM-Iterations');
+    ylabel('\Delta P');
     hold off
     
   end

### 2015-11-15 Paper/paper.tex
ein paar Kleinigkeiten

@@
 This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
-Furthermore, there are free surface methods which only take one fluid in account for computation \cite{Koerner}.
+Furthermore, there are free surface methods which only take one fluid in account for computation \cite{Koerner,Scardovelli,Hirt}.
 They work best for large viscosity and density ratios.
-%TODO: Mehr Referenzen, siehe Mail
 
-Gn this publication we use a hybrid lattice Boltzmann level set method.
-The motion of the interface is modelled by the level set method.
+In this publication we use a hybrid lattice Boltzmann level set method.
+The motion of the interface is modeled by the level set method.
 The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
@@
 The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}).
-%TODO Regina: Hier fehlen Referenzen!
 To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
@@
 We explain those fluxes as inaccuracies stemming from the used level set subroutines, according to the analysis shown in \cite{Thoemmes2}.
-Additionally, we want to state, that we were not able attain stable results for surface tension coefficients $\sigma > \mathrm{O(10^{-3})}$.
+Additionally, we want to state, that we were not able to attain stable results for surface tension coefficients $\sigma > \mathrm{O(10^{-3})}$.
 Large densitiy ratios were limited to big viscosity regimes, or refined spatial resolution in our tests.
@@
 \section{Conclusion}
-%% Danksagung? - Ian Mitchell, Thömmes et al. ?
-%% Zusammenfassung/Wiederholung des Abstracts
 We implemented a hybrid lattice Boltzmann method that uses the level set method to model the movement of the interface.
@@
 
+\bibitem{Scardovelli} {\sc R. SCARDOVELLI, S. ZALESKI}, Direct numerical simulation of free-surface and interfacial flow, Annu. Rev. Fluid Mech. 31 (1999) 567-603.
+
+\bibitem{Hirt} {\sc C.W. HIRT, J.P. SHANNON}, Free-surface stress conditions for incompressible-flow calculations, J. Comput. Phys. 2 (1968) 403-411
+
 \bibitem{LBM1} {\sc S. CHEN, G.D. DOOLENM}, Lattice Boltzmann method for fluid flows, Ann. Rev. Fluid Mech. 30 (1998) 329-364.

### 2015-11-15 Paper/paper.tex
Kleinigkeiten am Paper

--- 2015-11-15 Paper/paper.tex
@@
 
-Gn this publication we use a hybrid lattice Boltzmann level set method.
+In this publication we use a hybrid lattice Boltzmann level set method.
 The motion of the interface is modelled by the level set method.
@@
 At the center, a sphere of radius $0.25$ was placed with $\varrho_2 = 1.1$ while the exterior contained a fluid with $\varrho_1 = 1$.
-It is visible, how the approximated values attain the analytical solution in a oscillatory motion decaying amplitude, until both values agree.
+It is visible, how the approximated pressure attains the analytical solution in a oscillatory motion with decaying amplitude, until both values agree.
 The algorithm needed 1000 LBM-iterations, where every ten iterations, a call to the level-set routine was executed.

### 2015-11-15 Paper/paper.tex
Lid driven cavity
mit tropfen

--- 2015-11-15 Paper/paper.tex
@@
 \section{Introduction}
-%Something about the two-phase problem and some other algorithms that solve it. We could do this according to the presentation-slides.
 In engineering the immiscible multiphase flow problem often needs to be considered.
-For example, bubble dynamics are decisive for the design of chemical reactors.
+For example, bubble dynamics are decisive for the design of chemical reactors \cite{trygg}.
 Also, fingering in oil recovery is a common multiphase problem.
@@
 This method has the advantage that it allows for large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
+
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}).
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
+The material properties in each fluid are constant and the interface is assumed to be sharp.
+Thus, the overall material properties are discontinuous and the fluids will not mix.
 
@@
 Finally, we verified our implementation with different test cases.
-Possible applications for our algorithm are shown in figures TODO \& TODO, which show the transient movement of an oil drop in a lid driven cavity.
+
+A more vivid possible application of the algorithm we presented is shown in figure TODO, which shows the transient movement of an oil drop in a lid driven cavity.
 %Fig TODO shows two rising and coalescing bubbles in a fluid, produced with our code.
 
-We particularly want to thank Ian Mitchell for providing the toolbox for level set methods.
+The authors want to thank Ian Mitchell for providing the toolbox for level set methods.
 
@@
 \bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.
+
+\bibitem{trygg} {\sc G. TRYGGVASON, R. SCARDOVELLI, S. ZALESKI}, Direct Numerical Simulations of Gas-Liquid Multiphase Flows, Cambridge University Press, ISBN 9780521782401 (2011)
 

### 2015-11-15 ian_mitchell-toolbox/lbm/main.m

@@ -13,20 +13,20 @@ clear;
 % http://www.mathworks.com/matlabcentral/fileexchange/11837-fast-and-robust-curve-intersections
 
 %% Physical setup
-t_end = 50; % [s]
+t_end = 5; % [s]
 x_len = 1; % [m]
 y_len = 1; % [m]
-rho_phys(1) = 1.1; % [kg/m^3] % Mass-density of Fluid 1,
-rho_phys(2) = 1; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
-visc(1) = 1/6;% [m^2/s] kinematic viscosity of fluid 1
-visc(2) = 1/6;% [m^2/s] kinematic viscosity of fluid 2
-sigma = 1e-5;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air
+rho_phys(1) = 1; % [kg/m^3] % Mass-density of Fluid 1,
+rho_phys(2) = 1.01; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
+visc(1) = 2/6;% [m^2/s] kinematic viscosity of fluid 1
+visc(2) = 3/6;% [m^2/s] kinematic viscosity of fluid 2
+sigma = 1e-6;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air
 
-use_periodic_x = 1; % Use periodic boundaries on left/right domain border?
+use_periodic_x = 0; % Use periodic boundaries on left/right domain border?
 % -> Otherwise No-Slip/Bounce-Back
-use_periodic_y = 1; % Use periodic boundaries on top/bottom domain border?
+use_periodic_y = 0; % Use periodic boundaries on top/bottom domain border?
 % -> Otherwise No-Slip/Bounce-Back, optionally moving Top-boundary
-lidVel = 0; % [m/s] x-Velocity of the top Lid
+lidVel = 2; % [m/s] x-Velocity of the top Lid
 
 testcase = 'circle'; %possible values: 'line', 'circle'
 % !!NOTE!! Initial Inteface is defined below (Line 87), once Level-Set Grid was initialized
@@ -88,8 +88,8 @@ switch(testcase)
   case 'circle'
[…]

### 2015-11-15 Paper/paper.tex
noch ein paar Kleinigkeiten

--- 2015-11-15 Paper/paper.tex
@@
 The input data for the level set method is given by the lattice Boltzmann method (LBM), which is applied independently for each fluid.
-This method has the advantage that it allows for large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
+This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
 
@@
 \end{equation} 
-while the pressure is related to the lattice density $\rho$ as $p=\varrho * \rho/3$.
+while the pressure is related to the lattice density $\rho$ as $p=\varrho \cdot \rho/3$.
 
@@
 with the velocity $\vec v = \vec u(\vec x(t))$ for $\vec x(t) \in \Gamma_t$, which we obtain from the LBM.
-It is easily visible, that the normal of the surface is determined as $\vec n(x) = \frac{\nabla \varphi(x)}{\|\varphi(x)\|}$ and accordingly the curvature as the divergence of the normal $\kappa = \nabla \cdot \nabla \varphi = \Delta \varphi$.
+It is easily visible that the normal of the surface is determined as $\vec n(x) = \frac{\nabla \varphi(x)}{\|\varphi(x)\|}$ and accordingly the curvature as the divergence of the normal $\kappa = \nabla \cdot \nabla \varphi = \Delta \varphi$.
 
@@
 For this flow scenario an analytic solution can be derived from the Navier-Stokes equations, namely they simplify to $\frac{\partial }{\partial y}\left( \eta\frac{\partial u}{\partial y}\right) =0$.
-In combination with the no-slip conditions at top and bottom and wall this means, that the horizontal velocity has a linear profile with a kink at the fluid interface.
+In combination with the no-slip conditions at top and bottom wall this means that the horizontal velocity has a linear profile with a kink at the fluid interface.
 The respective slopes between both phases are related by $\frac{\partial_y u^{(1)}}{\partial_y u^{(2)}} = \frac{\eta^{(2)}}{\eta^{(1)}}$.
@@
 If it would get distorted, surface tension would have a stabilizing effect although.
-Hence, we use the Young-Laplace law for the pressure drop across curved surfaces, to validate the implementation of surface tension.
+Hence, we use the Young-Laplace law for the pressure drop across curved surfaces to validate the implementation of surface tension.
 Due to surface tension the pressure inside of convex surfaces is generally higher than on the outside and the pressure drop $\Delta p$ of a bubble of radius $r$ is proportional to the surface tension coefficient $\sigma$ according to the following relationship,
@@
 It is visible, how the approximated values attain the analytical solution in a oscillatory motion decaying amplitude, until both values agree.
-The algorithm needed 1000 LBM-iterations, where every ten iterations, a call to the level-set routine was executed.
+The algorithm needed 1000 LBM-iterations, where every ten iterations a call to the level-set routine was executed.
 Both fluids had an identical viscosity of $\nu = 1/6$.
@@
 We explain those fluxes as inaccuracies stemming from the used level set subroutines, according to the analysis shown in \cite{Thoemmes2}.
-Additionally, we want to state, that we were not able to attain stable results for surface tension coefficients $\sigma > \mathrm{O(10^{-3})}$.
-Large densitiy ratios were limited to big viscosity regimes, or refined spatial resolution in our tests.
+Additionally, we want to state that we were not able to attain stable results for surface tension coefficients $\sigma > \mathrm{O(10^{-3})}$.
+Large densitiy ratios were limited to big viscosity regimes or refined spatial resolution in our tests.
 

### 2015-11-15 Paper/paper.tex

@@
 This method has the advantage that it allows large ranges of viscosity- and density-ratios between the fluid phases, while describing a sharp interface.
+
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}).
+To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
+The material properties in each fluid are constant and the interface is assumed to be sharp.
+Thus, the overall material properties are discontinuous and the fluids will not mix.
 
@@
 At the center, a sphere of radius $0.25$ was placed with $\varrho_2 = 1.1$ while the exterior contained a fluid with $\varrho_1 = 1$.
-It is visible, how the approximated values attain the analytical solution in a oscillatory motion decaying amplitude, until both values agree.
+It is visible, how the approximated pressure attains the analytical solution in a oscillatory motion with decaying amplitude, until both values agree.
 The algorithm needed 1000 LBM-iterations, where every ten iterations a call to the level-set routine was executed.

### 2015-11-15 Paper/paper.tex
Langsam fertig

--- 2015-11-15 Paper/paper.tex
@@
 
-A more vivid possible application of the algorithm we presented is shown in figure TODO, which shows the transient movement of an oil drop in a lid driven cavity.
-%Fig TODO shows two rising and coalescing bubbles in a fluid, produced with our code.
+A more vivid possible application of the algorithm we presented is shown in \cref{cavity}, which shows the transient movement of an oil drop in a lid driven cavity.
+It is a known problem that level set methods tend to suffer from mass losses \cite{Thoemmes}, but ...
+TODO .trotzdem gut?
 
 The authors want to thank Ian Mitchell for providing the toolbox for level set methods.
-
-%TODO: add some nice pictures
+\begin{figure}
+	\hfill\includegraphics[trim = 0mm 8cm 0mm 8.0cm, clip, width=.95\textwidth, natwidth=595,natheight=842]{cavity.pdf}\hspace*{\fill}
+	\caption{The transient flow and deformation of a bubble in a lid driven cavity. The black lines show the interface at different points of time and the arrows display the velocity field.}
+	\label{cavity}
+\end{figure}
 

### 2015-11-15 Example codes/LBM_25_LINES_AND_VIEW/LBM_VIEW.m

@@ -1,174 +1,0 @@
-%% Sébastien Leclaire (2014)
-clear all;close all;addpath('distFig');rng('default');NX=10; NY=10; OMEGA=1.0; rho0=1.0; deltaUX=10^-6; 
-W=[4/9,1/9,1/36,1/9,1/36,1/9,1/36,1/9,1/36];
-cx=[0,0,1,1, 1, 0,-1,-1,-1];cy=[0,1,1,0,-1,-1,-1, 0, 1];
-SOLID=rand(NX*NY,1)>0.7;
-figure(1);figure(2);distFig('Rows',1);
-
-N=bsxfun(@times,rho0*ones(NX*NY,9),W)+0*1/36*(rand(NX*NY,9)-0.5);
-[x,y]=ind2sub([NX NY],1:NX*NY);x=x';y=y';
-x=repmat(x,1,9);
-y=repmat(y,1,9);
-cmap=jet(9)*0+0.5;
-
-figure(1);clf
-hold on;
-for i=1:NX*NY
-    if SOLID(i)
-        p = patch([x(i)-0.5 x(i)+0.5 x(i)+0.5 x(i)-0.5 x(i)-0.5],...
-            [y(i)-0.5 y(i)-0.5 y(i)+0.5 y(i)+0.5 y(i)-0.5], [0 0 0]);
-    end
-end
-for i=2:9
-    CNORM=hypot(cx(i),cy(i));
-    Nx=bsxfun(@times,N(:,i),cx(i)*CNORM);%./sum(N,2);
-    Ny=bsxfun(@times,N(:,i),cy(i)*CNORM);%./sum(N,2);
-    hfull{i}=quiver(x(:,i),y(:,i),Nx*4,Ny*4,'color',cmap(i,:),'autoscale','off','LineWidth',2);
-end
-axis image
-axis([0 NX+1 0 NY+1])
-axis off
-plot([0.5 NX+.5 NX+.5 0.5 0.5],[0.5 0.5 NY+.5 NY+.5 0.5],'k-','LineWidth',2)
-title('Initial condition.','fontsize',20)
-drawnow
-pause(2)
-
-for t_=1:4000    
-    pauseTime=1;
-    %% Collision
-    
-    figure(1);clf;hold on
-    for i=1:NX*NY
-        if SOLID(i)
-            p = patch([x(i)-0.5 x(i)+0.5 x(i)+0.5 x(i)-0.5 x(i)-0.5],...
[…]

### 2015-11-15 Example codes/LBM_25_LINES_AND_VIEW/distFig/distFig.m

@@ -1,249 +1,0 @@
-function distFig(varargin)
-% ===== Syntax ============================================================
-%
-% distFig(...,'Screen',Value)	/ distFig(...,'Scr',Value)
-% distFig(...,'Position',Value) / distFig(...,'Pos',Value)
-% distFig(...,'Rows',Value)
-% distFig(...,'Not',Value)
-% distFig(...,'Only',Value)
-% distFig(...,'Offset',Value)
-%
-% ===== Description =======================================================
-%
-% distFig(...,'Screen',Value) assigns where the figures will be
-% distributed. Value can be:
-% 'Left' / 'L'
-% 'Right' / 'R'
-% 'Top' / 'T'
-% 'Center' / 'C' (Default)
-%
-% distFig(...,'Position',Value) assigns in which part of the screen the
-% figures will be distributed. Value can be:
-% 'Left' / 'L'
-% 'Right' / 'R'
-% 'Center' / 'C' (Default)
-%
-% distFig(...,'Rows',Value) assigns how many rows the figures will be
-% distributed on. Value must be an integer larger than zero. The default
-% number of rows is 2.
-%
-% distFig(...,'Not',Value) excludes specified figures from the distribution
-% list. Value must be an matrix with the excluded figure numbers.
-%
-% distFig(...,'Only',Value) does only distrubute specified figures. Value
-% must be an matrix with the figure which will be destributed.
-%
-% distFig(...,'Offset',Value) can be used to shift all figures on the
-% distribution list. Value must be an integer larger or equal to zero. The
-% default offset value is 0.
-%
-% ===== Examples ==========================================================
-%
-% distFig();
-% This will distribute all open figures on the primary screen in two rows.
-%
-% distFig('Screen','Left','Position','Right','Only',[1,2,4])
-% This will only distrubute figure 1, 2 and 4 on the right part of the left
-% screen.
-%
-% distFig('Offset',2,'Not',[1,2])
-% This will distribute all figure but figure 1 and 2 in the same pattern as
-% distFig(), but figure 1 and 2 will not be distributed, but instead there will
-% be blank spots where they would have been distributed.
-% 
-% ===== Short notation ====================================================
-% 
-% An alternative way of using 'Screen', 'Position', 'Rows' and 'Offset' is
-% to use the short notation. For example:
-%
[…]

### 2015-11-15 Example codes/shanchen.m

@@ -1,128 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% shanChen.m: Multi-component fluid, using a LB method,
-%   based on the Shan-Chen model
-% [X.Shan and H.Chen, http://dx.doi.org/10.1103/PhysRevE.47.1815].
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, written in Matlab
-% Copyright (C) 2008 Orestis Malaspinas, Andrea Parmigiani, Jonas Latt
-% Address: EPFL-STI-LIN Station 9
-% E-mail: orestis.malaspinas@epfl.ch
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public
-% License along with this program; if not, write to the Free
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-clear
-clf
-
-% GENERAL FLOW CONSTANTS
-
-ly           = 201;
-lx           = 201;
-
-G = -1.2;  % Amplitude of the molecular interaction force
-
-omega1 = 1.;  % Relaxation parameter for fluid 1
[…]

### 2015-11-15 Example codes/voflbm/BreakingDam.m

@@ -1,189 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% BreakingDam.m: show behavior of breaking dam and 
-% free surface
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/Couette.m

@@ -1,115 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
-global ly;      % domain size y
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   7   3   6 
-%    \  |  /   
-%   4 - 1 - 2 
-%    /  |  \    
-%   8   5   9 
-%
-% D2Q9 lattice definitions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-b = 9;
-weight = [4/9, 1/9,1/9,1/9,1/9, 1/36,1/36,1/36,1/36]; 
-cx  = [ 0, 1, 0, -1, 0, 1, -1, -1, 1]; 
-cy  = [ 0, 0, 1, 0, -1, 1,  1, -1, -1];
-%dir = [ 1, 2, 3, 4,  5, 6,  7,  8,  9];
-inv = [ 1, 4, 5, 2,  3, 8,  9,  6,  7];
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Initialization starts here
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-lx = 16; ly = 14;
-tau = 2.0;
-omega = 1/tau;
-fx = 0.0;
-
-% create array of PDFs
-f = zeros(ly,lx,9);
-for i=1:9
-    f(:,:,i) = weight(i);
-end
-
-% create array for the boundary
-boundary = zeros(ly,lx);
-ub = zeros(ly, lx, 2);
-
-for i=1:lx
-  for j=1:ly
-      if((j-0.5) > (1+8 +0.25*(i-0.5)))
-	boundary(j,i) = 1.0;
-	ub(j,i,2) = 0.0025;
-	ub(j,i,1) = 0.01;
-      end
-      if((j-0.5) < (1 + 0.25*(i-0.5)))
[…]

### 2015-11-15 Example codes/voflbm/FilmFlow.m

@@ -1,173 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FilmFlow.m: Planar film low test case
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/FilmFlowLinear.m

@@ -1,180 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FilmFlowLinear.m: Planar film low test case
-%  using linearly interpolated interface condition
-%  here we can prescribe an arbitrary (non-integral)
-%  film thickness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
[…]

### 2015-11-15 Example codes/voflbm/Poiseuille.m

@@ -1,146 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Poiseuille.m: Poiseuille test case
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/PoiseuillePressure.m

@@ -1,168 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Poiseuille.m: Poiseuille test case
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
[…]

### 2015-11-15 Example codes/voflbm/Test.m

@@ -1,166 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Test.m: Experimental test case
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/TestInterface.m

@@ -1,188 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TestInterface.m: test free surface (Koerner et al., 2005)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/TestInterface_diag.m

@@ -1,188 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TestInterface_diag.m: test free surface (Koerner et al., 2005)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/TestInterface_y.m

@@ -1,188 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TestInterface_y.m: test free surface (Koerner et al., 2005)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GLOBAL VARIABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-global b;       % number of lattice dirs
-global weight;  % lattice weights
-global cx;      % stencil x
-global cy;      % stencil y
-global inv;     % inverse directions
-global lx;      % domain size x
[…]

### 2015-11-15 Example codes/voflbm/adjustFillLevel.m

@@ -1,43 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% adjustFillLevel.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-function [ fill_level ] = adjustFillLevel( fill_level,mass,rho)
-%BOUNDARIES does the half-way bounce back in cells, BEFORE the streaming
-% i.e. copies the post-col pdfs from boundary nodes into the inverted
-% direction of the obstacle nodes
-
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   
-   %[j,i] = find(interface);
-   %for k=1:length(i)
-    %   fill_level(i,j) = mass(i,j)./ rho(i,j);
-   %end
-   fill_level = mass./rho;
-end

### 2015-11-15 Example codes/voflbm/boundariesAfterStream.m

@@ -1,46 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% boundariesAfterStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = boundariesAfterStream( f, boundary )
-%BOUNDARIES does the half-way bounce back in cells, AFTER the streaming
-% i.e. off-domain nodes contain the postcol pdfs from the boundary nodes
-%   having a non-zero entry in the boundary field
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   
-   [j,i] = find(boundary);
-   for k=1:length(i)
-       for dir=1:b
-           % let (ni,nj) be the boundary node with an off-domain node
-           % in direction dir
-           nj = mod(j(k)-cy(dir)-1,ly) + 1;
-           ni = mod(i(k)-cx(dir)-1,lx) + 1;
-           f(nj, ni, inv(dir)) = f(j(k), i(k), dir);
-       end
-   end
-end

### 2015-11-15 Example codes/voflbm/boundariesBeforeStream.m

@@ -1,48 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% boundariesBeforeStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-function [ f ] = boundariesBeforeStream( f, boundary )
-%BOUNDARIES does the half-way bounce back in cells, BEFORE the streaming
-% i.e. copies the post-col pdfs from boundary nodes into the inverted
-% direction of the obstacle nodes
-
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   
-   [j,i] = find(boundary);
-   for k=1:length(i)
-       for dir=1:b
-           % let (ni,nj) be the boundary node neighbor with the off-domain node
-           % in direction dir
-           nj = mod(j(k)-cy(dir)-1,ly) + 1;
-           ni = mod(i(k)-cx(dir)-1,lx) + 1;
[…]

### 2015-11-15 Example codes/voflbm/calcMacro.m

@@ -1,37 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% calcMacro.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ rho, ux, uy ] = calcMacro( f )
-%CALCMACRO Summary of this function goes here
-%   Detailed explanation goes here
-
-    global b;
-    global cx;
-    global cy;
-    
-    rho = sum(f,3);
-    ux  = (sum(f(:,:,[2 6 9]),3)-sum(f(:,:,[4 7 8]),3))./rho;
-    uy  = (sum(f(:,:,[3 6 7]),3)-sum(f(:,:,[5 8 9]),3))./rho;
-end
-

### 2015-11-15 Example codes/voflbm/cellConversion.cc

@@ -1,383 +1,0 @@
-#include <octave/oct.h>
-
-// TODO: check boundary because of periodicity!!!! -> change cell conversions!!!
-
-DEFUN_DLD( cellConversion,args,, "do necessary cell conversions")
-{
-   int    ly     	= args(0).int_value();
-   int    lx     	= args(1).int_value();
-   Matrix mass      	= args(2).matrix_value();
-   Matrix fill      	= args(3).matrix_value();
-   Matrix liquid    	= args(4).matrix_value();
-   Matrix interface	= args(5).matrix_value();   
-   Matrix gas       	= args(6).matrix_value();  
-   Matrix conv_I_L  	= args(7).matrix_value();  
-   Matrix conv_I_G  	= args(8).matrix_value();
-   Matrix fValues       = args(9).matrix_value();
-   int    b             = args(10).int_value();
-   RowVector weight     = args(11).row_vector_value();
-   RowVector cx         = args(12).row_vector_value();
-   RowVector cy         = args(13).row_vector_value();  
-   
-   octave_value_list retval;
-
-   const double tol = 0.01; 
-
-   //---------------------------------------------------------------------//
-   // 4 possible cell conversions   
-   for(int i = 1; i < ly+1; i++){
-      for( int j=1;j< lx+1; j++){
- 
-      int i_left  = ((i-2) % ly) + 1; // i-1  
-      int i_right = (    i % ly) + 1; // i+1
-
-      int j_left  = ((j-2) % lx) + 1; // j-1
-      int j_right = ( j    % lx) + 1; // j+1
-
-      // I -> L
-      // TODO: conv_I_L = zeros(ly,lx) -> otherwise old values!!!!
-      if ( (fill(i,j)>= 1.0 + tol) && (interface(i,j)== 1) )  	// convert cell to liquid cell 
-      {
-         interface(i,j) = 0;
-         liquid(i,j)    = 1;       	   			// counter for gas cells in neighborhood -> how we can distribute mass
-         int counter    = 0;
-	 
-              if( gas(i_right,j)==1)    	 			// search for gas cells! -> convert them to interface cells
-              {
-                    gas(i_right,j) 		= 0;   	 		// generate new interface cell!
-                    interface(i_right,j) 	= 1;
[…]

### 2015-11-15 Example codes/voflbm/cellConversion2.cc

@@ -1,202 +1,0 @@
-#include <octave/oct.h>
-
-// TODO: check boundary because of periodicity!!!! -> change cell conversions!!!
-
-DEFUN_DLD( cellConversion2,args,, "do necessary cell conversions")
-{
-   int    ly     	= args(0).int_value();
-   int    lx     	= args(1).int_value();
-   Matrix mass      	= args(2).matrix_value();
-   Matrix fill      	= args(3).matrix_value();
-   Matrix liquid    	= args(4).matrix_value();
-   Matrix interface	= args(5).matrix_value();   
-   Matrix gas       	= args(6).matrix_value();  
-   Matrix conv_I_L  	= args(7).matrix_value();  
-   Matrix conv_I_G  	= args(8).matrix_value();
-   NDArray fValues      = args(9).array_value();
-   int    b             = args(10).int_value();
-   RowVector weight     = args(11).row_vector_value();
-   RowVector cx         = args(12).row_vector_value();
-   RowVector cy         = args(13).row_vector_value();  
-   
-   octave_value_list retval;
-
-   const double tol = 0.01; 
-
-   //---------------------------------------------------------------------//
-   // 4 possible cell conversions   
-   for(int i = 0; i < ly; i++){
-      for( int j=0; j< lx; j++){
-
-      // I -> L
-      // TODO: conv_I_L = zeros(ly,lx) -> otherwise old values!!!!
-      if ( (fill(i,j)>= 1.0 + tol) && (interface(i,j)== 1) )  	// convert cell to liquid cell 
-      {
-         interface(i,j) = 0;
-         liquid(i,j)    = 1;       	   			// counter for gas cells in neighborhood -> 
-								// how we can distribute mass
-         int counter    = 0;
-
-         std::cout << "I-> L begin" <<" " << "i: " << i << " j: " << j << std::endl;	
-         for(int k=1; k<b; k++)
-   	 {
-
-           std::cout << "Search gas neighbors" << std::endl;
-           
-           /// adjust mod to get positive values
-           //int ni = ((i+(int)cy(k)-1) % ly);
-   	   //int nj = ((j+(int)cx(k)-1) % lx);
-           int ni = ( (i+(int)cy(k) -1 ) % ly);
-           int nj = ( (j+(int)cx(k) -1 ) % lx);
-           if(ni < 0){
[…]

### 2015-11-15 Example codes/voflbm/cellConversion3.cc

@@ -1,323 +1,0 @@
-#include <octave/oct.h>
-
-// TODO: check boundary because of periodicity!!!! -> change cell conversions!!!
-
-DEFUN_DLD( cellConversion3,args,, "do necessary cell conversions")
-{
-   int    ly     	= args(0).int_value();
-   int    lx     	= args(1).int_value();
-   Matrix mass      	= args(2).matrix_value();
-   Matrix fill      	= args(3).matrix_value();
-   Matrix liquid    	= args(4).matrix_value();
-   Matrix interface	= args(5).matrix_value();   
-   Matrix gas       	= args(6).matrix_value();  
-   Matrix conv_I_L  	= args(7).matrix_value();  
-   Matrix conv_I_G  	= args(8).matrix_value();
-   NDArray fValues      = args(9).array_value();
-   int    b             = args(10).int_value();
-   RowVector weight     = args(11).row_vector_value();
-   RowVector cx         = args(12).row_vector_value();
-   RowVector cy         = args(13).row_vector_value();  
-   
-   octave_value_list retval;
-
-   const double tol = 0.01; 
-
-   //---------------------------------------------------------------------//
-   // 4 possible cell conversions   
-   for(int i = 0; i < ly; i++){
-      for( int j=0; j< lx; j++){
-
-      // I -> L
-      // TODO: conv_I_L = zeros(ly,lx) -> otherwise old values!!!!
-      if ( (fill(i,j)>= 1.0 + tol) && (interface(i,j)== 1) )  	// convert cell to liquid cell 
-      {
-         std::cout << " I -> L begin!!! at (i= " << i << "," << "j= " << j << ")" << std::endl; 
-         interface(i,j) = 0;
-         liquid(i,j)    = 1;       	   			// counter for gas cells in neighborhood ->  how we can distribute mass
-         int counter    = 0;
-       
-         for(int k=1; k<b; k++)
-   	 {
-           // std::cout << "Search gas neighbors: k = " << k  << std::endl;         
-           int ni = ( (i+(int)cy(k) ) % ly);
-           int nj = ( (j+(int)cx(k) ) % lx);
-           if(ni < 0){
-	      ni = ly - (abs( i+(int)cy(k) ) % ly);
-           }
-	   if(nj < 0){
-	      nj = lx - (abs( j+(int)cx(k) ) % lx);
-           }
[…]

### 2015-11-15 Example codes/voflbm/cellConversion4.cc

@@ -1,250 +1,0 @@
-#include <octave/oct.h>
-
-// TODO: check boundary because of periodicity!!!! -> change cell conversions!!!
-
-DEFUN_DLD( cellConversion4,args,, "do necessary cell conversions")
-{
-   int    ly     	= args(0).int_value();
-   int    lx     	= args(1).int_value();
-   Matrix mass      	= args(2).matrix_value();
-   Matrix fill      	= args(3).matrix_value();
-   Matrix liquid    	= args(4).matrix_value();
-   Matrix interface	= args(5).matrix_value();   
-   Matrix gas       	= args(6).matrix_value();  
-   Matrix conv_I_L  	= args(7).matrix_value();  
-   Matrix conv_I_G  	= args(8).matrix_value();
-   NDArray fValues      = args(9).array_value();
-   int    b             = args(10).int_value();
-   RowVector weight     = args(11).row_vector_value();
-   RowVector cx         = args(12).row_vector_value();
-   RowVector cy         = args(13).row_vector_value();  
-   
-   octave_value_list retval;
-
-   const double tol = 0.01; 
-   //---------------------------------------------------------------------//
-   // possible cell conversions   
-   for(int i = 0; i < ly; i++){
-      for( int j=0; j< lx; j++){
-
-      // I -> L
-      // TODO: conv_I_L = zeros(ly,lx) -> otherwise old values!!!!
-      if ( (fill(i,j)>= 1.0 + tol) && (interface(i,j)== 1) )  	// convert cell to liquid cell 
-      {
-         std::cout << " I -> L begin!!! at (i= " << i << "," << "j= " << j << ")" << std::endl; 
-         interface(i,j) = 0;
-         liquid(i,j)    = 1;       	   			// counter for gas cells in neighborhood ->  how we can distribute mass
-         int counter    = 0;
-       
-         for(int k=1; k<b; k++)
-   	 {
-            std::cout << "Search gas neighbors: k = " << k  << std::endl;         
-           int ni = ( (i+(int)cy(k) ) % ly);
-           int nj = ( (j+(int)cx(k) ) % lx);
-           if(ni < 0){
-	      ni = ly - (abs( i+(int)cy(k) ) % ly);
-           }
-	   if(nj < 0){
-	      nj = lx - (abs( j+(int)cx(k) ) % lx);
-           }
[…]

### 2015-11-15 Example codes/voflbm/collideBGK.m

@@ -1,33 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% collideBGK.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ fOut ] = collideBGK( fIn, omega )
-%COLLIDE Summary of this function goes here
-%   Detailed explanation goes here
-    fEq = project(fIn);
-    
-    fOut = fIn - omega*(fIn - fEq);
-
-end
-

### 2015-11-15 Example codes/voflbm/collideTRT.m

@@ -1,50 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% collideTRT.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ fOut, NonEq ] = collideTRT( fIn, lambda_even, lambda_odd )
-global inv b;
-%COLLIDE Relaxation according to Ginzburgs TRT model
-%   lambda_even controls viscosity
-%   lambda_odd should be chosen as
-%     -( 2.0*lambda_even + 4.0 )/( (4*Lambda - 1.0)*lambda_even - 2.0 )
-%   where Lambda = 1/4 controls the magic
-    NonEq = fIn - project(fIn);
-    
-%     for i=1:b
-%         fEven(:,:,i) = 0.5*(fIn(:,:,i) + fIn(:,:,inv(i)));
-%         fOdd(:,:,i) = 0.5*(fIn(:,:,i) - fIn(:,:,inv(i)));
[…]

### 2015-11-15 Example codes/voflbm/entropicEq.m

@@ -1,44 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% entropicEq.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [fEq] = entropicEq( ux, uy )
-%ENTROPICEQ Summary of this function goes here
-%   Detailed explanation goes here
-
-    global b;           % the number of dirs
-    global dir;         % the lattice directions
-    global weight;     % the lattice weights
-    global cx;
-    global cy;
-
-
-    for dir=1:b
-        sqtrmX = sqrt(1 + 3*ux.*ux);
-        sqtrmY = sqrt(1 + 3*uy.*uy);
-        fEq(:,:,dir)  = weight(dir) ...
-                   .* (2 - sqtrmX) .* ((2*ux + sqtrmX)./(1-ux)).^cx(dir)...
-                   .* (2 - sqtrmY) .* ((2*uy + sqtrmY)./(1-uy)).^cy(dir);
-    end
-end
-

### 2015-11-15 Example codes/voflbm/externalForce.m

@@ -1,37 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% externalForce.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = externalForce( rho, f, fx,fy )
-%EXTERNALFORCE Summary of this function goes here
-% (exactly as in He, Zou, Luo, Dembo 1997; also Luo 2000 eq (31))
-    global b;
-    global cx cy;
-    global weight;
-    
-    for dir=1:b
-        ca = (cx(dir)*fx+cy(dir)*fy); % discrete vel times force
-        f(:,:,dir) = f(:,:,dir) + 3*weight(dir)*rho*ca;
-    end
-end
-

### 2015-11-15 Example codes/voflbm/helloworld.cc

@@ -1,14 +1,0 @@
-#include <octave/oct.h>
-
-
-DEFUN_DLD (helloworld, args, nargout,
-           "Hello World Help String")
-{
-  int nargin = args.length ();
-
-  octave_stdout << "Hello World has "
-                << nargin << " input arguments and "
-                << nargout << " output arguments.\n";
-
-  return octave_value_list ();
-}

### 2015-11-15 Example codes/voflbm/interfaceBeforeStream.m

@@ -1,52 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% interfaceBeforeStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = interfaceBeforeStream( f, boundary, ux, uy )
-%INTERFACE-BOUNDARIES does the half-way pressure bounce back according to Koerner in cells, BEFORE the streaming
-% i.e. fetches the post-col pdfs from boundary nodes for the bc
-
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   global weight; % lattice weights
-   
-   [j,i] = find(boundary);
-   for k=1:length(i)
-       for dir=1:b
-           % let (ni,nj) be the boundary node neighbor with the off-domain node
-           % in direction dir
[…]

### 2015-11-15 Example codes/voflbm/interfaceLiBeforeStream.m

@@ -1,72 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% pabBeforeStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = interfaceLiBeforeStream( f, fNeq, boundary, delta, lambdaE, rho, ux, uy )
-%Pressure-BOUNDARIES does the half-way pressure ANTI-bounce back according to Ginzburg in cells, BEFORE the streaming
-% i.e. fetches the post-col pdfs from boundary nodes for the bc
-
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   global weight; % lattice weights
-
-   for i=1:b
-        NEven(:,:,i) = 0.5*(fNeq(:,:,i) + fNeq(:,:,inv(i)));
[…]

### 2015-11-15 Example codes/voflbm/linearEq.m

@@ -1,40 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% polynomialEq.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function fEq = linearEq( ux, uy )
-%linearEq Calculate linear equilibrium
-    
-    global b;           % the number of dirs
-    global weight;     % the lattice weights
-    global cx;
-    global cy;
-
-    
-    for dir=1:b
-        cu = 3*(cx(dir)*ux+cy(dir)*uy);
-        fEq(:,:,dir)  = weight(dir) * ( 1 + cu );
-    end
-end
-
-

### 2015-11-15 Example codes/voflbm/massExchange.m

@@ -1,49 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% massExchange.m: 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%function [ deltaM ] = massExchange( mass, fOld, fNew )
-function [deltaM]   = massExchange(liquid,interface,fOld,fNew)
-global lx ly cx cy b inv;
-%MASSEXCHANGE Given the old (post-collision) pdf-field fOld and the new
-% (streamed) pdf-field fNew
-%   Compute the mass exchange from the streaming
-% ATTENTION: boundary conditions must be set already!!
-    deltaM = zeros(ly,lx);
-    %fluid = mass > 0.0;
-    fluid = liquid+interface > 0.0;
-
-    for i=1:b
-        %deltaM(:,:) = deltaM(:,:) + circshift(mass, [cy(i), cx(i)]).*fNew(:,:,i) -
-	%mass(:,:).*fOld(:,:,inv(i));
[…]

### 2015-11-15 Example codes/voflbm/movingboundariesAfterStream.m

@@ -1,51 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% movingboundaries.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = movingboundaries( f, boundary, rho, ub )
-%BOUNDARIES does the half-way bounce back in cells
-%   having a non-zero entry in the boundary field
-%   rho is the density field
-%   ub is a matrix prescribing the boundary velocity
-   global b;        % number of lattice dirs
-   global cx;       % stencil x
-   global cy;       % stencil y
-   global inv;      % inverse directions
-   global weight;   % the lattice weights
-   global lx;       % domain size x
-   global ly;       % domain size y
-   
-   
-   [j,i] = find(boundary);
-   for k=1:length(i)
-       for dir=1:b
-           % let (ni,nj) be the boundary node with an off-domain node
-           % in direction dir
-           nj = mod(j(k)-cy(dir)-1,ly) + 1;
[…]

### 2015-11-15 Example codes/voflbm/movingboundariesShifted.m

@@ -1,62 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% movingboundaries.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = movingboundariesShifted( f, boundary, rho, ub,number )
-%BOUNDARIES does the half-way bounce back in cells
-%   having a non-zero entry in the boundary field
-%   rho is the density field
-%   ub is a matrix prescribing the boundary velocity
-   global b;        % number of lattice dirs
-   global cx;       % stencil x
-   global cy;       % stencil y
-   global inv;      % inverse directions
-   global weight;   % the lattice weights
-   global lx;       % domain size x
-   global ly;       % domain size y
-   
-   
-   [j,i] = find(boundary);
-   for k=1:length(i)
-       for dir=1:b
-           % let (ni,nj) be the boundary node with an off-domain node
-           % in direction dir
[…]

### 2015-11-15 Example codes/voflbm/normeq.m

@@ -1,31 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% normeq.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function fout = normeq( ux, uy )
-    % call either polynomial or entropic Eq.
-    fout = linearEq(ux, uy);
-    %fout = polynomialEq(ux, uy);
-    %fout = entropicEq(ux, uy);
-end
-

### 2015-11-15 Example codes/voflbm/pabBeforeStream.m

@@ -1,64 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% pabBeforeStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ f ] = pabBeforeStream( f, fNeq, boundary, lambdaE, rho, ux, uy )
-%Pressure-BOUNDARIES does the half-way pressure ANTI-bounce back according to Ginzburg in cells, BEFORE the streaming
-% i.e. fetches the post-col pdfs from boundary nodes for the bc
-
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   global weight; % lattice weights
-
-   for i=1:b
-        NEven(:,:,i) = 0.5*(fNeq(:,:,i) + fNeq(:,:,inv(i)));
-   end
-
-   [j,i] = find(boundary);
-   for k=1:length(i)
[…]

### 2015-11-15 Example codes/voflbm/periodicBoundaries.m

@@ -1,50 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% boundariesBeforeStream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-function [ f ] = periodicBoundaries( f )
-% periodic boundaries, BEFORE the streaming
- 
-   global b;    % number of lattice dirs
-   global cx;   % stencil x
-   global cy;   % stencil y
-   global inv;  % inverse directions
-   global lx;   % domain size x
-   global ly;   % domain size y
-   
-
-   for k = 2:(ly-1)
-       for dir = 1:b
-           f(k,1,dir) = f(k,lx,dir); 
-       end
-   end
- 
-   for j = 1:lx
-      for dir = 1:b
-          f(1,j,dir)=f(ly,j,dir);
-      end
-   end
-
-end
-  

### 2015-11-15 Example codes/voflbm/periodicShift.m

@@ -1,48 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% periodicShift.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ out ] = periodicShift( pdfs, number )
-%STREAM Stream the distribution functions
-    
-    global b;
-    global dir; % the lattice directions (stencil)
-    global cx;
-    global cy;
-    global lx;
-    global ly;
-
-    out = pdfs;
-    buffer1(:,:) = pdfs(:,1,:);
-    buffer2(:,:) = pdfs(:,lx,:);
-    ## for dir=1:b
-    ##   out(:,:,dir) = circshift(pdfs(:,:,dir), [number,0]);
-    ##   out(:,:,dir) = circshift(pdfs(:,:,dir), [-number,0]);
-    ## end
-    
-    buffer1 = circshift(buffer1, [number,0]);
-    buffer2 = circshift(buffer2, [-number,0]);
-    
[…]

### 2015-11-15 Example codes/voflbm/polynomialEq.m

@@ -1,41 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% polynomialEq.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function fEq = polynomialEq( ux, uy )
-%PolynomialEq Calculate polynomial equilibrium
-    
-    global b;           % the number of dirs
-    global weight;     % the lattice weights
-    global cx;
-    global cy;
-
-    
-    for dir=1:b
-        cu = 3*(cx(dir)*ux+cy(dir)*uy);
-        fEq(:,:,dir)  = weight(dir) * ...
-                       ( 1 + cu + 1/2*(cu.*cu)  - 3/2*(ux.^2+uy.^2) );
-    end
-end
-
-

### 2015-11-15 Example codes/voflbm/polynomialEq_cell.m

@@ -1,40 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% polynomialEq.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Regina Ammer
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: regina.ammer@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function fEq = polynomialEq( i, j, ux, uy)
-%PolynomialEq Calculate polynomial equilibrium
-    
-    global b;           % the number of dirs
-    global weight;      % the lattice weights
-    global cx;
-    global cy;
-
-    
-    for dir=1:b
-        cu = 3*(cx(dir)*ux+cy(dir)*uy);
-        fEq(dir,1)  = weight(dir) * ( 1 + cu + 1/2*(cu.*cu)  - 3/2*(ux.^2+uy.^2) );
-    end
-end
-
-

### 2015-11-15 Example codes/voflbm/setNewFlagField.cc

@@ -1,34 +1,0 @@
-#include <octave/oct.h>
-
-DEFUN_DLD( setNewFlagField,args, , "set new flag field")
-{
-   int           ly = args(0).int_value();
-   int           lx = args(1).int_value();
-   //int         init = args(2).int_value();
-  
-   Matrix      fill = args(4).matrix_value();
-   Matrix    liquid = args(5).matrix_value();
-   Matrix interface = args(6).matrix_value();   
-   Matrix       gas = args(7).matrix_value();  
- 
-   Matrix    liquid_tmp(args(2).matrix_value());
-   Matrix       gas_tmp(args(2).matrix_value());
-   Matrix interface_tmp(args(2).matrix_value());
-   
-   for(int i = 1; i < ly+1; i++){
-      for( int j=1;j< lx+1; j++){
-      if ( fill(i,j) <= 0.0 )
-         gas(i,j) = 1.0;
-      else if ( (fill(i,j)>0.0) && (fill(i,j)<1.0) )
-         interface(i,j) = 1.0;
-      else if (fill(i,j) == 1.0 )
-         liquid(i,j) = 1.0;
-      }
-   }
-   liquid    = liquid_tmp;
-   gas       = gas_tmp;
-   interface = interface_tmp;
-
-   return octave_value_list();
-
-}

### 2015-11-15 Example codes/voflbm/stream.m

@@ -1,36 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% stream.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Lattice Boltzmann sample, Octave/Matlab script
-% Copyright (C) 2014 Simon Bogner
-% Address:  Chair for System Simulation,
-%           Cauerstraße 11, 91058 Erlangen, Germany
-% E-mail: Simon.Bogner@fau.de
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This program is free software; you can redistribute it and/or
-% modify it under the terms of the GNU General Public License
-% as published by the Free Software Foundation; either version 2
-% of the License, or (at your option) any later version.
-% This program is distributed in the hope that it will be useful,
-% but WITHOUT ANY WARRANTY; without even the implied warranty of
-% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-% GNU General Public License for more details.
-% You should have received a copy of the GNU General Public 
-% License along with this program; if not, write to the Free 
-% Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
-% Boston, MA  02110-1301, USA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function [ out ] = stream( pdfs )
-%STREAM Stream the distribution functions
-    
-    global b;
-    global dir; % the lattice directions (stencil)
-    global cx;
-    global cy;
-
-    for dir=1:b
-        out(:,:,dir) = circshift(pdfs(:,:,dir), [cy(dir),cx(dir)]);
-    end
-end

### 2015-11-15 Example codes/voflbm/test.cc

@@ -1,18 +1,0 @@
-#include <octave/oct.h>
-
-
-DEFUN_DLD (test, args, nargout,
-           "test")
-{  
-  //int number1 = args(0).int_value();
-  //int number2 = args(1).int_value();
-  Matrix matrix_1 = args(0).matrix_value();
-  int lx        = args(1).int_value();
-  int ly   	= args(2).int_value();
-  int num       = args(3).int_value();
-  
-  int result = matrix_1( 0 % ly, 0 % lx);
-
-
-  return octave_value(result);
-}

### 2015-11-15 ian_mitchell-toolbox/Examples/Basic/convectionDemo.m

@@ -1,312 +1,0 @@
-function [ data, g, data0 ] = convectionDemo(flowType, accuracy, displayType)
-% convectionDemo: demonstrate a simple convective flow field.
-%
-%   [ data, g, data0 ] = convectionDemo(flowType, accuracy, displayType)
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   flowType     String to specify type of flow field.
-%                  'constant'    Constant flow field xdot = k (default).
-%                  'linear'      Linear flow field xdot = A x.
-%                  'constantRev' Constant flow field, negate at t_half.
-%                  'linearRev'   Linear flow field, negate at t_half.
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the helper visualizeLevelSet to see the options
-%                  (optional, default depends on grid dimension).
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 2/9/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
-%---------------------------------------------------------------------------
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Basic/laxFriedrichsDemo.m

@@ -1,386 +1,0 @@
-function [ data, g, data0 ] = ...
-       laxFriedrichsDemo(flowType, initShape, accuracy, dissType, displayType)
-% laxFriedrichsDemo: demonstrate Lax-Friedrichs on a convective flow field.
-%
-% [ data, g, data0 ] = ...
-%      laxFriedrichsDemo(flowType, initShape, accuracy, dissType, displayType)
-%  
-% This function demonstrates how the Lax-Friedrichs HJ term approximation
-%   termLaxFriedrichs could be used to approximate a convective flow field.
-%   In practice the LF approximation adds unnecessary dissipation, and so it
-%   should not be used for purely convective flow fields where the upwind
-%   direction can be easily determined (use termConvection instead).
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters (all inputs have defaults):
-%
-%   flowType     String to specify type of flow field.
-%                  'constant'    Constant flow field xdot = k (default).
-%                  'linear'      Linear flow field xdot = A x.
-%   initShape    String to specify what initial surface to use.
-%	   	   'sphere'      A sphere in the appropriate dimension.
-%	 	   'cube'  	 A cube in the appropriate dimension.
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   dissType     Which type of dissipation to use with the LF approximation?
-%                  'global'      Use artificialDissipationGLF.
-%                  'local'       Use artificialDissipationLLF.
-%                  'locallocal'  Use artificialDissipationLLLF.
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the helper visualizeLevelSet to see the options
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Basic/maskDemo.m

@@ -1,350 +1,0 @@
-function [ data, g, data0 ] = maskDemo(accuracy, displayType)
-% maskDemo: demonstrate the masking process on a convective flow.
-%
-% [ data, g, data0 ] = maskDemo(accuracy, displayType)
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the helper visualizeLevelSet to see the options
-%                  (optional, default depends on grid dimension).
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 4/11/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
-%---------------------------------------------------------------------------
-% Make sure we can see the kernel m-files.
-run('../addPathToKernel');
-
-%---------------------------------------------------------------------------
-% Which of the tasks do you wish to perform?
-doMask = 1;
-doMin = 1;
-
-%---------------------------------------------------------------------------
-% Integration parameters.
-tMax = 1.0;                  % End time.
-plotSteps = 9;               % How many intermediate plots to produce?
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Basic/reinitDemo.m

@@ -1,226 +1,0 @@
-function [ data, g, data0 ] = reinitDemo(initialType, accuracy, displayType)
-% reinitDemo: demonstrate the reinitialization equation.
-%
-% [ data, g, data0 ] = reinitDemo(initialType, accuracy, displayType)
-%
-% Demonstrates the application of the reinitialization equation to turn one
-%   of several different dynamic surface functions into signed distance
-%   functions.  While it works in any dimension, it is hard to visualize
-%   the difference in dimensions higher than two.
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   initialType  String to specify which initial dynamic implicit surface.
-%                  'circle'      An off center circle/sphere (default).
-%                  'star'        A star-shaped interface (not 1D).
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the helper visualizeLevelSet to see the options
-%                  (optional, default depends on grid dimension).
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 2/13/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Basic/reinitDemoFigures.m

@@ -1,63 +1,0 @@
-% reinitDemoFigures: figures from reinitDemo
-%
-% This is a script file to generate the figures for reinitDemo that
-% appear in the Toolbox documentation.
-
-% Copyright 2007 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 5/21/07
-
-% Get the data by running reinitDemo
-[ data, g, data0 ] = reinitDemo('star', 'medium', 'surf');
-
-% The figure produced at the end shows the final level set, but we need
-% to make it match a figure showing the initial conditions.  We also need
-% to remove the title.
-f2 = gcf;
-title('');
-
-% Create a figure with the initial conditions.
-f1 = figure;
-surf(g.xs{1}, g.xs{2}, data0);
-axis image;
-initial_axis = axis;
-
-% Adjust the final implicit surface function to use the same axis.
-figure(f2);
-axis(initial_axis);
-
-% Now a figure to show the effects of reinitialization on the zero contour.
-f3 = figure;
-[ ~, h_contour_final ] = contour(g.xs{1}, g.xs{2}, data, [ 0 0 ], 'b-');
-hold on;
-[ ~, h_contour_init ] = contour(g.xs{1}, g.xs{2}, data0, [ 0 0 ], 'r--');
-axis equal;
-axis(g.axis);
-set(h_contour_final, 'LineWidth', 2);
-set(h_contour_init, 'LineWidth', 2);
-legend([ h_contour_final(1), h_contour_init(1) ], ...
-       'after reinitialization', 'before reinitialization');
-
-% And finally a figure to show that the magnitude of the gradient is
-% one.  Note that Matlab's grad function does centered differences, while
-% reinitialization is based on the upwind differences in the Toolbox.
-% But the fact that the gradient magnitude is well behaved even for a
-% different finite difference is good evidence.
-f4 = figure;
-[ dx0 dy0 ] = gradient(data0, g.dx(1), g.dx(2));
-[ dx, dy ] = gradient(data, g.dx(1), g.dx(2));
-mag0 = sqrt(dx0.^2 + dy0.^2);
-mag = sqrt(dx.^2 + dy.^2);
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherFedkiw/animateSpinStar.m

@@ -1,292 +1,0 @@
-function [ data, g, data0 ] = animateSpinStar(filename, accuracy, compress)
-% animateSpinStar: create an animation of the growth of the spinning star.
-%
-%   [ data, g, data0 ] = animateSpinStar(filename, accuracy, compress)
-%  
-% This file generates an animation showing how the spinning star grows
-%   as time progresses.  It is basically a combination of the files:
-%        spinStarDemo (which sets up and handles the level set calculation),
-%        spinAnimation (which has the code necessary for animations).
-%
-% NOTES:
-%
-% 1) This function will probably only work in Windows, since it uses
-%    the avifile command and the avi animation format.
-%
-% 2) While the animation is being generated, don't move anything
-%    (mouse, other windows) in front of the matlab figure window,
-%    otherwise that image will be captured into the avi.
-%
-% 3) If this file stops because of an error, the avi file will remain open.
-%    In that case, you must issue a "clear all" command to get rid of
-%    the open file handle and then delete the partially completed avi file.
-%
-%  
-% Recreates figure 6.2 from O&F chapter 6, showing a combination of motion 
-%   by surface normal and convective rotation of a star-shaped interface 
-%   in two dimensions.
-%
-% The caption claim of "rigid body rotation" is clearly incorrect, since
-%   the tips of the star are rotating faster than the center.
-%
-% This function allows either recreation of the figure or true rigid
-%   body rotation (which is not quite so interesting).
-%
-% The parameters were guessed by trial and error.
-%
-% Parameters:
-%
-%   filename     The name to give to the animation avi file.
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   compress     Boolean specifying whether to use lossy compression to
-%                  (significantly) reduce the file size.  The degree of
-%                  compression can be modified by changing the source code.
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherFedkiw/normalStarDemo.m

@@ -1,289 +1,0 @@
-function [ data, g, data0 ] = normalStarDemo(accuracy, reverseFlow,displayType)
-% normalStarDemo: demonstrate motion by surface normal on star interface.
-%
-%   [ data, g, data0 ] = normalStarDemo(accuracy, reverseFlow, displayType)
-%
-% Recreates figure 6.1 from O&F chapter 6, showing motion by surface normal
-%   of a star-shaped interface in two dimensions.  The parameters were
-%   guessed by trial and error.
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   reverseFlow  Boolean specifies whether to reverse the motion of the
-%                  flow at half time (default == 0).
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the helper visualizeLevelSet to see the options
-%                  (optional, default depends on grid dimension).
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 3/1/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
-%---------------------------------------------------------------------------
-% Make sure we can see the kernel m-files.
-run('../addPathToKernel');
-
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherFedkiw/spiralFromEllipse.m

@@ -1,87 +1,0 @@
-function data = spiralFromEllipse(grid, M, d, offsetR, offsetTh)
-% spiralEllipse: Generate an implicit surface function for a wound spiral.
-%
-%   data = spiralFromEllipse(grid, M, d, offsetR, offsetTh)
-%
-% Generates an implicit surface function for a wound spiral.  This routine
-%   is an attempt to duplicate the wound spiral interface found in Osher &
-%   Sethian 88 and many subsequent level set publications discussing
-%   curvature dependent flow; for example, O&F figure 4.1.  While it is
-%   visually similar, simulations indicate that it probably isn't exactly
-%   right.
-%
-% The spiral is generated by constructing an ellipse in polar coordinates.
-%   To get a wound spiral (whose head is more than one revolution removed
-%   from its tail), we create duplicated copies of the grid with polar
-%   angular coordinates theta running beyond the range [ -pi, +pi ].  The
-%   implicit surface function for the ellipsoid is calculated over the
-%   entire range of theta, and then we take a minimum over equivalent values
-%   of theta.
-%
-% The implicit surface function for the ellipsoid is
-%
-%                 f(x) = sqrt(y' * M * y) - d,
-%
-%   where y = cart2pol(x).
-%
-% 
-% Parameters:
-%   grid         Grid on which the spiral will be defined.
-%   M            Shape matrix for the ellipsoid.
-%   d            Offset for implicit surface function.
-%   offsetR      Offset of ellipse's center in the r coordinate.
-%   offsetTh     Offset of ellipse's center in the theta coordinate.
-%
-%   data         Implicit surface function for the wound spiral.
-%
-%
-% Experimentation seems to indicate the following parameters generate a
-%   visually reasonable approximation of the spiral from O&F figure 4.1:
-%
-%                   M = diag([ 0.06, 2 * pi ].^(-2));
-%                   d = 1;
-%                   offsetR = 0.5;
-%                   offsetTh = -pi/3;
-%
-%                   angleRot = pi / 100;
-%                   matrixRot = [ cos(angleRot), -sin(angleRot); ...
-%                                 sin(angleRot), cos(angleRot) ];
-%                   angleM = matrixRot * M * matrixRot';
-%                   data = spiral(g, angleM, d, offsetR, offsetTh);
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherFedkiw/spiralFromPoints.m

@@ -1,64 +1,0 @@
-function data = spiralFromPoints(grid, samples)
-% spiralFromPoints: Generate an implicit surface function for a wound spiral.
-%
-%   data = spiralFromPoints(grid, samples)
-%
-% Generates an implicit surface function for a wound spiral.  This routine
-%   is an attempt to duplicate the wound spiral interface found in Osher &
-%   Sethian 88 and many subsequent level set publications discussing
-%   curvature dependent flow; for example, O&F figure 4.1.
-%
-% The spiral is generated as a signed distance function to a set of
-%   points from a parametric description of the spiral given in Osher &
-%   Sethian 88:
-%
-%         \gamma(s) = (0.1 * exp(-10 * y(s)) - 0.05 * (0.1 - x(s)))
-%                         * [ cos(a(s)); sin(a(s)) ],
-%
-%   where
-%         a(s) = 25.0  * atan(10 * y(s))
-%         x(s) =  0.1  * cos(2 * pi * s) + 0.1
-%         y(s) =  0.05 * sin(2 * pi * s) + 0.1
-%           s \in [ 0, 1 ]
-%
-% The sampling of the range of s mentioned in Osher & Sethian 88 is 
-%   \delta s = 0.005 (200 points).
-%
-%
-% Parameters:
-%   grid         Grid on which the spiral will be defined.
-%   samples      How many samples should be taken?
-%
-%   data         Implicit surface function for the wound spiral.
-  
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell 2/19/04
-
-% This function cannot run until we have code to generate an implicit
-%   surface function from a point cloud.
-error('This function is not currently operational');
-  
-  if(grid.dim ~= 2)
-    error('Spiral can only be created on two dimensional grids');
-  end
-  
-  s = linspace(0, 1, samples)';
-  x = 0.1  * cos(2 * pi * s) + 0.1;
-  y = 0.05 * sin(2 * pi * s) + 0.1;
-  a = 25 * atan(10 * y);
-  
-  multiplier = (0.1 * exp(-10 * y) - 0.05 * (0.1 - x));
-  gamma =  repmat(multiplier, 1, 2) .* [ cos(a), sin(a) ];
-
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherShu/burgersLF.m

@@ -1,360 +1,0 @@
-function [ data, g, data0 ] = ...
-                         burgersLF(accuracy, dissType, gridDim, gridSize, tMax)
-% burgersLF: demonstrate Lax-Friedrichs on Burgers' equation.
-%
-%   [ data, g, data0 ] = burgersLF(accuracy, dissType, gridDim, gridSize, tMax)
-%  
-% This function demonstrates how the Lax-Friedrichs HJ term approximation
-%   termLaxFriedrichs can be used to approximate the solution to a multiple
-%   dimensional version of Burgers' equation (an HJ PDE with an H function
-%   convex in \grad \phi).
-%
-% The example is taken from Osher & Shu, "High-Order Essentially
-%   Nonoscillatory Schemes for Hamilton-Jacobi Equations",
-%   SIAM J. Numerical Analysis, vol 28, num 4, pp 907-922 (August, 1991).
-%   In particular, we are doing the convex versions of examples 1 and 2.
-%
-% Specifically, in dimension d
-%   PDE:  D_t \phi + H(x, D_x \phi) = 0
-%   BC:   periodic in domain [ -d, +d ]
-%   IC:   \phi(x,0) = -\cos((\pi / d) * \sum_i x_i)
-%   Ham:  H(x,p) = 0.5 * (\alpha + \sum_i p_i)^2
-%
-% Parameters (all inputs have defaults):
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   dissType     Which type of dissipation to use with the LF approximation?
-%                  'global'      Use artificialDissipationGLF (default).
-%                  'local'       Use artificialDissipationLLF.
-%                  'locallocal'  Use artificialDissipationLLLF.
-%   gridDim      Number of dimensions.  Default = 2.
-%   gridSize     Number of nodes in each dimension. 
-%                  Default = 80 / 2^(gridDim-1).
-%   tMax         Final time.  Default = 1.5 / pi^2.
-%
-%   data         Implicit surface function at tMax.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at initial time.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/OsherShu/nonconvexLF.m

@@ -1,357 +1,0 @@
-function [ data, g, data0 ] = ...
-                       nonconvexLF(accuracy, dissType, gridDim, gridSize, tMax)
-% nonconvexLF: demonstrate Lax-Friedrichs on a nonconvex Hamiltonian.
-%
-%   [ data, g, data0 ] = nonconvexLF(accuracy, dissType, gridDim, gridSize, tMax)
-%  
-% This function demonstrates how the Lax-Friedrichs HJ term approximation
-%   termLaxFriedrichs can be used to approximate the solution to a multiple
-%   dimensional version of a general HJ PDE with an H function nonconvex in
-%   \grad \phi.
-%
-% The example is taken from Osher & Shu, "High-Order Essentially
-%   Nonoscillatory Schemes for Hamilton-Jacobi Equations",
-%   SIAM J. Numerical Analysis, vol 28, num 4, pp 907-922 (August, 1991).
-%   In particular, we are doing the nonconvex versions of examples 1 and 2.
-%
-% Specifically, in dimension d
-%   PDE:  D_t \phi + H(x, D_x \phi) = 0
-%   BC:   periodic in domain [ -d, +d ]
-%   IC:   \phi(x,0) = -\cos((\pi / d) * \sum_i x_i)
-%   Ham:  H(x,p) = -\cos(\alpha + \sum_i p_i)
-%
-% Parameters (all inputs have defaults):
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst (default).
-%                  'medium'      Use odeCFL2 and upwindFirstENO2.
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   dissType     Which type of dissipation to use with the LF approximation?
-%                  'global'      Use artificialDissipationGLF (default).
-%                  'local'       Use artificialDissipationLLF.
-%                  'locallocal'  Use artificialDissipationLLLF.
-%   gridDim      Number of dimensions.  Default = 2.
-%   gridSize     Number of nodes in each dimension. 
-%                  Default = 80 / 2^(gridDim-1).
-%   tMax         Final time.  Default = 1.5 / pi^2.
-%
-%   data         Implicit surface function at tMax.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at initial time.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/RUSSOSMEREKA/ellipseError.m

@@ -1,75 +1,0 @@
-% ellipseError: script to recreate figures 10 & 11 from Russo & Smereka.
-%
-% This script demonstrates that the subcell fix from
-%
-%   Giovanni Russo & Peter Smereka, "A Remark on Computing Distance
-%   Functions," J. Computational Physics, v. 163, pp. 51-67 (2000),
-%   doi:10.1006/jeph.2000.6553
-%
-% is convergent as the grid is refined, and that reaches an equilibrium
-% where the interface (zero level set) stops moving.  The script recreates
-% figures 10 & 11 from the R&S paper, by repeated runs of reinitEllipse.m
-%
-% Note that the subcell fix is applied only to nodes near the interface.
-% The rest of the reinitialization machinery is the standard ToolboxLS
-% methods (see termReinit for details), so the results may differ from those
-% in Russo & Smereka.
-%
-% In experimental runs, it appears that the standard ToolboxLS
-% reinitialization procedure is better than that used in R&S, in the sense
-% that the rate of divergence of the error with respect to time is lower.
-% The errors appearing in the recreated figure 11 are more than an order of
-% magnitude off (although they show the same general behaviour), leading me
-% to believe that either (27) is incorrect or that I have implemented it
-% incorrectly.
-
-% Copyright 2007 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 5/16/07
-
-accuracy = 'low';
-%accuracy = 'medium';
-
-subcell_grids = [ 50, 100, 200 ];
-no_subcell_grids = [ 200 ];
-
-subcell_data = cell(length(subcell_grids), 1);
-no_subcell_data = cell(length(no_subcell_grids), 1);
-
-f10 = figure;
-hold on;
-f11 = figure;
-hold on;
-
-for i = 1 : length(subcell_grids)
-  fprintf('\nReinit with subcell fix grid size %d: ', subcell_grids(i));
-  subcell_data{i} = reinitEllipse(1, accuracy, subcell_grids(i), 0);
-  figure(f10);
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/RUSSOSMEREKA/reinitCircle.m

@@ -1,282 +1,0 @@
-function [ data, g, data0 ] = ...
-           reinitCircle(apply_fix, accuracy, show_nodes, grid_anisotropy, dim) 
-% reinitCircle: demonstrate the subcell reinitialization fix on a circle
-%
-% [ data, g, data0 ] = ...
-%          reinitCircle(apply_fix, accuracy, show_nodes, grid_anisotropy, dim)
-%
-% Demonstrates the fix specified in
-%
-%   Giovanni Russo & Peter Smereka, "A Remark on Computing Distance
-%   Functions," J. Computational Physics, v. 163, pp. 51-67 (2000),
-%   doi:10.1006/jeph.2000.6553
-%
-% for nodes near the interface of the reinitialization equation.  The
-% example is taken from section 4, and we attempt here to recreate figures 7
-% and 8.  Note that the subcell fix is applied only to nodes near the
-% interface.  The rest of the reinitialization machinery is the standard
-% ToolboxLS methods (see termReinit for details), so the results may differ
-% from those in Russo & Smereka.
-%
-% In test runs, it appears that the recreation of figure 7 shows less but
-% still significant volume loss when compared to the original figure 7.  The
-% recreation of figure 8 is essentially identical to the original figure 8.
-%
-% Note that visualization is done here using Matlab's standard contour command,
-% while Russo & Smereka do not specify how they generate their plots.
-%
-% This function was originally designed as a script file, so most of the
-% options can only be modified in the file.  For example, edit the file to
-% change the grid dimension, boundary conditions, flow field parameters,
-% etc.
-%
-% Input Parameters:
-%
-%   apply_fix: Boolean.  Should Russo & Smereka's fix be applied?
-%   Optional.  Default = True.
-%
-%   accuracy: String.  Controls the order of approximations away from the
-%   interface.  If the subcell fix is applied, the order of the
-%   approximation near the interface is governed by the subcell fix.  The
-%   choice of 'low' should correspond with Russo & Smereka's results.
-%   Optional.
-%
-%     'low'         Use odeCFL1 and upwindFirstFirst (default).
-%     'medium'      Use odeCFL2 and upwindFirstENO2.
-%     'high'        Use odeCFL3 and upwindFirstENO3.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/RUSSOSMEREKA/reinitEllipse.m

@@ -1,339 +1,0 @@
-function [ data_out, g ] = ...
-                    reinitEllipse(apply_fix, accuracy, num_nodes, do_figure_9)
-% reinitCircle: demonstrate the subcell reinitialization fix on a circle
-%
-% [ data_out, g, data0 ] = ...
-%                   reinitEllipse(apply_fix, accuracy, num_nodes, do_figure_9)
-%
-% Demonstrates the fix specified in
-%
-%   Giovanni Russo & Peter Smereka, "A Remark on Computing Distance
-%   Functions," J. Computational Physics, v. 163, pp. 51-67 (2000),
-%   doi:10.1006/jeph.2000.6553
-%
-% for nodes near the interface of the reinitialization equation.  The
-% example is taken from section 4.  This file can either recreate figure 9,
-% or it can be used by a driver routine to generate data for recreating
-% figures 10 & 11.  Note that the subcell fix is applied only to nodes near
-% the interface.  The rest of the reinitialization machinery is the standard
-% ToolboxLS methods (see termReinit for details), so the results may differ
-% from those in Russo & Smereka.
-%
-% In test runs, it appears that the recreation of figure 7 shows less but
-% still significant volume loss when compared to the original figure 7.  The
-% recreation of figure 8 is essentially identical to the original figure 8.
-%
-% Note that visualization for figure 9 is done here using Matlab's standard
-% contour command, while Russo & Smereka do not specify how they generate
-% their plots.
-%
-% This function was originally designed as a script file, so most of the
-% options can only be modified in the file.  For example, edit the file to
-% change the grid dimension, boundary conditions, flow field parameters,
-% etc.
-%
-% Input Parameters:
-%
-%   apply_fix: Boolean.  Should Russo & Smereka's fix be applied?
-%   Optional.  Default = 1.
-%
-%   accuracy: String.  Controls the order of approximations away from the
-%   interface.  If the subcell fix is applied, the order of the
-%   approximation near the interface is governed by the subcell fix.  The
-%   choice of 'low' should correspond with Russo & Smereka's results.
-%   Optional.
-%
-%     'low'         Use odeCFL1 and upwindFirstFirst (default).
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Reachability/acoustic.m

@@ -1,381 +1,0 @@
-function [ data, g, data0 ] = acoustic(accuracy)
-% acoustic: demonstrate the acoustic capture reachable set.
-%
-%   [ data, g, data0 ] = acoustic(accuracy)
-%  
-% In this example the target set is a horizontal wide but shallow rectangle
-%   near the origin, which represents the pursuer's capture set.
-%   The computation is done in relative coordinates with the pursuer fixed at
-%   the origin.
-%
-% The relative coordinate dynamics are
-%
-%        \dot x    = W_p ( 0) + W_p/R ( y) b + 2 W_e S_e ax
-%	 \dot y    = W_p (-1) + W_p/R (-x) b + 2 W_e S_e ay
-%
-%   where W_p, W_e, R, S are constants
-%         S_e = min(sqrt(x^2 + y^2), S)
-%         input a is trying to avoid the target, sqrt(ax^2 + ay^2) \leq 1.
-%	  input b is trying to hit the target, |b| \leq 1.
-%
-% For more details, see my PhD thesis, section 3.2.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   aircraft parameters, etc.
-%
-% To get exactly the result from the thesis choose:
-%   We = 1.3, Wp = 1, R = 0.8, S = 0.5
-%   and capture set [ -3.5, +3.5 ] x [ -0.2, 0 ]
-%
-% Parameters:
-%
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 4/21/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Reachability/air3D.m

@@ -1,388 +1,0 @@
-function [ data, g, data0 ] = air3D(accuracy)
-% air3D: demonstrate the 3D aircraft collision avoidance example
-%
-%   [ data, g, data0 ] = air3D(accuracy)
-%  
-% In this example, the target set is a circle at the origin (cylinder in 3D)
-% that represents a collision in relative coordinates between the evader
-% (player a, fixed at the origin facing right) and the pursuer (player b).
-%
-% The relative coordinate dynamics are
-%
-%   \dot x    = -v_a + v_b \cos \psi + a y
-%	  \dot y    = v_b \sin \psi - a x
-%	  \dot \psi = b - a
-%
-% where v_a and v_b are constants, input a is trying to avoid the target
-%	input b is trying to hit the target.
-%
-% For more details, see my PhD thesis, section 3.1.
-%
-% This function was originally designed as a script file, so most of the
-% options can only be modified in the file.  For example, edit the file to
-% change the grid dimension, boundary conditions, aircraft parameters, etc.
-%
-% To get exactly the result from the thesis choose:
-%   targetRadius = 5, velocityA = velocityB = 5, inputA = inputB = +1.
-%
-% Input Parameters:
-%
-%   accuracy: Controls the order of approximations.
-%     'low': Use odeCFL1 and upwindFirstFirst.
-%     'medium': Use odeCFL2 and upwindFirstENO2 (default).
-%     'high': Use odeCFL3 and upwindFirstENO3.
-%     'veryHigh': Use odeCFL3 and upwindFirstWENO5.
-%
-% Output Parameters:
-%
-%   data: Implicit surface function at t_max.
-%
-%   g: Grid structure on which data was computed.
-%
-%   data0: Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 3/26/04
-% Subversion tags for version control purposes.
-% $Date: 2012-07-04 14:27:00 -0700 (Wed, 04 Jul 2012) $
-% $Id: air3D.m 74 2012-07-04 21:27:00Z mitchell $
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Reachability/airMode.m

@@ -1,350 +1,0 @@
-function [ reach, g, avoid, data0 ] = airMode(accuracy)
-% airMode: demonstrate the 3 mode collision avoidance scenario.
-%
-%   [ reach, g, avoid, data0 ] = airMode(accuracy)
-%  
-% In this example, the target set is a circle at the origin
-%   that represents a collision in relative coordinates between the evader
-%   (player a, fixed at the origin facing right) and the pursuer (player b).
-%
-% Both aircraft are flying a fixed, synchronized series of segments.
-%   Each segment has fixed linear and angular velocity.  The only input
-%   is the time at which the protocol is initiated, which is a controlled
-%   switch from mode 1 to mode 2.  The switch from mode 2 to mode 3 is timed.
-%
-% The relative coordinate dynamics in mode 1 and 3 are
-%
-%        \dot x    = -v_a + v_b \cos \psi
-%	 \dot y    = v_b \sin \psi
-%
-% The relative coordinate dynamics in mode 2 are
-%
-%        \dot x    = -v_a + v_b \cos \psi + \omega y
-%	 \dot y    = v_b \sin \psi - \omega x
-%
-%   where \omega, \psi, v_a and v_b are constants.
-%
-% For more details, see my PhD thesis, section 6.1.
-%
-% Because there are no continuous inputs, this reachable set calculation
-%   can be performed with convection instead of general HJ PDEs.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   aircraft parameters, etc.
-%
-% To get exactly the result from the thesis choose:
-%   targetRadius = 5, velocityA =  3, velocityB = 4, 
-%   \psi = 4 \pi / 3, \omega = 1.
-%
-% Parameters:
-%
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%
-%   reach        Implicit surface function for unsafe (reach) set in mode 1.
-%   g            Grid structure on which data was computed.
-%   avoid        Implicit surface function for safe to switch set (avoid)
-%                  in mode 1.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Reachability/animateAcoustic.m

@@ -1,417 +1,0 @@
-function [ data, g, data0 ] = acoustic(filename, accuracy, compress)
-% animateAcoustic: create an animation of the growth of the acoustic reach set.
-%
-%   [ data, g, data0 ] = animateAcoustic(filename, accuracy, compress)
-%  
-% This file generates an animation showing how the reachable set grows
-%   as time progresses.  It is basically a combination of the files:
-%        acoustic (which sets up and handles the reach set calculation),
-%        spinAnimation (which has the code necessary for animations).
-%
-% NOTES:
-%
-% 1) This function will probably only work in Windows, since it uses
-%    the avifile command and the avi animation format.
-%
-% 2) While the animation is being generated, don't move anything
-%    (mouse, other windows) in front of the matlab figure window,
-%    otherwise that image will be captured into the avi.
-%
-% 3) If this file stops because of an error, the avi file will remain open.
-%    In that case, you must issue a "clear all" command to get rid of
-%    the open file handle and then delete the partially completed avi file.
-%
-%  
-% In this example the target set is a horizontal wide but shallow rectangle
-%   near the origin, which represents the pursuer's capture set.
-%   The computation is done in relative coordinates with the pursuer fixed at
-%   the origin.
-%
-% The relative coordinate dynamics are
-%
-%        \dot x    = W_p ( 0) + W_p/R ( y) b + 2 W_e S_e ax
-%	 \dot y    = W_p (-1) + W_p/R (-x) b + 2 W_e S_e ay
-%
-%   where W_p, W_e, R, S are constants
-%         S_e = min(sqrt(x^2 + y^2), S)
-%         input a is trying to avoid the target, sqrt(ax^2 + ay^2) \leq 1.
-%	  input b is trying to hit the target, |b| \leq 1.
-%
-% For more details, see my PhD thesis, section 3.2.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   aircraft parameters, etc.
-%
-% To get exactly the result from the thesis choose:
-%   We = 1.3, Wp = 1, R = 0.8, S = 0.5
-%   and capture set [ -3.5, +3.5 ] x [ -0.2, 0 ]
-%
-% Parameters:
-%
-%   filename     The name to give to the animation avi file.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Reachability/figureAir3D.m

@@ -1,102 +1,0 @@
-function hs = figureAir3D(g, data, data0, superimpose)
-% figureAir3D: Generate a figure for 3D aircraft collision avoidance example.
-%
-%   hs = figureAir3D(g, data, data0, superimpose)
-%  
-% Depending on the inputs, this function will generate one or two
-%   figures with three dimensional isosurfaces showing the backwards
-%   reachable set for the 3D aircraft collision avoidance example 
-%   (also called the game of two identical vehicles).
-%
-% The g, data and data0 parameters are normally generated by running
-%   air3D.m first.
-%
-% Parameters:
-%
-%   g            Grid structure on which data was computed.
-%   data         Implicit surface function for reachable set.
-%   data0        Implicit surface function for target set (optional).
-%   superimpose  Boolean specifying whether to superimpose the target and
-%                  reachable sets on a single figure using transparent
-%                  isosurfaces (optional, default = 0).
-%
-%   hs           Handles to any isosurfaces that are generated.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 4/18/04
-
-%---------------------------------------------------------------------------
-if(nargin < 2)
-  error('g and data parameters are required');
-end
-if(nargin < 3)
-  plotTarget = 0;
-else
-  plotTarget = 1;
-end
-if(nargin < 4)
-  superimpose = 0;
-end
-
-%---------------------------------------------------------------------------
-% What level set should we view?
-level = 0;
-
-% Visualize the angular dimension a little bigger.
-aspectRatio = [ 1 1 0.4 ];
-
-% A small number to avoid speckle in overlapped reachable sets.
-small = 0.01;
-
-%---------------------------------------------------------------------------
-% Visualize the reachable set.
-
-  figure;
-  hR = patch(isosurface(g.xs{1}, g.xs{2}, g.xs{3}, data, level));
-  %isonormals(g.xs{1}, g.xs{2}, g.xs{3}, data, hR);
-  set(hR, 'FaceColor', 'red', 'EdgeColor', 'none');
-  lighting phong;
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/SDE/exerciseKP529.m

@@ -1,256 +1,0 @@
-% exerciseKP529: Solve Exercise 17.1.2 from Kloeden & Platen, pp.529-531
-%
-% This script solves Exercise 17.1.2, pp.529-531 from 
-%   Kloeden & Platen, "Numerical Solution of SDEs", 3rd edition.
-%
-% The terminal value PDE is
-%
-%       D_t u + 0.5 * laplacian(u) + V(x) * u = 0
-%
-%   with V(x) = 0.5 * x^2 and terminal conditions u(T,x) = 1.
-%
-% We will solve forward in time by negating the two spatial terms.
-%
-% The analytic solution quoted there is (after substituting t := T - t):
-%
-%       u(t,x) = exp[ 0.5 * t
-%                     + 0.5 * x^2 * (1 - exp(2*t))/(1 + exp(2*t))
-%                     + 0.5 * ln(2 / (1 + exp(2*t))) ]
-%
-% Problem parameters can be modified in the file.  For example, edit the 
-%   file to change the grid dimension, boundary conditions, etc.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 8/26/04
-
-%---------------------------------------------------------------------------
-% Make sure we can see the kernel m-files.
-run('../addPathToKernel');
-
-%---------------------------------------------------------------------------
-% Integration parameters.
-tMax = 0.5;                  % Final time.
-plotSteps = 26;              % How many intermediate plots to produce?
-t0 = 0;                      % Start time.
-singleStep = 0;              % Plot at each timestep (overrides tPlot).
-
-% Period at which intermediate plots should be produced.
-tPlot = (tMax - t0) / (plotSteps - 1);
-
-% How close (relative) do we need to get to tMax to be considered finished?
-small = 100 * eps;
-
-% Useful constant.
-invSqrt2 = 1.0 / sqrt(2);
-
-%---------------------------------------------------------------------------
-% Pause after each plot?
-pauseAfterPlot = 0;
-
-% Plot in separate subplots (set deleteLastPlot = 0 in this case)?
-useSubplots = 0;
-
-% Delete previous plot unless we are using separate subplots.
-deleteLastPlot = ~useSubplots;
-
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/SDE/linearAdditiveSDE.m

@@ -1,312 +1,0 @@
-function [ data, g, data0 ] = linearAdditiveSDE(payoff, a, b, tf, dim,accuracy)
-% linearAdditive: demonstrate linear SDE with additive noise
-%
-%   [ data, g, data0 ] = linearAdditiveSDE(payoff, a, b, tf, dim, accuracy)
-%
-% This file computes the expected payoff for motion according to
-%   the linear ODE with additive noise
-%
-%	dx = a * x * dt + b dW
-%
-%   where constants a,b are specified.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   payoff       Expectation of what function should be computed?
-%                    'x'           Compute expected terminal state (default).
-%                    'x^2'         Compute expected terminal x^2.
-%                                    Used to find variance.
-%   a            Deterministic component of flow.  Scalar, defaults to 1.0.
-%   b            Stochastic component of flow.  Scalar, defaults to 0.1.
-%   tf           Final time.  Defaults to 1.0.
-%   dim          Dimension of grid in which to run.  Defaults to 1.
-%   accuracy     Controls the order of approximation.
-%                    'low'         Use odeCFL1 and upwindFirstFirst.
-%                    'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                    'high'        Use odeCFL3 and upwindFirstENO3.
-%                    'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%                  Note that the Hessian term is always second order accurate.
-%
-%   data         Expected value of payoff at terminal time.
-%   g            Grid structure on which data was computed.
-%   data0        Exact payoff at terminal time.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 8/25/04
-
-%---------------------------------------------------------------------------
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/SDE/testLinearAdditiveSDE.m

@@ -1,118 +1,0 @@
-% testLinearAdditiveSDE: script to test the correctness of linearAdditive
-%
-% This script file runs the function linearAdditive to compute
-%   the mean and variance of motion according to a linear ODE with
-%   additive white noise:
-%
-%	dx = a * x * dt + b dW
-%
-% Constants a,b may be modified within the script.  It is also possible
-%   to run a 2D version of the problem, which is just the 1D version
-%   with variable x_1 + x_2 (the orthogonal direction x_1 - x_2 has
-%   zero dynamics).
-%
-% The analytic mean and variance of such a flow is given by
-%
-%       E[x]   = exp(a * t) E[x(0)]
-%	Var[x] = 0.5 / a * ((b^2 + 2 * a * Var[x(0)]) * exp(2 * a * t) - b^2)
-%
-%   which is taken from the end of a chapter of lecture notes at
-%
-% 	http://www.eng.tau.ac.il/~liptser/lectures/lect_new10.pdf
-%
-%   The script plots these analytic solutions for comparison purposes.
-%
-% Note that many problem parameters can be modified in the routine
-%   linearAdditive.  However, modifications there may cause the
-%   analytic solutions plotted here to be incorrect.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 8/26/04
-
-%---------------------------------------------------------------------------
-% Problem parameters
-a = 1.0;
-b = 1.0;
-tf = 0.25;
-dim = 1;
-accuracy = 'medium';
-
-% Where to put the legend (according to help entry for legend)?
-legendLocation = 4;
-
-%---------------------------------------------------------------------------
-% Compute the mean state at final time.
-%   This call will also give us a grid structure to work with.
-payoff = 'x';
-[ dataX, g ] = linearAdditiveSDE(payoff, a, b, tf, dim, accuracy);
-
-% We don't need the figure generated by linearAdditive.
-close;
-
-%---------------------------------------------------------------------------
-% What is our dependent variable, 
-%   and what grid nodes should we examine for results?
-switch(dim)
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Sethian/dumbbell1.m

@@ -1,232 +1,0 @@
-function [ data, g, data0 ] = dumbbell1(accuracy)
-% dumbbell1: recreate figure 14.2 from Sethian
-%
-%   [ data, g, data0 ] = dumbbell1(accuracy)
-%
-% Recreates figure 14.2 from Sethian chapter 14, 
-%   showing motion by mean curvature of a 3D dumbbell shaped region.
-%   This example is interesting because it shows pinch off and separation
-%   of the implicit surface.
-%
-% The grid parameters have been chosen to try and get close to the figures.
-%   The user can specify the curvature multiplier within the file.
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   accuracy     Controls the order of the time approximation.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%                Note that this parameter has no effect on the order
-%                  of the spatial approximation, which is always order 2.
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 5/17/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
-%---------------------------------------------------------------------------
-% Make sure we can see the kernel m-files.
-run('../addPathToKernel');
-
-%---------------------------------------------------------------------------
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Sethian/tripleSine.m

@@ -1,226 +1,0 @@
-function [ data, g, data0 ] = tripleSine(b, accuracy)
-% tripleSine: recreate figures 2.6 and 2.7 from Sethian.
-%
-%   [ data, g, data0 ] = tripleSine(b, accuracy)
-%
-% Recreates figures 2.6 and 2.7 from Sethian chapter 2, 
-%   showing a combination of motion by surface normal and mean curvature
-%   on a 2D example with a sinusoidal curve as the initial conditions.
-%
-% Basically, this is 2D motion in the normal direction with speed
-%   			F(x) = 1 - b \kappa(x).
-%
-% The user may choose what multiplier to place on the curvature term
-%   with input parameter b.
-%
-% The grid parameters have been chosen to try and get close to figure 2.6
-%   with the same multiplier for \kappa; however, since no scaling
-%   is given in the figures an exact match is not possible.
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   b            Multiplier for the curvature dependent term.
-%                  Must be nonnegative (default = 0).
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 4/21/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
-%---------------------------------------------------------------------------
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/firstDerivSpatialConverge.m

@@ -1,102 +1,0 @@
-% Script file to demonstrate the convergence rate of the first derivative
-% approximation schemes.
-%
-% Uses firstDerivSpatialTest1 for a sequence of approximation schemes and
-% grid sizes.
-%
-% Also demonstrates Matlab's bizarre but useful method of accessing
-% structure fields by string variables.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-%
-% This software is used, copied and distributed under the licensing 
-% agreement contained in the file LICENSE in the top directory of 
-% the distribution.
-%
-% Ian Mitchell, 1/25/04
-
-run('../addPathToKernel');
-
-% Be careful with grid dx that you don't overwhelm the memory
-schemes = { @upwindFirstFirst; @upwindFirstENO2; ...
-            @upwindFirstENO3a; @upwindFirstENO3b; ...
-            @upwindFirstWENO5a; @upwindFirstWENO5b };
-gridSizes = [ 20; 40; 80; 160; 320; 640; 1280 ];
-%gridSizes = [ 20; 40; 80; 160 ];
-dim = 2;
-whichDim = 1;
-
-% File id for a place to report the statistics (the screen).
-screen = 1;
-
-schemeNames = cell(size(schemes));
-schemeStyles = { 'b-v', 'r-*', 'k-x', 'b-.o', 'k-+', 'r-.s' };
-
-% Create some figures to display the results.
-errorTypes = { 'maximum', 'average', 'rms', 'jumps' };
-for errorTypeN = 1 : length(errorTypes)
-  errorType = errorTypes{errorTypeN};
-  f.(errorType) = figure;
-  title([ 'Error analysis for ' errorType ' error.' ]);
-  hold on;
-end
-
-h = zeros(length(errorTypes), length(schemes));
-times = zeros(length(schemes), 1);
-fprintf(screen, 'For grid size %d in %d dimensions, execution time (sec)\n',...
-        gridSizes(end), dim);
-for schemeN = 1 : length(schemes);
-  scheme = schemes{schemeN};
-  schemeNames{schemeN} = func2str(scheme);
-
-  % Collect the error statistics.
-  for gridSizeN = 1 : length(gridSizes);
-    gridSize = gridSizes(gridSizeN);
-    
-    % We'll just look at the leftward error in the upwinded case.  It would
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/firstDerivSpatialTest1.m

@@ -1,257 +1,0 @@
-function [ errorL, errorR, time ] = ...
-    firstDerivSpatialTest1(scheme, dim, whichDim, dx)
-% firstDerivSpatialTest1: test various approximations of first derivative.
-%
-% [ errorL, errorR, time ] = firstDerivSpatialTest1(scheme, dim, whichDim, dx)
-%
-% Function to test the various approximations of the first spatial
-% derivative.
-%
-% Uses a concatenation of shifted sin functions for data so as to introduce
-% three derivative discontinuities (including one at the boundary in the
-% periodic BC case).
-%
-% If the function passed in scheme begins with the characters "upwind"
-% then both left and right approximations are tested, and both
-% errorL and errorR are generated.
-%
-% Otherwise errorR = [] and errorL contains the error analysis.
-%
-% If no output parameters are requested, this function produces a figure
-% showing the function and derivatives, as well as text output.
-%
-% Input Parameters:
-%
-%   scheme: Function handle to the derivative calculation scheme.
-%
-%   dim: How many dimensions should the computational grid be?
-%
-%   whichDim: Which dimension should the derivative be calculated in?
-%
-%   dx: Grid spacing.
-%
-% Output Parameters:
-%
-%   errorL: structure containing information about the error (error for the
-%   left approximation in upwinded case).
-%
-%   errorR: structure containing information about the error for the right
-%   approximation in the upwind case (otherwise just empty).
-%
-%   time: execution time to compute the derivative approximation
-%
-% The outputs errorL and errorR (when defined) are structures with the
-% following fields:
-%
-%   .maximum    maximum error (inf norm)
-%   .average    average error (one norm)
-%   .rms        root mean square error (two norm)
-%   .jump       average error at the three jumps
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 1/22/04
-
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/ghostCell.m

@@ -1,94 +1,0 @@
-% Script file to test the various routines for adding ghost cells 
-%   in dimensions one and two.
-%
-% Uses a portion of a sin function for data.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 1/13/04
-
-run('../addPathToKernel');
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-% Which one of the routines would you like to test? (comment out the rest)
-which = 'periodic';
-%which = 'extrapolate';
-%which = 'dirichlet';
-%which = 'neumann';
-
-% In how many dimensions?
-dims = 2;
-
-% Test which dimension?
-testDim = 2;
-
-% How many ghost cells?
-width = 2;
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-% Create a grid.
-clear g;
-g.dim = dims;
-g.min = zeros(g.dim, 1);
-g.max = ones(g.dim, 1);
-g.dx = 1 / 20;
-
-% details depend on the type of ghost cell
-switch(which)
-  case 'periodic'
-    g.max = g.max - g.dx;
-    g.bdry = @addGhostPeriodic;
-    % no need for bdryData
-
-  case 'extrapolate'
-    g.bdry = @addGhostExtrapolate;
-    g.bdryData.towardZero = 0;
-
-  case 'dirichlet'
-    g.bdry = @addGhostDirichlet;
-    g.bdryData.lowerValue = 0;
-    g.bdryData.upperValue = 1;
-
-  case 'neumann'
-    g.bdry = @addGhostNeumann;
-    g.bdryData.lowerSlope = 0 * g.dx;
-    g.bdryData.upperSlope = 1 * g.dx;
-
-  otherwise
-    error('Unknown type of ghost cells %s', which);
-
-end
-
-g = processGrid(g);
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-% Create some data.
-switch(dims)
-  case 1
-    dataIn = sin(pi * (g.xs{1} + 0.25));
-
-  case 2
-    dataIn = sin(pi * (g.xs{1} + 0.25)) + g.xs{2};
-
-  otherwise
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/initialConditionsTest1D.m

@@ -1,115 +1,0 @@
-function initialConditionsTest1D()
-% initialConditionsTest1D: test initial condition routines in 1 dimension.
-%
-%   initialConditionsTest1D (no arguments)
-%
-% This function (basically a script file) generates a sequence of 
-%   shapes built by constructive solid geometry methods
-%
-% In 1D, basically all the implicit surfaces are (possibly infinite) intervals.
-%   Showing the intervals themselves would be pretty dull, so we show the
-%   entire implicit surface function.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 6/23/04
-
-run('../addPathToKernel');
-
-%---------------------------------------------------------------------------
-% Standard output file id.
-fid = 1;
-
-%---------------------------------------------------------------------------
-fprintf(fid, '\n%s %s\n%s', ...
-             'A sequence of implicit surface functions in 1D', ...
-             'along with their descriptions.', ...
-             'Press any key after each display to move to the next');
-
-figure;
-
-%---------------------------------------------------------------------------
-% All 1D implicit surfaces are intervals, but we should check that the
-%   methods work (stupid Matlab stupid no 1D arrays).
-
-% A 1D grid.
-g1.dim = 1;
-g1.min = -2;
-g1.max = +2;
-g1.N = 101;
-g1 = processGrid(g1);
-
-%---------------------------------------------------------------------------
-% Some basic shapes.
-sphere1 = shapeSphere(g1, 0.2, 0.9);
-show1D(g1, sphere1);
-fprintf(fid, '\nInterval centered on %f, width %f, generated by %s', ...
-             0.2, 0.9, 'shapeSphere');
-pause;
-
-rectangle1 = shapeRectangleByCorners(g1);
-show1D(g1, rectangle1);
-fprintf(fid, '\nInterval centered on %f, width %f, generated by %s', ...
-             0.5, 0.5, 'shapeRectangleByCorners');
-pause;
-
-rectangle2 = shapeRectangleByCenter(g1);
-show1D(g1, rectangle2);
-fprintf(fid, '\nInterval centered on %f, width %f, generated by %s', ...
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/initialConditionsTest2D.m

@@ -1,176 +1,0 @@
-function initialConditionsTest2D()
-% initialConditionsTest2D: test initial condition routines in 2 dimensions.
-%
-%   initialConditionsTest2D (no arguments)
-%
-% This function (basically a script file) generates a sequence of 
-%   shapes built by constructive solid geometry methods.
-%
-% We show both the 2D implicit surface (a contour) and the implicit
-%   surface function (a 3D surface plot).
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 6/23/04
-
-run('../addPathToKernel');
-
-%---------------------------------------------------------------------------
-% Standard output file id.
-fid = 1;
-
-%---------------------------------------------------------------------------
-fprintf(fid, '\n%s %s\n%s', ...
-             'A sequence of implicit surface functions in 2D', ...
-             'along with their descriptions.', ...
-             'Press any key after each display to move to the next');
-
-%---------------------------------------------------------------------------
-% A 2D grid.
-g2.dim = 2;
-g2.min = -2;
-g2.max = +2;
-g2.N = 101;
-g2 = processGrid(g2);
-
-%---------------------------------------------------------------------------
-% Some basic shapes.
-sphere1 = shapeSphere(g2);
-show2D(g2, sphere1);
-fprintf(fid, '\nUnit circle at the origin, generated by shapeSphere');
-pause;
-
-sphere2 = shapeSphere(g2, [ -0.5; +0.5 ]);
-show2D(g2, sphere2);
-fprintf(fid, '\nUnit circle in upper left quadrant, generated by shapeSphere');
-pause;
-
-cylinder1 = shapeCylinder(g2, 2, [ 0.5; 0.5 ], 0.5);
-show2D(g2, cylinder1);
-fprintf(fid, '\nVertical slab width 0.5 centered to right at 0.5, %s', ...
-             'generated by shapeCylinder');
-pause;
-
-rectangle1 = shapeRectangleByCorners(g2);
-show2D(g2, rectangle1);
-fprintf(fid, '\nUnit square in upper right quadrant, %s', ...
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Test/reinitTest.m

@@ -1,191 +1,0 @@
-function [ data, g, data0 ] = reinitTest(initialType, accuracy, displayType)
-% reinitTest: test signedDistanceIterative.
-%
-%   [ data, g, data0 ] = reinitTest(initialType, accuracy, displayType)
-%
-% Demonstrates how signedDistanceIterative can be used to turn one of
-%   several different dynamic surface functions into signed distance
-%   function.  While it works in any dimension, it is hard to visualize the
-%   difference in dimensions higher than two.
-%  
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   flow field parameters, etc.
-%
-% Parameters:
-%
-%   initialType  String to specify which initial dynamic implicit surface.
-%                  'circle'      An off center circle/sphere (default).
-%                  'star'        A star-shaped interface (not 1D).
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   displayType  String to specify how to display results.
-%                  The specific string depends on the grid dimension;
-%                  look at the subfunction visualize to see the options
-%                  (optional, default depends on grid dimension).
-%
-%   data         Implicit surface function at t_max.
-%   g            Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 2/14/04
-
-%---------------------------------------------------------------------------
-% You will see many executable lines that are commented out.
-%   These are included to show some of the options available; modify
-%   the commenting to modify the behavior.
-  
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/analyticDoubleIntegratorTTR.m

@@ -1,40 +1,0 @@
-function mttr = analyticDoubleIntegratorTTR(grid)
-% analyticDoubleIntegratorTTR: Analytic double integrator time to reach.
-%
-%   mttr = analyticDoubleIntegratorTTR(grid)
-%  
-% Computes the analytic minimum time to reach each node in the grid
-%   for the double integrator under optimal unit bounded control.
-%
-% Analytic solution from equation (7-26), p. 514 of M. Athans & P. Falb,
-%   "Optimal Control", McGraw-Hill (1966).
-%
-% The dynamics are
-%
-%        \dot x    = y
-%	 \dot y    = b
-%
-%   where input |b| \leq 1 is trying to hit the target.
-%
-% Parameters:
-%
-%   grid         Grid structure on which data is to be computed.
-%
-%   mttr         Minimum time to reach function.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 11/26/04
-
-switchCurve = -0.5 * grid.xs{2} .* abs(grid.xs{2});
-
-right = (grid.xs{1} > switchCurve);
-left  = (grid.xs{1} < switchCurve);
-on = (grid.xs{1} == switchCurve);
-
-mttr = ((grid.xs{2} + sqrt(4 * grid.xs{1} + 2 * grid.xs{2}.^2)) .* right ...
-        + (-grid.xs{2} + sqrt(-4 * grid.xs{1} + 2 * grid.xs{2}.^2)) .* left ...
-        + abs(grid.xs{2}) .* on);

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/analyticHolonomicTTR.m

@@ -1,53 +1,0 @@
-function mttr = analyticHolonomicTTR(whichNorm, gridIn)
-% analyticHolonomicTTR: analytic solution, holonomic time to reach example.
-%
-%   mttr = analyticHolonomicTTR(whichNorm, grid)
-%  
-% Computes the analytic minimum time to reach each node in the grid
-%   for the holonomic 2D integrator under unit bounded input.
-%
-% The dynamics are
-%
-%        \dot x    = b_1
-%	 \dot y    = b_2
-%
-%   where input ||b|| \leq 1 is trying to hit the target.  The norm
-%   in which b is bounded can be modified to produce different shapes
-%   of time to reach function.
-%
-% The true solution for point x is simply ||x|| in whichever norm
-%   the input is bounded.
-%
-% Parameters:
-%
-%   whichNorm    Controls the norm in which b is bounded.
-%                  '1',1,'sum'       norm(b, 1) = sum(abs(b)) <= 1.
-%                  '2',2,'rms'       norm(b, 2) = sqrt(sum(b.^2)) <= 1.
-%                  'inf',inf,'max'   norm(b, inf) = max(abs(b)) <= 1.
-%   grid         Grid structure on which data is to be computed.
-%
-%   mttr         Minimum time to reach function.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 12/06/04
-
-
-switch(whichNorm)
-
- case { '1'; 1; 'sum' }
-  mttr = abs(gridIn.xs{1}) + abs(gridIn.xs{2});
-
- case { '2'; 2; 'rms' }
-  mttr = sqrt(gridIn.xs{1}.^2 + gridIn.xs{2}.^2);
-
- case { 'inf'; inf; 'max' }
-  mttr = max(abs(gridIn.xs{1}), abs(gridIn.xs{2}));
-
- otherwise
-  error('Unknown type of norm: %s', schemeData.whichNorm);
-
-end

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/analyticSumSquareTTR.m

@@ -1,82 +1,0 @@
-function mttr = analyticSumSquareTTR(radius, grid)
-% analyticSumSquareTTR: analytic solution special holonomic time to reach.
-%
-%   mttr = analyticSumSquareTTR(radius, grid)
-%  
-% Computes the analytic minimum time to reach each node in the grid
-%   for the holonomic 2D integrator under unit bounded input.
-%
-% This routine is specialized to compute the analytic solution for
-%   a square target set when the input is bounded in 1 norm.
-%
-% The dynamics are
-%
-%    \dot x    = b_1
-%	 \dot y    = b_2
-%
-%   where input ||b||_1 \leq 1 is trying to hit the target.
-%
-% The true solution's level sets look like octagons with long diagonal faces.
-%
-% Parameters:
-%
-%   radius       Half length of the sides of the target square.
-%                  Target square is centered at the origin.
-%   grid         Grid structure on which data is to be computed.
-%
-%   mttr         Minimum time to reach function.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 12/07/04
-
-  % Time to reach the origin when input is 1-norm bounded.
-  mttr = abs(grid.xs{1}) + abs(grid.xs{2});
-
-  % In fact, from most initial states we only have to reach the corners
-  %   of the target square.
-  mttr = mttr - 2 * radius;
-
-  % For states directly in line with the initial square, it is even easier.
-  mttr = chopCorner(mttr, grid.xs{1}, grid.xs{2}, radius);
-  mttr = chopCorner(mttr, grid.xs{2}, grid.xs{1}, radius);
-
-  % Finally, make sure we do not have negative time to reach.
-  mttr = max(0, mttr);
-
-
-
-%---------------------------------------------------------------------------
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%---------------------------------------------------------------------------
-function new = chopCorner(old, constrGrid, distGrid, radius)
-% chopCorner: chop off a corner of a diamond.
-%
-%   new = chopCorner(old, constrGrid, distGrid, radius)
-%
-% This function takes a diamond shaped time to reach function, and
-%   chops off the corners to make it octagonal.
-%
-% Parameters:
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/convectionTTR.m

@@ -1,276 +1,0 @@
-function [ mttr, data, gridOut, data0 ] = convectionTTR(front, accuracy,gridIn)
-% convectionTTR: demonstrate time to reach on a trivial convective flow field.
-%
-%   [ mttr, data, gridOut, data0 ] = convectionTTR(front, accuracy, gridIn)
-%  
-% In this example we calculate the minimum time to reach a front
-%   under simple convective motion.  Several different options of front shapes
-%   are provided.
-%
-% The dynamics are
-%
-%        \dot x    = 1
-%	 \dot y    = 0
-%
-% The goal is slightly more ambitious than the standard reach set, since
-%   we would also like to record the minimum time to reach function by
-%   tracking the time at which the reach set arrives at each node.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   aircraft parameters, etc.
-%
-% Parameters:
-%
-%   front        Shape of front.
-%                  'sine'        Use a sine function (default).
-%                  'flat'        Use a hyperplane.
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   gridIn       Computational grid.
-%                  Default is dim = 2; min = -1; max = +1; N = 101;
-%                  and bdry = @addGhostExtrapolate.
-%
-%   mttr         Minimum time to reach function at t_max.
-%   data         Implicit surface function at t_max for the reach set.
-%   gridOut      Grid structure on which data was computed.
-%   data0        Implicit surface function at t_0.
-%                  For data0 >= 0, this is also the analytic time to reach.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 12/06/04
-
-%---------------------------------------------------------------------------
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/convergeDoubleIntegratorTTR.m

@@ -1,110 +1,0 @@
-% convergeDoubleIntegratorTTR: demonstrate double integrator convergence.
-%
-% This script file runs through a variety of grid resolutions and
-%   algorithm accuracies to generate empirical convergence plots for 
-%   the double integrator example.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 12/05/04
-
-% Numerical and analytic solution generator.
-numeric = @doubleIntegratorTTR;
-
-% What accuracies?
-accuracy = { 'low', 'medium', 'high', 'veryHigh' };
-%accuracy = { 'low', 'medium' };
-
-% What resolutions?
-%   Note that some fudging will occur (eg, add 1 to get round g.dx).
-resolution = { 50; 71; 100; 141; 200; 283; 400; 566 };
-%resolution = { 50; 71; 100; 141; 200 };
-%resolution = { 50; 71; 100 };
-
-err.max = zeros(length(accuracy), length(resolution));
-err.two = zeros(length(accuracy), length(resolution));
-err.avg = zeros(length(accuracy), length(resolution));
-
-gridDX = zeros(length(resolution), 1);
-
-for res = 1 : length(resolution),
-  % Computational grid.
-  clear g;
-  g.dim = 2;
-  g.min = -1.1;
-  g.max = +1.1;
-  g.bdry = @addGhostExtrapolate;
-  
-  % Increase resolution to handle increased grid size and for round g.dx.
-  g.N = round(resolution{res} * 1.1 + 1);
-  
-  g = processGrid(g);
-
-  gridDX(res) = min(g.dx);
-
-  for acc = 1 : length(accuracy),
-
-    fprintf('\nGrid Size %d, accuracy %s\n', resolution{res}, accuracy{acc});
-
-    % Get the numeric and analytic solutions.
-    [ nttr, attr ] = feval(numeric, accuracy{acc}, g);
-
-    % Compare only in interior of domain and where nttr is defined.
-    interior = find((g.xs{1} >= -1) & (g.xs{1} <= +1) & ...
-                    (g.xs{2} >= -1) & (g.xs{2} <= +1) & ...
-                    ~isnan(nttr));
-
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/convergeHolonomicTTR.m

@@ -1,117 +1,0 @@
-% convergeHolonomicTTR: script file to demonstrate holonomic convergence.
-%
-% This script file runs through a variety of grid resolutions and
-%   algorithm accuracies to generate empirical convergence plots for 
-%   the simple holonomic system example of minimum time to reach.
-%
-% Most parameters must be set within holonomicTTR, rather than here.
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 12/06/04
-
-% Solution generator (both analytic and numeric).
-numeric = @holonomicTTR;
-
-% Which norm?
-whichNorm = 'sum';
-
-% What accuracies?
-accuracy = { 'low', 'medium', 'high', 'veryHigh' };
-%accuracy = { 'low', 'medium' };
-%accuracy = { 'high' };
-
-% What resolutions?
-%   Note that some fudging will occur (eg, add 1 to get round g.dx).
-resolution = { 50; 71; 100; 141; 200; 283; 400; 566 };
-%resolution = { 50; 71; 100; 141; 200 };
-%resolution = { 50; 71; 100; };
-
-err.max = zeros(length(accuracy), length(resolution));
-err.two = zeros(length(accuracy), length(resolution));
-err.avg = zeros(length(accuracy), length(resolution));
-
-gridDX = zeros(length(resolution), 1);
-
-for res = 1 : length(resolution),
-  % Computational grid.
-  clear g;
-  g.dim = 2;
-  g.min = -1.1;
-  g.max = +1.1;
-  g.bdry = @addGhostExtrapolate;
-  
-  % Increase resolution to handle increased grid size and for round g.dx.
-  g.N = round(resolution{res} * 1.1 + 1);
-  
-  g = processGrid(g);
-
-  gridDX(res) = min(g.dx);
-
-  for acc = 1 : length(accuracy),
-
-    fprintf('\nGrid Size %d, accuracy %s\n', resolution{res}, accuracy{acc});
-
-    % Get the solutions.
-    [ nttr, attr ] = feval(numeric, whichNorm, accuracy{acc}, g);
-
-    % Compare only in interior of domain and where nttr is defined.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/TimeToReach/holonomicTTR.m

@@ -1,457 +1,0 @@
-function [ mttr, attr, data, gridOut, data0 ] = ...
-                                       holonomicTTR(whichNorm, accuracy,gridIn)
-% holonomicTTR: demonstrate a holonomic time to reach function.
-%
-%   [ mttr, attr, data, gridOut, data0 ] = ...
-%                                     holonomicTTR(whichNorm, accuracy, gridIn)
-%  
-% In this example we calculate the minimum time to reach a small ball
-%   around the origin when motion is allowed in any direction.
-%
-% The dynamics are
-%
-%        \dot x    = b_1
-%	 \dot y    = b_2
-%
-%   where input ||b|| \leq 1 is trying to hit the target.  The norm
-%   in which b is bounded can be modified to produce different shapes
-%   of time to reach function.
-%
-% The goal is slightly more ambitious than the standard reach set, since
-%   we would also like to record the minimum time to reach function by
-%   tracking the time at which the reach set arrives at each node.
-%
-% Reinitialization is available, but only seems to degrade solution quality.
-%
-% This function was originally designed as a script file, so most of the
-%   options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-%   aircraft parameters, etc.
-%
-% Parameters:
-%
-%   whichNorm    Controls the norm in which b is bounded.  Default is 2.
-%                  '1',1,'sum'       norm(b, 1) = sum(abs(b)) <= 1.
-%                  '2',2,'rms'       norm(b, 2) = sqrt(sum(b.^2)) <= 1.
-%                  'inf',inf,'max'   norm(b, inf) = max(abs(b)) <= 1.
-%   accuracy     Controls the order of approximations.
-%                  'low'         Use odeCFL1 and upwindFirstFirst.
-%                  'medium'      Use odeCFL2 and upwindFirstENO2 (default).
-%                  'high'        Use odeCFL3 and upwindFirstENO3.
-%                  'veryHigh'    Use odeCFL3 and upwindFirstWENO5.
-%   gridIn       Computational grid.
-%                  Default is dim = 2; min = -1; max = +1; N = 101;
-%                  and bdry = @addGhostExtrapolate.
-%
-%   mttr         Minimum time to reach function at t_max.
-%   attr         Analytic minimum time to reach function.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Vector/smerekaSpirals.m

@@ -1,513 +1,0 @@
-function [ dataCurve, dataMask, g, tPlot ] = ...
-                            smerekaSpirals(whichFig, exactCopy, accuracy, tMax)
-% smerekaSpirals: example of dynamic open curves by vector level sets.
-%
-%   [ dataCurve, dataMask, g, tPlot ] = ...
-%                           smerekaSpirals(whichFig, exactCopy, accuracy, tMax)
-%  
-% This function demonstrates use of vector level set methods for dynamic
-% implicit open curves by recreating examples of spiral crystal growth from
-%
-%      Peter Smereka, "Spiral Crystal Growth," Physica D 138, pp. 282-301
-%      (2000).
-%
-% Note that this function may take a LONG TIME to run because the motion by
-% mean curvature dictates a very small timestep.  In 2007, it took more
-% than 24 hours to complete the co-rotating spirals.
-%
-% The essential idea for open curves is to propagate two implicit surface
-% functions at once.  One tracks a closed curve and the other a masking
-% region.  Where the mask function is positive, the curve is considered
-% real, and where the mask function is negative the curve is a dummy. The
-% ends of the open real curve lie where the mask function is zero.
-%
-% The dynamics for curve motion are essentially motion in the normal
-% direction plus motion by curvature.
-%
-% This function was originally designed as a script file, so most of the
-% options can only be modified in the file.
-%
-% For example, edit the file to change the grid dimension, boundary conditions,
-% flow field parameters, etc.
-%
-% Input Parameters (all inputs have defaults):
-%
-%   whichFig: Number specifying which figure from Smereka's paper to
-%   recreate.  Default is 4.
-%                    4           Counter-rotating spirals, large spacing.
-%                    7           Counter-rotating spirals, small spacing.
-%                    12          Co-rotating spirals.
-%                    17          Single spiral.
-%
-%   exactCopy: Boolean indicating whether Smereka's exact figure should be
-%   recreated.  If not, use the same parameters and initial conditions, but
-%   plot equally spaced time increments.  Default is 0.
-%
-%   accuracy: Controls the order of approximations.
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/Vector/visualizeOpenCurve.m

@@ -1,96 +1,0 @@
-function [ hCurve, hAll ] = ...
-                       visualizeOpenCurve(grid, curve, mask, showAll, titleStr)
-% visualizeOpenCurve: plots an open curve from a vector level set.
-%
-%   [ hCurve, hAll ] = ...
-%                      visualizeOpenCurve(grid, curve, mask, showAll, titleStr)
-%
-% Regular level set functions can be used only for closed curves (in 2D
-% spaces).  As observed in
-%
-%      Peter Smereka, "Spiral Crystal Growth," 
-%      Physica D 138, pp. 282-301 (2000).
-%
-% open curves can be represented by a vector level set:
-%
-%      \Gamma = \{ x | \phi(x) = 0 and \psi(x) >= 0 \}
-%
-% Following Smereka's method for plotting this "open curve", we define
-%
-%      \theta = abs(\phi), if \psi \geq 0;
-%                 +1,      if \psi   <  0.
-%
-% and then plot the zero contour of \theta - 0.5 * max(g.dx).  This
-% generates a double line that is usually visually indistinguishable from a
-% single line.
-%
-% If the boolean parameter showAll is set, the entire zero contour of \phi
-% is plotted first, and then overlapped with the \theta contour for those
-% portions which are physical.
-%
-% Parameters:
-%
-%   grid         Grid structure for both the curve and mask functions.
-%                  Must be two dimensional.
-%   curve        Level set function whose zero level set defines the curve.
-%                  In Smereka's notation, \phi.
-%   mask         Level set function whose zero sublevel set defines
-%                  the portion of the state space where the curve is real.
-%                  In Smereka's notation, \psi.
-%   showAll      Boolean specifying whether to show the entire zero contour
-%                  of \phi (distinguishing between the physical step line
-%                  and the artificial step line with color).  Default = 0.
-%   titleStr     String to place as a title to the generated plot.
-%                  Default to no title.
-%
-%   hCurve       Graphics handle(s) to the line(s) making up the zero 
-%                  contour of the physical open curve.
-%   hAll         Graphics handle(s) to the line(s) making up the zero
-%                  contour of \phi.  Only available if showAll = 1; otherwise
-%                  returns [].
-
-% Copyright 2005 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
[…]

### 2015-11-15 ian_mitchell-toolbox/Examples/addPathToKernel.m

@@ -1,16 +1,0 @@
-% Script file that adds the Kernel subdirectories to the path.
-%
-% Call this script before working with the Matlab Level Set Toolbox
-%   (or place it in your startup.m file).
-
-% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
-% This software is used, copied and distributed under the licensing 
-%   agreement contained in the file LICENSE in the top directory of 
-%   the distribution.
-%
-% Ian Mitchell, 1/13/04
-
-% Proper operation of function handles seems to require an absolute path
-%   (at least for Matlab version 6.5).
-addpath(genpath('C:\Users\Public\Documents\Studium\Master\BGCE\Projekt\multi-lbm\ian_mitchell-toolbox\Kernel'));
-

### 2015-11-15 ian_mitchell-toolbox/lbm/main.m

@@ -17,7 +17,7 @@ t_end = 5; % [s]
 x_len = 1; % [m]
 y_len = 1; % [m]
 rho_phys(1) = 1; % [kg/m^3] % Mass-density of Fluid 1,
-rho_phys(2) = 1.01; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
+rho_phys(2) = 1; % [kg/m^3] e.g. ~1000 for Water, 1.2 for Air. In [LU] Cell-density is varying around 1!
 visc(1) = 2/6;% [m^2/s] kinematic viscosity of fluid 1
 visc(2) = 3/6;% [m^2/s] kinematic viscosity of fluid 2
 sigma = 1e-6;  % [kg/s^2] surface tension between the two phases, e.g. ~ 76E-3 between water and air

### 2015-11-15 Paper/paper.tex

--- 2015-11-15 Paper/paper.tex
@@
 
-A more vivid possible application of the algorithm we presented is shown in figure TODO, which shows the transient movement of an oil drop in a lid driven cavity.
-%Fig TODO shows two rising and coalescing bubbles in a fluid, produced with our code.
+A more vivid possible application of the algorithm we presented is shown in \cref{cavity}, which shows the transient movement of an oil drop in a lid driven cavity.
+It is a known problem that level set methods tend to suffer from mass losses \cite{Thoemmes}, but still a very good insight into detailed flow behavior is possible.
+A variety of two-phase flow scenarios is possible for simulation with the presented method.
 
 The authors want to thank Ian Mitchell for providing the toolbox for level set methods.
-
-%TODO: add some nice pictures
+\begin{figure}
+	\hfill\includegraphics[trim = 0mm 8cm 0mm 8.0cm, clip, width=.95\textwidth, natwidth=595,natheight=842]{cavity.pdf}\hspace*{\fill}
+	\caption{The transient flow and deformation of a bubble in a lid driven cavity. The black lines show the interface at different points of time and the arrows display the velocity field.}
+	\label{cavity}
+\end{figure}
 

### 2015-11-15 Paper/paper.tex

@@
 This method actually models miscible fluids and can only approximately describe the behavior of immiscible fluids.
-Furthermore, there are free surface methods which only take one fluid in account for computation \cite{Koerner,Scardovelli,Hirt}.
+Furthermore, there are free surface methods which only take one fluid into account for computation \cite{Koerner,Scardovelli,Hirt}.
 They work best for large viscosity and density ratios.
@@
 
-The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}).
+The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids \cref{nse1,nse2}, see \cite{ferziger}.
 To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
@@
 Thus, the overall material properties are discontinuous and the fluids will not mix.
-
-The incompressible two-phase flow problem can be described mathematically with the Navier-Stokes equations for two incompressible fluids (\cref{nse1,nse2}, \cite{ferziger}).
-To apply them, we distribute our domain into three parts: $\Omega_1$ and $\Omega_2$ describe the two fluids and $\Gamma = \delta\Omega_1 \cap \delta\Omega_2$ is the interface in-between (\cref{intro_phases}).
-The material properties in each fluid are constant and the interface is assumed to be sharp.
-Thus, the overall material properties are discontinuous and the fluids will not mix.
-
 \begin{figure}[h!]
@@
 	\hfill\includegraphics[width=9cm,natwidth=1690,natheight=1174]{skizze.png}\hspace*{\fill}
-	\caption{Two fluid domains $\Omega_i$ separated by an interface.}
+	\caption{Two fluid domains $\Omega_i$ separated by an interface $\Gamma$. $\vec n$ denotes the surface normal.}
 	\label{intro_phases}
@@
 
+\vspace{1cm}
 The change of momentum within each fluid can be expressed as
@@
   \vec u_i(x,t) &= 0 \text{, on } \delta\Omega_i \backslash \Gamma \text{,} \\
-  \vec u_i(x,0) &= \vec u_{ini,i}(x) \text{, in } \Omega_i \text{.}
+  \vec u_i(x,0) &= \vec u_{0,i}(x) \text{, in } \Omega_i \text{.}
 \end{align}
-At the interface $\Gamma$ we have the influence of the surface tension and a no-slip condition, i.e. continuity of the velocities between the fluid phases. Therefore, we get the jump conditions,
+At the interface $\Gamma$ we have a no-slip condition, i.e.
+continuity of the velocities between the fluid phases and the balance of viscous shear stress with surface tension.
+Therefore, we get the jump conditions,
 \begin{align}
@@
 \section{Numerical Methods}
-The algorithm we describe in this paper uses the LBM and the level set method.
-The lattice Boltzmann method covers the description of the velocity and density field for each fluid, as it can be shown to reproduce the Navier-Stokes-equations in the asymptotic limit with Chapman-Enskog expansion \cite{LBM3}.
+The algorithm we describe in this paper uses the Lattice Boltzmann Method (LBM) and the level set method.
+The LBM covers the description of the velocity and density field for each fluid, as it can be shown to reproduce the Navier-Stokes-equations in the asymptotic limit with Chapman-Enskog expansion \cite{LBM3}.
 The level set method uses a velocity field to model the movement of the interface.
@@
 We use the D2Q9 model in 2D, which has 9 velocity vectors on a plane grid with unit spacing including one zero velocity (\cref{lbmc_i}).
-\begin{figure}
-	\hfill\includegraphics[width=4cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
+
+\begin{figure}[h]
+	\hfill\includegraphics[trim = 0mm 0cm 0mm 35mm, clip, width=4cm,natwidth=403,natheight=409]{LBMc_i.png}\hspace*{\fill}
 	\caption{The vectors of one cell in LBM.}
@@
 We set,
-\begin{figure}
+\begin{figure}[h!]
 	\hfill\includegraphics[width=8cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
@@
 $$
-The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error that is introduced by the first order accurate bounce back treatment,
+The additional term $R_i$ ensures the jump conditions of the normal stress and corrects the error that is introduced by the first order accurate bounce back treatment above,
 \begin{equation}
@@
 \end{equation}
-That is an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction.
+That is, an orthogonal projection of the column vectors of the (symmetric) deviatoric shear rate jump tensor on the link direction.
 This projection is weighted with the interface distance and a compensation term for the interpolation error.
@@
 \end{equation}
-\begin{figure}
+\begin{figure}[h]
 	\hfill\includegraphics[width=6cm,natwidth=445,natheight=305]{refillmethod.png}\hspace*{\fill}
@@
 We can now compute the equilibrium part $f_i^{eq}(\tilde{\rho},\tilde{u})$ according to \cref{equil} and add it to the non-equilibrium part which we copy from a nearest neighbor,
-$$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t+1) \text{.}$$
+$$f_i(\vec{x},t+1) = f_i^{eq}(\tilde{\rho},\tilde{u}) + f_i^{neq}(x+c_i,t) \text{.}$$
 This completes the refill algorithm.
 
-\begin{figure}
-	\hfill\includegraphics[width=6cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
-	\caption{Data exchange between LBM and level set method.}
-	\label{dataexchange}
-\end{figure}
 Finally, the complete coupling of the lattice Boltzmann and the level set method reads (see also \cref{dataexchange}):
@@
 \end{itemize}
+\begin{figure}[h!]
+	\hfill\includegraphics[width=6cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
+	\caption{Data exchange between LBM and level set method.}
+	\label{dataexchange}
+\end{figure}
 
@@
 \subsection{Couette channel flow}
-\begin{figure}[b!]
+\begin{figure}[h!]
 	\flushright
@@
 A more vivid possible application of the algorithm we presented is shown in \cref{cavity}, which shows the transient movement of an oil drop in a lid driven cavity.
-It is a known problem that level set methods tend to suffer from mass losses \cite{Thoemmes}, but still a very good insight into detailed flow behavior is possible.
-A variety of two-phase flow scenarios is possible for simulation with the presented method.
+It is a known problem that level set methods tend to suffer from mass losses \cite{Thoemmes}, but still a very good insight into the detailed flow behavior is possible.
+Accordingly, a variety of two-phase flow scenarios is possible for simulation with the presented method.
 

### 2015-11-15 Paper/paper.tex
Figure 3 jetzt am oberen Rand der Seite
bilder

@@
 \begin{figure}[h!]
-	\flushright
-	\hfill\includegraphics[width=9cm,natwidth=1690,natheight=1174]{skizze.png}\hspace*{\fill}
+  \vspace{-2cm}
+  \centering
+  \hspace{2cm}\includegraphics[width=10cm,natwidth=1690,natheight=1174]{skizze.png}
 	\caption{Two fluid domains $\Omega_i$ separated by an interface $\Gamma$. $\vec n$ denotes the surface normal.}
@@
 One should consider that every position, direction, and velocity is two-dimensional.
+\begin{figure}[h!]
+	\hfill\includegraphics[width=8cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
+	\caption{Link between two points in different fluids.}
+	\label{coupling}
+\end{figure}
 
@@
 We set,
-\begin{figure}[h!]
-	\hfill\includegraphics[width=8cm,natwidth=437,natheight=178]{coupling.png}\hspace*{\fill}
-	\caption{Link between two points in different fluids.}
-	\label{coupling}
-\end{figure}
 \begin{equation}
@@
 \begin{figure}[h!]
-	\hfill\includegraphics[width=6cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
+	\hfill\includegraphics[trim = 0mm 0cm 0mm 4cm, clip, width=6cm,natwidth=632,natheight=562]{dataexchange.png}\hspace*{\fill}
 	\caption{Data exchange between LBM and level set method.}
